```{r clprefpoints}
#stage and room reference points
stage.refs <- tribble(
~group, ~name, ~type,        ~x,      ~y,      ~z,   ~notes,
"ref",     "r1",    "ref", 0,        0,       0,       "",
"ref",     "r2",    "ref", 0,       28+8/12,  0,       "",
"ref",     "r3",    "ref", 10+8/12, 0,        0,       "",
"ref",     "r4",    "ref", 10+8/12, 28+8/12, 0,        "",
"ref",     "r5",    "ref", 40+6/12,      0,        0,  "",
"ref",     "r6",    "ref", 25.8,    14.4,     0,       "position guessed"
)

room.refs <- tribble(
~group, ~name, ~type,        ~x,      ~y,      ~z,   ~notes,
 "ref",     "r7",    "ref", (123+6/12)/2, -23-2/12, 0,  "",
 "ref",     "r8",    "ref", (45+2/12)/2, -(90+2/12)+(28+8/12), 0,"",
 "ref",     "r9",    "ref", 0,   -(90+2/12)+(28+8/12), 0,"" 
)

thrust.refs <- tribble(
~group, ~name, ~type,        ~x,      ~y,      ~z,   ~notes,
 "ref",     "r7",    "ref", (123+6/12)/2, -23-2/12, 0,  "",
 "ref",     "r8",    "ref", (45+2/12)/2, -(90+2/12)+(28+8/12), 0,"",
 "ref",     "r9",    "ref", 0,   -(90+2/12)+(28+8/12), 0,"" 
)

balcony.refs <- tribble(
  ~group, ~name, ~type,        ~x,      ~y,      ~z,   ~notes,
  "balcony", "b1", "ref",       35,    -50,       0,  "position guessed",
  "balcony", "b2", "ref",       35,    -25,       0,  "position guessed",
  "balcony", "b3", "ref",       20,    -35,       0,  "position guessed",
  "balcony", "b4", "ref",       12,    -35,       0,  "position guessed",
  "balcony", "b5", "ref",        6,    -31,       0,  "position guessed",
  "post",    "b10", "ref",      12,    -36,       0,  "post-position guessed",
  "post",    "b11", "ref",      13,    -36,       0,  "post-position guessed",
  "post",    "b12", "ref",      13,    -35,       0,  "post-position guessed"
)
```

```{r walls}
all.refs <- rbind(stage.refs, room.refs, balcony.refs)

wall <- function(p1, p2) {
  a <- all.refs[all.refs$name==p1,] %>% select(x,y)
  b <- all.refs[all.refs$name==p2,] %>% rename(xend=x, yend=y) %>% select(xend, yend)
  return( cbind(a, b))
}

wall.flip1 <- function(p1,p2) {
  a <- all.refs[all.refs$name==p1,] %>% select(x,y)  
  b <- all.refs[all.refs$name==p2,] %>% mutate(xend = -x, yend=y) %>% select(xend, yend) 
  return( cbind(a, b))
}

wall.flip2 <- function(p1,p2) {
  a <- all.refs[all.refs$name==p1,] %>% mutate(x = -x, y=y) %>% select(x,y)  
  b <- all.refs[all.refs$name==p2,] %>% mutate(xend = -x, yend=y) %>% select(xend, yend) 
  return( cbind(a, b))
}

s.wall  <- wall.flip1("r4","r4")  
sw.wall <- wall("r4", "r7") 
nw.wall <- wall("r7", "r8")
n.wall  <- wall.flip1("r8","r8")  
ne.wall <- wall.flip2("r8", "r7")
se.wall <- wall.flip2("r7", "r4")
stage1  <- wall("r6","r3")
stage2  <- wall.flip1("r3","r3")
stage3  <- wall.flip2("r6","r3")

wall.segments <- rbind(s.wall, sw.wall, nw.wall, n.wall, ne.wall, se.wall, stage1, stage2, stage3)

stage.segments <- rbind(stage1, stage2, stage3, s.wall,
                        wall("r4", "r6"),
                        wall.flip2("r4", "r6")
                        )
thrust <- wall.flip1("r3","r3")
#geom_curve(data=thrust, aes(x=x,y=y, xend=xend, yend=yend), curvature=-0.5)
```

```{r balconywalls}
b1.wall <- wall("b1" , "b2")
b2.wall <- wall("b2" , "b3")
b3.wall <- wall("b3", "b4")
b4.wall <- wall("b4", "b5")
b5.wall <- wall.flip1("b5", "b5")
b6.wall <- wall.flip2("b4", "b5")
b7.wall <- wall.flip2("b3", "b4")
b8.wall <- wall.flip2("b2" , "b3")
b9.wall  <- wall.flip2("b1","b2")

post1.s1 <- wall("b4", "b10")
post1.s2 <- wall("b10", "b11")
post1.s3 <- wall("b11", "b12")
post1.s4 <- wall("b12", "b4")
post2.s1 <- wall.flip2("b4", "b10")
post2.s2 <- wall.flip2("b10", "b11")
post2.s3 <- wall.flip2("b11", "b12")
post2.s4 <- wall.flip2("b12", "b4")

balc.segments <- rbind(b1.wall,  b2.wall, b3.wall, 
                       b4.wall, b5.wall, b6.wall, 
                       b7.wall, b8.wall,b9.wall 
					   ,post1.s1, post1.s2, post1.s3, post1.s4
					   ,post2.s1, post2.s2, post2.s3, post2.s4
					   )
# drawing the posts didn't display well on the plots - detail too small
```


```{r allpots}
pots.w <- tribble(
~group, ~name, ~type,        ~x,      ~y,      ~z,   ~notes,
"Down Stage",     "w01",    "F",   17.5/12,  4+1/12, 19+6/12,  "",
"Down Stage",     "w02",    "F",   68/12,    4+3/12, 19+5/12,  "",
"Down Stage",     "w03",    "F",   119.5/12, 6+6/12, 19+7/12,  "5-10 from edge on curve",
"Down Stage",     "w04",    "F",   179.5/12, 11+2/12, 19+7/12, "4-10 from front edge",
"Wall",     "w05",    "S",   239/12,   15+8/12, 19+6/12, 
                                        "2-10 from side wall. y guessed",
"Centre",     "w06",    "F",   27/12,    9+1/12,  22+1/12, "",
"Centre",     "w07",    "F",   87.5/12,  10+5/12, 21+12/12, "",
"Centre",     "w08",    "VWF",   11/12,    13+6/12, 21+2/12,  "",
"Centre",     "w09",    "VWF",   60.5/12,  14+1/12, 21,       "",
"Centre",     "w10",   "VWF",   118/12,   16+3/12, 20+5/12,  "",
"Wall",     "w11",   "S",   14+8/12,  20+4/12, 18+2/12,  
                "y guessed. 14 inch riser. 2-3 from wall"  ,
"Up Stage",     "w12",   "WF",   23/12,    18+6/12, 19+4/12, "7 inch riser",
"Up Stage",     "w13",   "WF",   87/12,    20+2/12, 19+4/12, "14 inch riser",
"Wall",     "w14",   "S",   125/12,   25+8/12, 16+2/12, "28 inch riser",
"Wall",     "w15",   "S",   44/12,    25+9/12, 16+2/12, "")

pots.e <- pots.w %>%
        filter(type != "ref") %>%
        mutate( x = -x) %>%
        mutate (name = gsub(  "w", "e", name,  fixed=TRUE)) 

all.pots <- rbind(pots.e, pots.w)
```

# Lighting Plots

The following diagrams in this section illustrate the physical layout of the lighting instruments and the related console channels that control those instruments. 

Each channel maps to one or more DMX addresses and is documented in the [DMX Details](#channel-and-dmx-details) section. 

These diagrams are approximations (dimension wise), and somewhat simplified. For example, the stage has some rounded corners at the front which are not depicted, and the physical stage is not quite symmetrical. 

## Theartrical Channels

This first diagram (@fig-clptchan) shows the auditorium and all theatrical fixtures, and so excludes the architectural fixtures (i.e. Excludes stage pots, sconces, house pendants, and the under balcony pots.)

Also excluded are two (black) incandescent fixtures which are hanging from the balcony bars. They are manually controlled via breakers in the closet.

Some items are quite moveable so may not match this diagram, specifically fixtures 34-40 and 67.

* 34-40 are sometimes free standing and washing the walls around the screens. And more recently have been installed inside the white plastic pillars.
* 67 (which is actually 6 bars) has been used for a ceiling wash, the large scrims,  etc.

```{r fig-clptchan }
#| label: fig-clptchan
#| fig-cap: Room Overview
#| cap-location: bottom

channels <-  dmx.details %>% filter(!is.na(x))

g <- ggplot() + 
        geom_segment(data=wall.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
        coord_equal() + #scale_size_identity() +
        geom_point(data=channels, aes(x=x, y=y, color=Type), size=2)  +
        geom_text(data=channels, aes(x=x, y=y, label=Channel), 
              nudge_x=channels$nx, nudge_y=channels$ny   ) +
        geom_segment(data=balc.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
        geom_curve(data=thrust, aes(x=x,y=y, xend=xend, yend=yend), curvature=-0.5)
g
```

Zoom in on the stage (@fig-clpzoomstage). Some of the lighting is mounted on the ceiling and some sits on the stage. Some of them are portabe (CSPARs and AW Bars) and are used for lighting scrims, backdrops, etc.

```{r fig-clpzoomstage}
#| label: fig-clpzoomstage
#| fig-cap: Zoom in on stage
#| cap-location: bottom

channels <-  dmx.details |>
	filter(!is.na(x)) |>
	filter(   between(Channel,18,48) | Channel == 67 )

ggplot() + 
  coord_equal() +
  geom_segment(data=stage.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
  scale_size_identity() +
  geom_point(data=channels, aes(x=x, y=y, color=Type), size=8)  +
  geom_curve(data=thrust, aes(x=x,y=y, xend=xend, yend=yend), curvature=-0.5) +
  geom_text(data=channels, aes(x=x, y=y, label=Channel)    ) 
```


## Stage Pots

```{r fig-clpstagepots}
#| label: fig-clpstagepots
#| fig-cap: Stage Pots
#| cap-location: bottom
#| 
chs <- dmx.details |> filter(Location == "Stage Pots") |> select(Channel, Usage)
lox <- merge(chs, all.pots, by.x="Usage", by.y="group" )

ggplot() +
  geom_point(data=lox,              aes(x=x, y=y, color=Usage ), size=9) +
  geom_segment(data=stage.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
  geom_text(data=lox, aes(x=x,y=y, label=Channel) ) +
  geom_curve(data=thrust, aes(x=x,y=y, xend=xend, yend=yend), curvature=-0.4) +
  coord_equal() + 
  ylim(-5,31) +
  scale_size_identity() 
```

## House Pendants

>TODO: Positions are only notional.

__Pendants over the main floor sections__

* Each pendant has two groups of lamps. An outer group of four lamps and an inner single lamp . The four outer lamps have a wide beam spread, the inner one is narrow. They are colour colour controllable (LED RGB).
* The main floor lighting is divided into two groups so that the middle of the auditorium can be lit independently from the outer sections.

__Pendants over the Balcony__

* These pendants have only two lamps. The two inner pendants have two channels. The diagram exagerates the distance between them so the channel numbers can be read on the diagram. These are designed so that light can be kept on for the technical team while the rest of the baclony is dark. 

```{r clppendants}
#| label: fig-clppendants
#| fig-cap: Pendants
#| cap-location: bottom

pendants <- tribble(
~fixture,  ~Channel, ~x,  ~y, ~sz,
"p03",  73,      -24,  -8,  1, #L+R Spot 
"p03",  69,      -24,  -8,  7, #L+R Wash
"p12",  73,       24,  -8,  1, #L+R Spot
"p12",  69,       24,  -8,  7, #L+R Wash

"p04",  73,      -32,  -20,  1, #L+R Spot 
"p04",  69,      -32,  -20,  7, #L+R Wash
"p13", 73,        32,  -20,  1, #L+R Spot
"p13",  69,       32,  -20,  7, #L+R Wash  
  
"p01",  73,      -41,  -10,  1, #L+R Spot
"p01",  69,      -41,  -10,  7, #l+R Wash
"p15",  73,       41,  -10,  1, #L+R Spot 
"p15",  69,       41,  -10,  7, #L+R Wash
  
"p05",  73,      -42,  -35,  1, #L+R Spot
"p05",  69,      -42,  -35,  7, #l+R Wash
"p14",  73,       42,  -35,  1, #L+R Spot 
"p14",  69,       42,  -35,  7, #L+R Wash    
    
"p02",  73,      -54,  -22,  1, #L+R Spot
"p02",  69,      -54,  -22,  7, #l+R Wash
"p16",  73,       54,  -22,  1, #L+R Spot 
"p16",  69,       54,  -22,  7, #L+R Wash
  
"p06", 68,      -10,  -8,  1, #Main Spot
"p06",  71,      -10,  -8,  7, #Main Wash
"p09",  68,       10,  -8,  1, #Main Spot
"p09",  71,       10,  -8,  7, #Main Wash
  
"p07",  68,      -10,  -17,  1, #Main Spot
"p07",  71,      -10,  -17,  7, #Main Wash
"p10",  68,       10,  -17,  1, #Main Spot
"p10",  71,       10,  -17,  7, #Main Wash
  
"p08",  68,      -10,  -27,  1, #Main Spot
"p08",  71,      -10,  -27,  7, #Main Wash
"p11",  68,       10,  -27,  1, #Main Spot
"p11",  71,       10,  -27,  7, #Main Wash
  
#balcony
"p19",  32,        5,  -43, 1, #Balcony Booth
"p18",  32,       -5,  -43, 1, #Balcony Booth

"p19",  72,        9,  -46, 3, #Balcony Wash
"p18",  72,       -9,  -46, 3, #Balcony Wash

"p20",  72,       25,  -45, 3, #Balcony Wash
"p17",  72,      -25,  -45, 3  #Balcony Wash
) |>
	 mutate(rn = row_number()) 

p1 <- pendants %>% filter(sz==1)
p2 <- pendants %>% filter(sz==7)
p3 <- pendants %>% filter(sz==3)

ggplot() + 
    geom_segment(data=wall.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
    geom_point(data=p2, aes(x=x, y=y, color=factor(sz), size=12) ) +
    geom_point(data=p1, aes(x=x, y=y, color=factor(sz), size=7) ) +
    geom_point(data=p3, aes(x=x, y=y, color=factor(sz), size= 8) ) +
    geom_text(data=p1, aes(x=x, y=y, label=Channel )) +
    geom_text(data=p3, aes(x=x, y=y, label=Channel ) ) +
    geom_text(data=p2, aes(x=x, y=y, label=Channel ), nudge_x=4, nudge_y=4) +
    geom_curve(data=thrust, aes(x=x,y=y, xend=xend, yend=yend), curvature=-0.4) +
    geom_segment(data=balc.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
    coord_equal() + theme(legend.position="none") + scale_size_identity()
```

```{r eval=FALSE}
d <- pendants |> 
	select(-sz, -Channel, -rn) |>
	unique()   |>
	 mutate(rn = row_number()) 
	
d |>	
ggplot() + 
    geom_segment(data=wall.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
    geom_point( aes(x=x, y=y, color=factor(sz), size=12) ) +
    geom_text(  aes(x=x, y=y, label=fixture ) ) +
    geom_curve(data=thrust, aes(x=x,y=y, xend=xend, yend=yend), curvature=-0.4) +
    geom_segment(data=balc.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
    coord_equal() + theme(legend.position="none") + scale_size_identity()
```


## Sconce (Main floor perimeter)

* These lamps are RGB lamps.
* There is a pair of 3-way light swtiches at the entrance doors that can turn off the lights. These are controlled via a switch located by the south-east and north-east doors. The control at the south-east door has a programmable timer. This is to ensure that there is some lighting in the evenings between dusk and midnight to enable safe passage.

>Note: Positions are notional. 

```{r fig-clpsconse}
#| label: fig-clpsconse
#| fig-cap: Pendants
#| cap-location: bottom

sconse1 <- tribble(
  ~Item, ~Channel, ~x, ~y,
  1,           31, -39,   -3,
  2,           31, -45,   -9,
  3,           31, -51,  -15,
  4,           31, -57,  -21,
  5,           31, -49,  -32,
  6,           31, -40,  -41
)
sconse2 <- sconse1 %>%
  mutate(Item=Item+6) %>%
  mutate(x = -x)

sconse <- rbind(sconse1, sconse2)

ggplot() + 
  geom_segment(data=wall.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
  coord_equal() + 
  theme(legend.position="none") + 
  scale_size_identity() +
  geom_point(data=sconse, aes(x=x, y=y, size= 8), color="lightblue" ) +
  geom_curve(data=thrust, aes(x=x,y=y, xend=xend, yend=yend), curvature=-0.4) +
  geom_segment(data=balc.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
  geom_text(data=sconse, aes(x=x, y=y, label=Channel ) ) 
```

<small> >TODO: add boxes on the above diagram to indicate the sconce switches
</small>

## Under the Balcony
    
Each Pot under the Balcony is an RGB lamp.

The plot is illustrative - They are not accurately placed. There are 24 pot lights (all Ketra). 

>TODO: Correct placement

```{r fig-clpubal }
#| label: fig-clpubal
#| fig-cap: Under Balcony
#| cap-location: bottom
 
ubal <- tribble(
~fixture,  ~Channel, ~x,  ~y, ~sz, 
# under balcony
"u07",  72,        3,  -37, 3,
"u06",  72,       -3,  -37, 3,
"u08",  72,        9,  -40, 3,
"u05",  72,       -9,  -40, 3,
"u09",  72,       14,  -40, 3,
"u04",  72,      -14,  -40, 3,
"u10",  72,       20,  -40, 3,
"u03",  72,      -20,  -40, 3,
"u11",  72,       25,  -37, 3,
"u02",  72,      -25,  -37, 3,
"u12",  72,       30,  -33, 3,
"u01",  72,      -30,  -33, 3,

"u23",  72,        3,  -52, 3,
"u22",  72,       -3,  -52, 3,
"u24",  72,       11,  -52, 3,
"u21",  72,      -11,  -52, 3,
"u25",  72,       22,  -52, 3,
"u20",  72,      -22,  -52, 3,
"u26",  72,       30,  -49, 3,
"u25",  72,      -32,  -49, 3,

"u13",  72,      -30,  -43, 3,
"u14",  72,      -25,  -45, 3,
"u15",  72,      -20,  -46, 3,
"u18",  72,       30,  -43, 3,
"u17",  72,       25,  -45, 3,
"u16",  72,       20,  -46, 3
)
```

```{r g.ubal.channels}
ggplot() +
    geom_segment(data=wall.segments, aes(x=x,y=y, xend=xend, yend=yend) ) +
    geom_point(data=ubal, aes(x=x, y=y, size=8), color="lightblue" ) +
    geom_text(data=ubal, aes(x=x, y=y, label=Channel )) +
    geom_segment(data=balc.segments, aes(x=x,y=y, xend=xend, yend=yend) ) +
    coord_equal() + theme(legend.position="none") +
    scale_size_identity() +
    coord_cartesian(xlim=c(-40,40),  ylim = c(-65, -25))
```

```{r g.ubal.names}
ubal |>
ggplot() + 
    geom_segment(data=wall.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
    geom_point(data=ubal, aes(x=x, y=y, size=8), color="lightblue" ) +
    geom_text(data=ubal, aes(x=x, y=y, label=fixture )) +  
    geom_segment(data=balc.segments, aes(x=x,y=y, xend=xend, yend=yend) ) + 
    coord_equal() + 
	theme(legend.position="none") + 
    scale_size_identity() +     
    coord_cartesian(xlim=c(-40,40),  ylim = c(-65, -25))
```

