---
title: "UAC Electrical Guide"
author: "Terry Doner"
date: "`r format(Sys.time(), '%B %d %Y')`"
output: 
    html_document:
        toc: true
---

```{r options, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
options(knitr.table.format = "html") # latex for pdf 
```

```{r packages, include=FALSE}
require(dplyr)
require(readxl)
require(knitr)
```

```{r getdata}
path <-"~/Documents/UACTech/SystemDocumentation/data"
#path <- "../../data"
electricalfile <- "Electrical.xlsx"
fname <- paste(path, electricalfile, sep="/")
panels <- read_excel( fname, sheet = "Panels")
nodes <- read_excel(fname, sheet = "Nodes")
routes <- read_excel(fname, sheet = "Routes")

lutron <- read_excel(fname, sheet = "Lutron")
```

> as of 1993/03/12

These notes are to be considered as a starting point only. The accuracy of these notes can not be guaranteed.

CHECK IT OUT BEFORE STARTING WORK.

Changes that have been made since 1993:

* Technical Power Panel on Main floor and revamp of balcony power - circa 2000
* 2016 Installtion of the HVAC system
* 2016 Installation of lobby thermostat
* repartitioning of the office space - several times

Please notify Terry Doner of any changes or corrections for inclusion in the next release of these notes.

[Back to top](#top)
 
# Breaker Panel - LP1
```{r echo=FALSE}
panel <- "LP1"

odd  <- panels %>% 
  filter(Panel==panel) %>% 
  filter(Circuit %% 2 == 1) %>% 
  select(Description, Circuit)
even <- panels %>% 
  filter(Panel==panel) %>% 
  filter(Circuit %% 2 == 0) %>% 
  select(Circuit, Description)

cbind(odd, even) %>% kable()
```

[Back to top](#top)

# Breaker Panel - LP2
```{r echo=FALSE}
panel <- "LP2"

odd  <- panels %>% 
  filter(Panel==panel) %>% 
  filter(Circuit %% 2 == 1) %>% 
  select(Description, Circuit)
even <- panels %>% 
  filter(Panel==panel) %>% 
  filter(Circuit %% 2 == 0) %>% 
  select(Circuit, Description)

cbind(odd, even) %>% kable()
```

[Back to top](#top)
 
# Breaker Panel - LP3
```{r echo=FALSE}
panel <- "LP3"

odd  <- panels %>% 
  filter(Panel==panel) %>% 
  filter(Circuit %% 2 == 1) %>% 
  select(Description, Circuit)
even <- panels %>% 
  filter(Panel==panel) %>% 
  filter(Circuit %% 2 == 0) %>% 
  select(Circuit, Description)

cbind(odd, even) %>% kable()
```

[Back to top](#top)

# Breaker Panel - HP3 (Heat)
```{r echo=FALSE}
panel <- "HP3"

odd  <- panels %>% 
  filter(Panel==panel) %>% 
  filter(Circuit %% 2 == 1) %>% 
  select(Description, Circuit)
even <- panels %>% 
  filter(Panel==panel) %>% 
  filter(Circuit %% 2 == 0) %>% 
  select(Circuit, Description)

cbind(odd, even) %>% kable()
```
 
[Back to top](#top)

# Node Locations
```{r echo=FALSE}

nodes %>% kable()
```

[Back to top](#top)

#Routing Descriptions
```{r echo=FALSE}

routes %>% select(RouteNum,	RouteDesc,	Wire,	Usage) %>% kable()
```

```{r echo=FALSE}
DiagrammeR::grViz("eg-routes.gv" )
```	

[Back to top](#top)
 
#Lutron Dimmers
```{r echo=FALSE}

lutron %>% kable()
```

[Back to top](#top)

# Schematic Diagram

[Back to top](#top)

# Document Source
This document is compiled by merging text and data together using rmarkdown. The source is found here `r paste0(getwd(),  "/",  knitr::current_input())`.