---
title: "UAC Technical Inventory Report"
author: "Terry Doner, Technical Director"
date: "`r format(Sys.time(), '%B %d %Y %H:%M')`"
format:
  html:
    toc: true
    toc-expand : 2
    toc-location: right
    number-sections: true
  pdf:
    toc: true
---

```{r options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
options(knitr.table.format = "html") # latex for pdf 
```

```{r package }
source("commonPackages.R")
require(treemap)
require(kableExtra)
```

```{r functions}
source("commonFunctions.r")
```

```{r data}
Tech_Inventory   <- get.inventory()
NetworkInventory <- get.network()
```

# Introduction

This document provides various reports on the technical inventory of UAC. The inventory has been divided up into multiple categories and is summarized in this table. 

The items in the Network category is only subset of the church's broader inventory. It is only the items directly connected to AV Technical systems. 

>ToDO: adjust filter throughout report to exclude disposed equipment consistently.

```{r cip_adjustmemt, eval=FALSE}
library(readr)
base2022 <- 151.2

cpi <- read_csv("~/Downloads/1810000501_databaseLoadingData.csv") |>
	filter(`Products and product groups` == "All-items")  |>
	select(REF_DATE, `Products and product groups`, VALUE ) |>
	mutate(value2022 = VALUE/base2022)

row2023 <- cpi |> filter(REF_DATE == 2022)
# value2022 is the value to divide by to adjust a value from a given year to 2022. 
row2023$REF_DATE <- 2023
#assume 2023 is same as 2022

cpi <- rbind(cpi, row2023)

Tech_Inventory <- inner_join(Tech_Inventory, cpi
							 , by=join_by(AcqYear == REF_DATE) ) |>
		mutate(AdjAcqValue = AcqValue/value2022)
```

```{r inventory }
total_value <- Tech_Inventory |>  
	filter(Disposition == "N") |>
	mutate(ext_cost = Qty*UnitValue) |>
	pull(ext_cost) |>
	sum(  na.rm=TRUE)

Inventory_Overview <- Tech_Inventory |>  
  filter(Disposition == "N") |>
  mutate( TotalValue =  Qty*UnitValue  ) |>        
  group_by(Category) |>
  summarise(ItemCount = n(), Value=sum(TotalValue, na.rm=TRUE)) |>
  #summarise(ItemCount = n(), Value=sum(AdjAcqValue, na.rm=TRUE)) |>
  
  arrange(desc(Value)) |>
  mutate(Percent = Value*100/total_value)	

Inventory_Overview |>
	gt() |>
	tab_header("Acquisition Cost of Current Inventory by Category") |>
	opt_stylize(style=3) |>
	fmt_number(columns = "Percent", decimals=0) |>
	fmt_currency(columns = "Value", scale=.001, decimals = 0) |>
	cols_label( Value = "Acquisition Cost"
			  , ItemCount ="Count" ) |>
	grand_summary_rows(columns = c("Value" )
					  , fns = list( Total ~ sum(Value) )
					  , fmt = Total ~ fmt_currency(., decimals = 0
					  					 , use_seps = TRUE, scale=.001)
					   ) |> 
	tab_footnote("Acquisition Cost in thousands (not indexed)",
				 locations=(cells_column_labels(columns="Value"))
				 )
```

```{r gg_history}
p <- Tech_Inventory |>  
  filter(Disposition == "N") |>
  filter(!is.na(AcqYear)) |>	
  mutate( TotalValue =  Qty*UnitValue  ) |>  
  #mutate( TotalValue =  AdjAcqValue  ) |>  
  group_by(AcqYear, Category) |>
  summarise(  Value=sum(TotalValue, na.rm=TRUE)) |> 
  ggplot() +
	geom_bar(aes(x=AcqYear, y=Value, fill=Category), stat="identity") +
	ggtitle("Acquisition Costs by Year", subtitle="Not Index for inflation") 

#ggplotly(p)
p
```


Or in a picture with a specfic focus on Audio, Lighting and Video.

```{r treemap}
Tech_Inventory |> 
  filter(Disposition == "N") |>
  filter(Category %in% c("Audio", "Lighting", "Video")) |>
  treemap(index=c("Category","Type"), vSize="AcqValue")
```

# Top Investments

The top 5 valued items in each category. If we have several of a thing then we base this on the value of the aggregate.
```{r top, echo=FALSE}
top_5 <- Tech_Inventory |> 
    filter(InService != "N") |>
    #filter(!is.na(Manufacturer)  ) |>
    mutate( ExtendedValue = Qty*UnitValue ) |>
    group_by(Category, Manufacturer, Model ) |> 
    summarise(TotalValue=sum(ExtendedValue), Qty=sum(Qty) ) |>
    group_by(Category) |> 
    top_n(5, TotalValue) |> 
    arrange(Category, desc(TotalValue)) |>
    select(Category, Manufacturer, Model, Qty, TotalValue)

top_5$TotalValue <- printCurrency(top_5$TotalValue ) 

top_5 |>
	gt(groupname_col = "Category") |>
	opt_stylize(style=3)
```

 
## Investments by Room
```{r}
byLocation <- Tech_Inventory |> 
    filter(InService != "N") |>
    mutate( ExtendedValue = Qty*UnitValue ) |>
    group_by(Building, Floor, Room ) |> 
    summarise(TotalValue=sum(ExtendedValue), Qty=sum(Qty) ) |>
    arrange( desc(TotalValue)) |>
	ungroup()

byLocation |>
	gt() |>
	tab_header("Investments by Room") |>
	opt_stylize(style=3) |>
	fmt_currency(columns = "TotalValue", decimals = 0)
```

```{r}
now <- format(Sys.time(), "%Y") |> as.numeric()

offset <- 1 #number of years to shift the window - use this if working on the next fiscal year view in the prior calendar year.

window.size <- 5 #years

window.first.year <- now+offset
window.last.year <- window.first.year + window.size

eol <- Tech_Inventory |> 
    filter(InService != "N", EolYear > 0) |>
    mutate( TotalValue=  trunc(Qty*UnitValue)  ) |>
  select(Category, Manufacturer,	Model, 
         Desc, TotalValue, EolYear) |>
  group_by(EolYear, Category) |>
  summarise( Value=sum(TotalValue))

mkGroup <- function(y) {
  
  if (y < window.first.year) {
  paste(" ", window.first.year-1, "and prior" ) # force sort to top
  } else if (y > window.last.year) {
  paste(window.last.year+1, "and beyond")
  } else {
  as.character(y)
  }
}

forecast <- Tech_Inventory |> 
    filter(InService != "N", EolYear > 0) |>
    mutate( TotalValue=  trunc(Qty*UnitValue)  ) |>
    rowwise() |>
    mutate( EoL_Year = mkGroup( EolYear ) ) |>
    select(Category, Manufacturer,	Model, 
                     Desc, TotalValue, EoL_Year) |>
    group_by(EoL_Year, Category) |>
    summarise( Value=sum(TotalValue)) |>
    spread(  key=Category, value=Value, fill="")

pastdue <- eol |> 
  filter(EolYear < now) |>
  group_by(Category) |>
  summarise(Value=sum(Value))

totalpastdue <- sum(pastdue$Value)
totalpastdue.df <- data.frame(Category="Total",  Value=totalpastdue)

pastdue <- rbind(pastdue, totalpastdue.df)

eol.base  <- Tech_Inventory |> 
    filter(InService != "N", EolYear > 0) |>
    mutate( TotalValue=  trunc(Qty*UnitValue)  ) |>
    select(Category, AssetTag, Manufacturer,	Model, 
         Desc, TotalValue, EolYear) |>
    arrange(Category, Manufacturer,	Model)
```

 
# Equipment End-of-Life

The purpose of the end-of-life discussion is to contribute to the fiscal planning process. What should we budget for next year needs to include the expenditure to 'keep the lights on'.

Equipment has a limited service life and when it reaches a certain age it should be replaced before it fails. It is important to note that the dollar amount is based on the original (or estimated) purchase cost and as such is only a rough indicator for the amount to budget. Like-for-like replacement is not always the right choice as needs may have changed or the appropriate technology choice.

There are several ways to look at our inventory situation: 

* By Ministry
* By Category (Audio, Video, etc)
* By Year. 

The tables that follow will do just that.

## By Ministry
The "by ministry" view is an approximation derirved from location. Some locations, Fellowship Hall specifically, are hard to classify in this manner. (It is part of children at this point). 

```{r}
# mapping Location to ministry
Location_Ministry_map <- tribble(
  ~Location, ~Ministry, 
"EastStorage", "Adult",
"Balcony",     "Adult",
"WestStorage", "Adult",
"Stage",       "Adult",
"Boardroom",   "Youth",
"FellowshipHall", "Children",
"BalconyCabinet", "Adult",
"Electrical",     "Other",
"Lobby" ,        "Adult",
"Nursery",        "Adult",       
"BalconyCloset", "Adult",
"Library",        "Adult",
"Coliseum"  ,     "Children",
"Server Room",    "Other"   
) 

ministry <- merge(Tech_Inventory, Location_Ministry_map) |> 
    filter(InService != "N", EolYear > 0) |>
    mutate( TotalValue=  trunc(Qty*UnitValue)  ) |>
    rowwise() |>
    mutate( EoL_Year = mkGroup( EolYear ) ) |>
    select(Ministry, Manufacturer,	Model, 
                     Desc, TotalValue, EoL_Year) |>
    group_by(EoL_Year, Ministry) |>
    summarise( Value=sum(TotalValue)) |>
    spread(  key=Ministry, value=Value, fill="") |>
	ungroup()

ministry |>
	gt()|>
	tab_header("Obsolescence forecast by year and ministry") |>
	opt_stylize(style=3)
 
```

## By Category

```{r eval=FALSE}
pastdue |>
	gt()|>
	tab_header("Overdue Investments Summary") |>
	opt_stylize(style=3)
```

In the next table, a breakdown by category and year of obsolescence. Years prior to `r window.first.year ` and years following `r window.last.year ` have been consolidated.

```{r}
forecast |>
	ungroup()|>
	gt()|>
	tab_header("Obsolescence forecast by Year and Category") |>
	opt_stylize(style=3)   
	# fmt_currency(decimals=0
	# 			 , columns = c("Audio", "Lighting", "Misc", "Music"
	# 			 			  , "Network", "Power", "Video"))
```

## Year-by-Year Breakdown

The next few listings are of the gear which should be replaced in that year, or earlier. Sometimes there are components that should be replaced together but fall into different years. 

```{r ybyb}
printEOL <- function(data, 
                     yr, 
                     txt="Equipment which should replaced before") { 

if  ( nrow(data) > 0 ) {  
    # result <- kable(data,
    #                 caption=paste(txt, yr) ) #|>
             # kable_styling("striped", full_width = TRUE)
	result <- gt(data) |>
			tab_header( paste(txt, yr)) |>
			opt_stylize(style=3)
    } else { 
  result <- paste("No equipment will reach end of life in", yr)
             }
  result
}

eol.base |> filter(EolYear < window.first.year ) |> 
  printEOL( window.first.year,
            "Equipment which should have been replaced prior to" )

eol.base |> 
  filter(EolYear == now+0) |> printEOL( window.first.year+0)
    
eol.base |> 
  filter(EolYear == now+1) |> printEOL( window.first.year+1)

eol.base |> 
  filter(EolYear == now+2) |> printEOL( window.first.year+2)

eol.base |> 
  filter(EolYear == now+3) |> printEOL( window.first.year+3)
```

# Serial Numbers for all items > $1000 value

This list maybe of interest when looking at insurance aspects, or if there is every a theft. Only "in service" items included.

```{r}
Tech_Inventory |> 
  filter(InService != "N", UnitValue*Qty >1000) |>
  arrange(Manufacturer, Model, SN) |>
  select(Manufacturer, Model, SN, Location) |>
	gt() |>
	opt_stylize(style=3) |>
	tab_header("Serial Numbers for all items > $1000 value")

```

 
# Not In Service
Equipment that is no longer in service. Much of this can be disposed, sold or donated.

```{r nis, echo=FALSE}
not_in_service <- Tech_Inventory |> 
    filter(InService == "N") |>
    select(Category, Manufacturer,	Model, Desc, Qty) |>
    arrange(Category ) 

not_in_service |> 
  kable( format.args = list(big.mark = ',') )# |>
#  kable_styling("striped", full_width = TRUE)
```

 
# Vendor Spend by Year

```{r vsby}
temp <-  Tech_Inventory  |> 
    filter(InService != "N" ) |>
    mutate( TotalValue=  trunc(Qty*UnitValue)  ) |>
    mutate( PurcYear = format(PurcDate, format="%Y")) |>
    select(PurcFrom,   TotalValue, PurcYear) |>
	mutate(PurcYear = ifelse(PurcYear < "2016", "2015-", PurcYear)) |>
    group_by(PurcYear, PurcFrom) |> 
    summarise( Value=sum(TotalValue)) 
    
rowtotal <- temp |>
            group_by(PurcFrom) |>
            summarise(Total = sum( Value))

vendor <- temp |> 
  spread(  key=PurcYear, value=Value, fill="")

agg <- merge(vendor, rowtotal) |>
        arrange(desc(Total))

agg |>
	ungroup() |>
	filter(Total > 500) |>
	gt() |>
	opt_stylize(style=3) |>
	tab_header("Vednor Spend by Year"
			   , subtitle = "Total spend < $500 excluded")  |>
	tab_footnote("Category includes all years prior to and including 2013.",
				 locations = cells_column_labels(columns = "2015-"))
```

 
# Inventory that can be sold

```{r}
Tech_Inventory |>
  filter(InService == "N", Disposition == "Sell") |>
  select(AssetTag, Manufacturer, Model, SN, AcqValue, DisposedValue,
         DisposedComment) |>
  kable() #|>
    #  kable_styling("striped", full_width = TRUE)
```


# Inventory that has been or can be Donated

## Turtle Mountain Bible Camp

This camp is in the middle of Manitoba farm land and won't likely encounter any interference problems.

```{r}
Tech_Inventory |>
  filter(InService == "N", Disposition %in% c("Donate", "Donated")) |>
  filter(DispositionDestination == "TMBC") |>
  select(AssetTag, Manufacturer, Model, SN,  Qty, Desc  ) |>
  kable() #|>
  #    kable_styling("striped", full_width = TRUE)
```

## In2One - Stouffville
Graham Clinton has always had a great creative vision and the new building they have acquired has wonderful architectural features which can really play well with light. Some items have already been shipped, others pendings



```{r}
Tech_Inventory |>
  filter(InService == "N", Disposition ==  "Donated" ) |>
  filter(DispositionDestination == "In2One") |>
  select(AssetTag, Manufacturer, Model, SN, Qty, Desc,
           DisposedComment ) |>
  kable(caption="Shipped") #|>
   #   kable_styling("striped", full_width = TRUE)
```

```{r}
Tech_Inventory |>
  filter(InService == "N", Disposition == "Donate" ) |>
  filter(DispositionDestination == "In2One") |>
  select(AssetTag, Manufacturer, Model, SN,  Qty, Desc,
          DisposedComment ) |>
  arrange(DisposedComment) |>
  kable(caption="Pending") #|>
    #  kable_styling("striped", full_width = TRUE)
```
# Data Quality Reports

This section provides reporting on the Quality of the Technical Inventory. Each of these lists should (ideally) be empty.
 
`r limit <- 2500` 
## High Value Assets (>$ `r limit` ) without AssetTag
 
Nothing should be listed.  
```{r} 
Tech_Inventory |> 
      filter( is.na(AssetTag) ) |> 
      filter( UnitValue > limit ) |>
      kable(align="l") # |>
    #  kable_styling("striped", full_width = TRUE)
```

```{r limits}
dt <- 2015
limit <- 100
cap <- glue("Items acquired after {dt} and value over ${limit} without AssetTag")
```

 
## New Assets (Newer than `r dt` ) without AssetTag

 
With a purchase price exceeding $`r limit`. Nothing should be listed. 
 
```{r} 
Tech_Inventory |> 
      filter( is.na(AssetTag) ) |> 
      filter( AcqYear > dt ) |>
      filter( UnitValue > limit ) |>
	  filter( Type != "Cable" ) |>
	  select(Category, Qty, UnitValue, Manufacturer, Model, Building
	  	   , Floor,	Room,	Location,	Type,	Desc,	SN	 ) |>
	  gt() |>
	  opt_stylize(style=3) |>
	  tab_header(cap, subtitle = "Cables excluded") |>
	  fmt_currency(decimals=0, columns=c("UnitValue"))
```

## All Asset Tags are unique

Nothing should be listed.
```{r}
dups <- Tech_Inventory |> 
      filter( !is.na(AssetTag) ) |> 
      select(AssetTag) |>
      group_by(AssetTag) |>
      summarise(n=n()) |>
      filter(n>1) 

inner_join(dups, Tech_Inventory, by=join_by( AssetTag == AssetTag  )) |>
	  arrange(AssetTag, n, ) |>
	  select(AssetTag, n, Category,Manufacturer , Model, Type, Desc ) |>
	  gt( groupname_col = c("AssetTag", "n"))  |>
	  tab_header(("Duplicate Asset Tags")) |>
	  opt_stylize(style=3)
```

`r limit <- 1500`

## High-Valued Assets without serial numbers (> $`r limit`).
Nothing should be listed.
```{r}
Tech_Inventory |> 
      filter( is.na(SN) ) |> 
      filter( UnitValue > limit ) |>
	  mutate(InService = glue("InService={InService}")) |>
      select(AssetTag, Manufacturer, Model, Desc, UnitValue, InService) |>
	  gt(groupname_col = "InService") |>
	  opt_stylize(style=3) |>
	  tab_header("High-Valued Assets without serial numbers")
```

```{r eval=FALSE}
x <- Tech_Inventory |> 
    filter(InService != "N") |>
    mutate( ExtendedValue = Qty*UnitValue ) |>
    filter(is.na(Location ) ) |> 
    arrange(desc(tv))  

    print(nrow(x))
    print(sum(x$tv))

    x |>
      select(Manufacturer,	Model,Desc, tv) |>
    kable(align="l")  #|>
 #   kable_styling("striped", full_width = TRUE)
```

 
# Document Source
This document is compiled by merging text and data together using rmarkdown. The source is found here `r file.path(getwd(), knitr::current_input())`.