---
title: "Network Graph"
author: "Terry Doner"
date: '2019-02-01'
output:
  html_document: default
---

Data-driven network diagrams depicting physical connectivity (Layer 1). Location inforamtion is in the data table accompanying each diagram.

I don't have the official asset tags for some equipment, such as the wireless access points. 

TODO: See if the port configuration data can be pulled from each switch and use that rather than a manually maintained table. MAC address can be used as a linking key.

```{r options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
options(knitr.table.format = "html") 
```

```{r eval=FALSE}
install.packages("ggraph")
install.packages("tidygraph")
```

```{r packages}
require(ggraph)
require(tidygraph)
require(kableExtra)
require(dplyr)
require(readxl)
require(tidyr)
```
 
```{r functions}
source("commonFunctions.R")
```
 
```{r data}
NetworkInventory <- get.network()
TechInventory <- get.inventory()

net_map <- NetworkInventory %>%
           mutate(to = AssetTag, from=UpLink) %>% #always have trouble with rename
           select(from, to, Category)
```

```{r}
selected.at <- c("NSCU-A001","NSCU-A002","NSCU-A003",
                 "NSCU-A004","NSCU-A005",
                 "MHPL-0004", "Rogers",
                 "CSWU1"
                 )

core <- net_map %>%
        filter( to %in% selected.at) %>%
        as_tbl_graph() %>%
        mutate(Type = ifelse( substr(name,1, 4) =="NSCU", "Switch",  "")) %>%
        mutate(Type = ifelse( substr(name,1, 4) =="MHPL", "Modem",  Type)) %>%
        mutate(Type = ifelse( substr(name,1, 4) =="CSWU", "Server", Type)) 
```

```{r}
ggraph(core, layout = 'kk') + 
    geom_edge_fan(aes(alpha = ..index..),  show.legend = FALSE) + 
    theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
    geom_node_label(aes(label=name, fill=Type), size=2.7, alpha=0.5) +
    theme(legend.position="none" ) +
    labs(title="Network Core")
```
 
```{r corechart}
selected.at <- as_tibble(core) %>%
               mutate(AssetTag = name) 

merge(NetworkInventory, selected.at) %>% 
    select(AssetTag, Location, Rack, Device, Usage) %>%
    kable(align="l") %>% 
    kable_styling("striped", full_width = FALSE)
```
 
```{r}
graph_it <- function(data, node) { 
  gd <- data %>% filter(from==node )

gr <- as_tbl_graph(gd) %>% 
    mutate(Type = ifelse( centrality_degree(mode = 'out')  >0,  "Core" , "Edge" )) %>%
    mutate(Type = ifelse( substr(name,1, 2) =="ap", "WAP", Type) ) %>%
    mutate(Type = ifelse( substr(name,1, 4) =="NAHU", "WAP", Type) ) 


a<- ggraph(gr, layout = 'nicely') + 
    geom_edge_fan(aes(alpha = ..index..), show.legend = FALSE) + 
    theme_graph(foreground = 'steelblue', fg_text_colour = 'white') +
    geom_node_label(aes(label=name, fill=Type), size=3 ) +
    theme(legend.position="none") +
    labs(title=paste("Connectivity for:", node))

selected.at <- as_tibble(gr) %>%
               mutate(AssetTag = name) 

b <- merge(NetworkInventory, selected.at) %>% 
    select(AssetTag, Location, Rack, Device, Usage) %>%
    kable(align="l") %>% 
    kable_styling("striped", full_width = FALSE)

list(graph=a,data=b)
}
```

```{r}
o <- graph_it(net_map , "NSCU-A001")
o$graph
o$data
o <- graph_it(net_map , "NSCU-A002")
o$graph
o$data
o <- graph_it(net_map , "NSCU-A003")
o$graph
o$data
o <- graph_it(net_map , "NSCU-A004")
o$graph
o$data
o <- graph_it(net_map , "NSCU-A005")
o$graph
o$data
```
 
```{r scratch, eval=FALSE}
selected.at <- get_AssetTags(net_map)

merge(NetworkInventory, selected.at) %>% 
    select(AssetTag, Location, Device, Usage) %>%
    kable(align="l")

```
 
 
```{r eval=FALSE}
 
 location hierarchy
 org
 --campus
 ---building
 ----level
 -----room
 ------container (rack/desk)
 -------position (u count from top, U21-2/3 = 21 units down, 2nd of 3 devices)

```

# Document Source
This document is compiled by merging text and data together using rmarkdown. The source is found here `r file.path(getwd(), knitr::current_input())`.

# Change History

`r commit.log.html( knitr::current_input() )`