---
title: "System Design Fellowship Hall"
date: last-modified
editor: visual
execute: 
  eval: TRUE
  echo: false
  warning: false
  message: false

format:
  html:
    toc: true
  pdf:
    toc: true
  titlepage-pdf:
    toc: true     

always_allow_html: yes  
---

# Introduction

This is a detailed design report for the Audio and Video systems in Fellowship Hall. This documents is almost complete, with the bluray player details missing.

```{r packages_functions }
source('commonPackages.R')
source('commonFunctions.R')
source('commonDiagram.R')
```

```{r get_data}
inventory <- get.inventory()  |>  
	filter(   Building == 'Main'  
			& Floor    == 'Basement'  
		    & Room     %in% c( 'FellowshipHall', 'Electrical'
		    				   , "Server Room")) |>
	filter(  Disposition == 'N') |>
	filter(!is.na(Building) )
 
cables <- get.cables()
```

# Audio Diagrams

Diagrams have been broken up into sections to be more readable.

::: {#fig-audio-inputs-vid .cell-output-display}
```{r audio_diag_in_vid, results="asis"}
label <- "'Audio '"

targets_v <- c(  
			   'CDWU-A001'   
			 , "fh_guest"
			 , "2402-0701" # audio extractor
			 , "ZVPU-0001" #bluray
			 
			   , "2401-3004" # video switch
			 ) 
xd <- c("2401-2800","2401-3001" , "2402-0702", "2401-3002"
		 , "2401-3100",  "2401-3101"
		, "NSCU-A002" #ether switch
 		, "NAHU-B008" #wifi wap
	    , "2401-3003" #audio mixer
		) 
dot_code <- get_diagram(targets_v
						, inventory, cables
						, label=label , exc_dev=xd )
out_str <- get_diagram_aux(dot_code)
cat(out_str)
#grViz(dot_code)
```

Audio Inputs from Video Diagram
:::

::: {#fig-audio-inputs .cell-output-display}
```{r audio_diag_in, results="asis"}
label <- "'Audio '"

targets_i <- c(  "2401-6034"
			  
			 , "2402-0701" # audio extractor
			 , "2401-3001" # hdmi-sdi
			 , "2401-3003" # mixer
			 , "2402-0702" #bidi
			 ) 
xd <- c("2401-2800","2401-3001" , "2402-0702", "2401-3002"
		 , "2401-3100",  "2401-3101"
		, "NSCU-A002" #ether switch
 		, "NAHU-B008" #wifi wap
		 , "2401-3004"
		) 
dot_code <- get_diagram(targets_i
						, inventory, cables
						, label=label , exc_dev=xd )
out_str <- get_diagram_aux(dot_code)
cat(out_str)
#grViz(dot_code)
```

Audio Inputs (non-video) Diagram
:::

::: {#fig-audio-outputs .cell-output-display}
```{r audio_diag_out, results="asis"}
label <- "'Audio '"

targets_o <- c(  "2401-3003" # mixer
			 , "2401-3100",  "2401-3101" # Speakers
			 ) 
xd <- c(   "2401-6034" #mic
		 , "2402-0701" #adio extractor
		 , "fh_guest"
		) 
dot_code <- get_diagram(targets_o
						, inventory, cables
						, label=label 
						, exc_dev=xd )
out_str <- get_diagram_aux(dot_code)
cat(out_str)
#grViz(dot_code)
```

Audio Output Diagram
:::

::: {#fig-audio-dev .cell-output-display}
```{r audio_devices, results="asis"}

targets <- c(  targets_i, targets_o , targets_v  ) 

inventory |>
	filter(AssetTag %in% targets) |>
	select(AssetTag, Manufacturer, Model, Desc) |>
	arrange(AssetTag) |>
	gt() |> 
	opt_stylize(style=3) |>
	tab_header("Audio Devices") |>
	print_gt_table() |>
	cat()
```

Audio Devices
:::

::: {#fig-audio-cables .cell-output-display}
```{r audio_cables, results="asis"}
x <- targets
ex <- c()

cables |> 
	filter(SrcTag %in% x | DstTag %in% x  ) |> 
	filter(str_detect(Type, "audio") |  str_detect(Type, "amp") ) |>
	select(-Invoice, -GraphFormula, -`Labelled?`) |>
	arrange(SrcTag, DstTag) |>
	gt() |> 
	opt_stylize(style=3) |>
	tab_header("Audio Cables") |>
	sub_missing(missing_text = "") |>
	print_gt_table() |>
	cat()
```

Audio Cables
:::

# Video System Diagrams

::: {#fig-video-system1 .cell-output-display}
```{r video_diagram_1, results="asis" }
targets1 <- c(  'CDWU-A001' 
			, "2401-3004"
			, "ZVPU-0001" #bluray
			, "2402-0701"
			, "fh_guest"
            )
 
xd <- c("2401-3003"	, "2402-0702"
		, "NSCU-A002", "NAHU-B008")
dot_code <- get_diagram(targets1, inventory, cables
						, label="'Video System'"
						, exc_dev=xd)
out_str <- get_diagram_aux(dot_code)
cat(out_str)
#grViz(dot_code)
```

Video Diagram - Source to Audio Extractor
:::

::: {#fig-video-system2 .cell-output-display}
```{r video_diagram_2, results="asis" }
targets2 <- c(   
              '2401-3002'  
			, "1704-0100"
		 	, "2402-0702"
			, "2402-0701" 
            )
 
xd <- c("2401-3003", "2401-3004"  )
dot_code <- get_diagram(targets2, inventory, cables
						, label="'Video System'"
						, exc_dev=xd)
out_str <- get_diagram_aux(dot_code)
cat(out_str)
#grViz(dot_code)
```

Video Diagram - Audio Extractor to Projector
:::

::: {#fig-video-diag .cell-output-display}
```{r video_devices, results="asis"}
targets <- c( targets1, targets2)
inventory |>
	filter(AssetTag %in% targets) |>
	select(AssetTag, Manufacturer, Model, Desc) |>
	gt() |> 
	opt_stylize(style=3) |>
	tab_header("Video Devices") |>
	print_gt_table() |>
	cat()

```

Video Devices
:::

::: {#fig-video-cables .cell-output-display}
```{r video_cables, results="asis"}
x <- targets
cables |> 
	filter(SrcTag %in% x | DstTag %in% x  ) |> 
	filter(Type %in% c('hdmi','sdi')) |>
	select(-Invoice, -GraphFormula, -`Labelled?`) |>
	arrange(SrcTag, DstTag) |>
	gt() |> 
	opt_stylize(style=3) |>
	tab_header("Video Cables") |>
	print_gt_table() |>
	cat()
```

Video Cables
:::

{{< pagebreak >}}

# Network Diagram

::: {#fig-network .cell-output-display}
```{r network_digram, results="asis" }
targets <- c(  
			  "NSCU-A002" #electrical sw   
			,"CDWU-A001")
xd <- c("2401-3003", "2401-3004", "patchpanel", "NSCU-A005"  
		, "NSCU-A001") 
dot_code <- get_diagram(targets, inventory, cables
						, label="'Network System'"
						, exc_dev=xd)
out_str <- get_diagram_aux(dot_code)
cat(out_str)
```

Network
:::

{{< pagebreak >}}

# Full Inventories

::: {#fig-item-inv .cell-output-display}

```{r item_inventory, results='asis'}
#| label: fig-item_inventory

asset_items <- inventory |>
	filter(  Building == 'Main' 
		   & Room     == 'FellowshipHall' 
		   ) |> 
    arrange(AssetTag) |>
	select(AssetTag, Category ,Location, SN, Manufacturer, Model, Type, Desc) 

nr <- nrow(asset_items )
mhdr <- glue("Installed Items (excluding cables)")
shdr <- glue("n={nr}") 

asset_items |>
	gt() |>
	opt_stylize(style = 3) |>
	tab_header( mhdr, subtitle = shdr  )   |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=AssetTag)
	) |>
	print_gt_table() |>
	cat()
```
Item Inventory
:::

::: {#fig-installed-cables .cell-output-display}

```{r installed_cables, results="asis"}
cable_items <- cables |>
	filter(SrcTag %in% asset_items$AssetTag 
		   | DstTag %in% asset_items$AssetTag) |>
	filter(!is.na(SrcTag) & !is.na(DstTag))

nr <- nrow(cable_items)
mhdr <- glue("Installed Cables ")
shdr <- glue("n={nr}")

cable_items |>
	arrange(Tag) |>
	select(Tag, SrcTag, SrcPort, DstTag, DstPort, Type, Usage, Notes) |>
	gt() |>
	opt_stylize(style=3) |>
	tab_header(mhdr, subtitle = shdr) |>
	sub_missing(missing_text="") |>
	print_gt_table() |>
	cat()
```
Installed Cables
:::

{{< include common_trailer.qmd >}}
