---
title: "System Design - Projection"
 
execute: 
  eval: true
  echo: false
  warning: false
  message: false
format:
  html:
    toc: true 
  pdf:
    toc: true
  titlepage-pdf:
    toc: true
always_allow_html: yes
---

```{r packages}
source("commonPackages.R")
```

```{r functions}
source("commonFunctions.R")
source("commonDiagram.R")
source("commonDiagramConnectivity.R")
```

```{r data }
NetworkInventory <- get.network()
assets           <- get.assets()
db.inventory     <- get.inventory()
db.cables        <- get.cables()
```

# Introduction

This document provides key technical documentation for the projection subsystem at UAC: how ProPresenter's outputs reach the projectors and the TVs around the building. @fig-overview provides a simplified overview of the whole video system; the projection parts are the ProPresenter computer, the DeckLink, the two video matrices, the projectors and the TVs. Recording, streaming and the video mixer are covered in the *System Design - Video* document.

```{dot overview}
//| fig-width: 4
//| label: fig-overview
//| fig-cap: "Video System Overview"
//| file: gv/sdv-topology0-overview.gv
```

Every significant inventory item has an asset tag. Tags are either of the form Zxxx-xxxx or yymm-ddxx (the date the item was tagged plus a sequence number). Cables are tagged the same way.

# ProPresenter {#sec-propresenter}

ProPresenter runs on the Mac Studio CUMU-G002. It produces seven SDI outputs through the DeckLink card, one HDMI output through the computer's dock, and an NDI output on the network:

* Three DeckLink outputs are the **triple wide** image (TW1, TW2, TW3), one per front-of-house projector.
* Two DeckLink outputs feed the ATEM video mixer as a **Key** and **Fill** pair. The *Fill* looks like a normal single wide image. The *Key* is a mask which the ATEM uses to select which parts of the *Fill* are displayed: white areas are shown, black areas are transparent, and grey areas are semi-transparent.
* One DeckLink output is the **stage display**, and another carries a second stage display layout.
* The DeckLink also has one **input** (sdi7) which brings the ATEM program back into ProPresenter so that live video can be placed on a slide. The video is delayed by about 20ms, which may be noticeable on a tight vocal shot or a drummer.
* The **HDMI** output ("PP SW", the switched output) is a normal operating-system display and is used when the DeckLink outputs are not appropriate, e.g. PowerPoint, DVDs or a web page. It reaches the VideoHub through the VS-88DT and an HDMI-to-SDI converter.
* The **NDI** output is a copy of the stage display sent over the network to the audio engineer running the livestream.

::: callout-note
See the document *deepdive_displaying_a_web_page_within_pp7.docx* for instructions on how to display a browser webpage via ProPresenter.
:::

## DeckLink

The DeckLink Quad 2 (ZVIU-E004) sits in a Thunderbolt expansion chassis (ZVIU-E005) next to the Mac Studio and is configured with Blackmagic's *Desktop Video* application. Its ports are special purpose outputs which are not recognized by the Mac operating system, so you cannot do things like DVD playback or Safari web page display on them; use the HDMI output for that, with a corresponding routing change on the VideoHub.

```{r decklink-ports}
#| label: tbl-decklink-ports
#| tbl-cap: DeckLink Ports
dl <- "ZVIU-E004"
# what ProPresenter assigns to each port (logical), and what each port is cabled to (physical)
logical  <- db.cables |> filter(SrcTag == "CUMU-G002", DstTag == dl) |>
	select(Port = DstPort, ProPresenter = Usage)
physical <- db.cables |>
	filter((SrcTag == dl & DstTag != dl & DstTag != "CUMU-G002") |
		   (DstTag == dl & SrcTag != dl & SrcTag != "CUMU-G002"),
		   Type != "internal") |>
	mutate(Port = ifelse(SrcTag == dl, SrcPort, DstPort),
		   Direction = ifelse(SrcTag == dl, "Output", "Input"),
		   Connected = ifelse(SrcTag == dl, paste(DstTag, DstPort), paste(SrcTag, SrcPort))) |>
	select(Port, Direction, Connected, Usage) |>
	distinct()
physical |>
	full_join(logical, by = "Port") |>
	arrange(Port) |>
	select(Port, ProPresenter, Direction, Connected, Usage) |>
	gt() |>
	opt_stylize(style = 3) |>
	cols_label(ProPresenter = "ProPresenter Output", Connected = "Connected To") |>
	sub_missing(missing_text = "-")
```

The paths from the DeckLink through the VideoHub to their normal destinations are generated from the cable database below. The dashed lines inside the VideoHub are the default crosspoints.

```{r decklink-paths, results='asis'}
dot_code <- videohub_path_diagram(db.cables, db.inventory
					, src_tags = c("ZVIU-E004", "ZVIU-A006")
					, label = "ProPresenter outputs through the VideoHub")
cat(get_diagram_aux(dot_code))
```

# Video Routing

There are two video matrices. The BMD VideoHub (2507-0700) is the primary one: every ProPresenter output goes into it and the projectors and most TVs are fed from it over SDI. The older Kramer VS-88DT (ZVKU-A001) is an HDBaseT matrix which now provides the long cable runs to the lobby, nursery and rear projector, and a second, fallback feed to each front projector.

## VideoHub (SDI)

The VideoHub is a 40x40 SDI matrix. Any input can be routed to any number of outputs. It is normally left on its default routing; the *VideoHub* page on the video desk Stream Deck has presets that change the projector routing for special situations (see the Operations document). Routing can also be changed from the front panel or the *VideoHub Control* application.

The projector and TV paths from the VideoHub are generated from the cable database below. Each front projector is reached through a BiDirectional SDI/HDMI converter mounted at the projector.

```{r vh-projectors, results='asis'}
dot_code <- videohub_path_diagram(db.cables, db.inventory
					, dest_tags = c("2601-1304", "2601-1305", "2601-1306")
					, label = "VideoHub to the Front Projectors")
cat(get_diagram_aux(dot_code))
```

```{r vh-tvs, results='asis'}
dot_code <- videohub_path_diagram(db.cables, db.inventory
					, dest_tags = c("ZVIU-A005", "ZVIU-G004", "2512-1001")
					, label = "VideoHub to the Stage Display TV, the VS-88DT and the Library TV")
cat(get_diagram_aux(dot_code))
```

```{r sd-videohub}
#| label: tbl-sd-videohub
#| tbl-cap: Stream Deck VideoHub Presets
tribble(
	~Preset, ~Effect,
	"Normal Projectors", "Triple wide (TW1/2/3) to projectors A/B/C. The default.",
	"Baptism", "Routing configuration for a baptism.",
	"Pgm to B", "ATEM program to the centre projector (B); A and C stay on triple wide.",
	"Pgm to A & C", "ATEM program to the side projectors (A and C).",
	"ProP HDMI to ABC", "The ProPresenter HDMI (PP SW) output to all three front projectors, e.g. for a DVD or PowerPoint."
) |>
	gt() |>
	opt_stylize(style = 3)
```

## VS-88DT (HDBaseT)

The Kramer VS-88DT is an 8x8 matrix with HDMI inputs and HDMI or [HDBaseT](https://en.wikipedia.org/wiki/HDBaseT) outputs. HDBaseT carries video over Cat6 cable, which is how the long runs to the lobby, nursery and rear projector are made. It can be controlled from the buttons on its front panel or from its built-in web page.

The front projectors each have two feeds: HDMI on **Input C** from the VideoHub path above, and HDBaseT on **Input D** from the VS-88DT. Input D is the fallback if the SDI path fails, and is also used for HDCP-protected (copyrighted) material, which the SDI/HDMI converter path will not pass.

```{r vs-in, results='asis'}
#| tbl-cap: "VS-88DT Inputs"
#| tbl-cap-location: bottom
dev <- "ZVKU-A001"
tab <- db.cables |>
	filter(DstTag == dev, SrcTag != dev, !Type %in% c("cat6a")) |>
	left_join(db.inventory |> select(AssetTag, Desc), by = c("SrcTag" = "AssetTag")) |>
	select(Tag, DstPort, SrcTag, Desc, SrcPort, Usage) |>
	arrange(DstPort) |>
	gt() |>
	opt_stylize(style = 3) |>
	tab_header(glue("Inputs for {dev}")) |>
	cols_label(Tag = "Cable", DstPort = "Input", SrcTag = "Source", Desc = "Source Description") |>
	sub_missing(missing_text = "-")
print_gt_table(tab) |> cat()
```

```{r vs-out, results='asis'}
#| tbl-cap: "VS-88DT Outputs"
#| tbl-cap-location: bottom
tab <- db.cables |>
	filter(SrcTag == dev, DstTag != dev) |>
	left_join(db.inventory |> select(AssetTag, Desc), by = c("DstTag" = "AssetTag")) |>
	select(Tag, SrcPort, DstTag, Desc, DstPort, Usage) |>
	arrange(SrcPort) |>
	gt() |>
	opt_stylize(style = 3) |>
	tab_header(glue("Outputs for {dev}")) |>
	cols_label(Tag = "Cable", SrcPort = "Output", DstTag = "Destination", Desc = "Destination Description") |>
	sub_missing(missing_text = "-")
print_gt_table(tab) |> cat()
```

```{r vs-routes}
#| label: tbl-vs-routes
#| tbl-cap: VS-88DT Default Routes
db.cables |>
	filter(SrcTag == dev, DstTag == dev) |>
	select(Input = SrcPort, Output = DstPort, Usage) |>
	arrange(Output) |>
	gt() |>
	opt_stylize(style = 3) |>
	sub_missing(missing_text = "-")
```

# Topologies

## Computers

CUMU-G002 / MacOS / ProPresenter

: The Mac Studio that runs ProPresenter. Its outputs are described in @sec-propresenter. Its HDMI output is also fed to a KVM-over-IP encoder so the operator display can be seen elsewhere.

CDWU-0009 / Windows / PowerPoint

: A Windows system with the Windows version of PowerPoint, for guests whose presentation only runs on Windows. Its HDMI output goes into the VideoHub.

CUMU-G001 / MacOS / Companion

: The video computer. It runs the *Companion* software that drives all of the Stream Decks, including the projector power controls, as well as the ATEM software.

```{r comp-inv, results='asis'}
#| label: tbl-comp-top
#| tbl-cap: Computer Inventory
print_inv(c("CUMU-G002", "ZVIU-E004", "ZVIU-E005", "CDWU-0009", "CUMU-G001"), db.inventory) |>
	print_gt_table() |>
	cat()
```

## Projectors

There are three front-of-house laser projectors on the bulkhead and a rear (confidence) projector in the balcony. All four have HDBaseT inputs; the front three also take HDMI from the VideoHub converters.

```{r projtopo, results="asis"}
targets <- c("ZVKU-A001")
ps <- c("2507-0700"
		, "ZVVU-0001"
		, "2604-2401", "2604-2402", "2604-2403"
		, "2601-1304", "2601-1305", "2601-1306")
a <- get_connectivity_diagram(targets, "both", db.inventory, db.cables
							  , types = NULL, label = '"Projection Topology"'
							  , rankdir = "LR", partners = ps)
cat(get_diagram_aux(a))
```

```{r proj-inv, results='asis'}
#| label: tbl-proj-det
#| tbl-cap: Projection Inventory
print_inv(c("2604-2401", "2604-2402", "2604-2403", "2601-1304", "2601-1305", "2601-1306"
			, "ZVVU-0001", "ZVKU-A001", "2507-0700"), db.inventory) |>
	print_gt_table() |>
	cat()
```

Each front projector is also on the network so that the Stream Deck can turn it on and off and freeze or thaw its image.

## Stage Display

The stage display (confidence display) is shown on two devices: the rear projector (ZVVU-0001) fed by HDBaseT from VS-88DT output 4, and the 85in TV in the balcony (2605-0500) fed from VideoHub output 6 through an SDI-to-HDMI converter.

```{r stgdsp-inv, results='asis'}
#| label: tbl-stgdsp-det
#| tbl-cap: Stage Display Inventory
print_inv(c("ZVVU-0001", "2605-0500", "ZVIU-A005"), db.inventory) |>
	print_gt_table() |>
	cat()
```

## Lobby Topology

The TV in the lobby gets the ATEM program: VideoHub output 33 feeds an SDI-to-HDMI converter into VS-88DT input 1, which is routed to HDBaseT output 7. The Stream Deck power button for the lobby TV also forces its input to HDMI 1. HDBaseT is used for this and also requires a converter at the TV to provide the HDMI format.

```{dot top_lobby}
//| fig-width: 4
//| label: fig-top-lobby
//| fig-cap: "Lobby Topology"
//| file: gv/sdv-topology3-lobby.gv
```

```{r gt-topLobby, results='asis'}
#| tbl-cap: Lobby Inventory
#| label: tbl-lob-top
print_inv(c("ZVKU-A001", "ZVIU-A001", "2310-1700"), db.inventory) |>
	print_gt_table() |>
	cat()
```

## Nursery/Toddler Topology

The TV in the nursery gets the same feed as the lobby, from VS-88DT HDBaseT output 8. HDBaseT is used for this and also requires a converter at the TV to provide the HDMI format.

There is an HDMI splitter at the Nursery TV which provides an HDMI feed to the TV in the Toddler room.

Each TV has a remote control.

```{dot }
//| fig-width: 4
//| label: fig-top-nursery
//| fig-cap: "Nursery Topology"
//| file: gv/sdv-topology4-nursery.gv
```

```{r top3, results='asis'}
#| tbl-cap: Nursery Topology Inventory
#| label: tbl-nursery-det
print_inv(c("ZVKU-A001", "ZVIU-A002", "2308-2900", "ZVVU-0002", "ZVVU-0003"), db.inventory) |>
	print_gt_table() |>
	cat()
```

## Library

The TV in the library is fed directly from the VideoHub (output 38) through a BiDirectional SDI/HDMI converter. The default route is the ATEM program.

```{r lib-inv, results='asis'}
#| label: tbl-lib-det
#| tbl-cap: Library Inventory
print_inv(c("2507-0700", "2512-1001", "2601-0600"), db.inventory) |>
	print_gt_table() |>
	cat()
```

# Terminology

```{r terminology, results="asis"}
# A hack - gt doesn't provide a means of line-breaking for pdf. So we create a graphic and then include the graphic.

tab <- get.glossary() |>
	filter(  Topic == "Video" 
		   | Topic == "General"
		   | Term == "Category Cable") |>
	select(Term, Definition, Topic) |>
	arrange(Topic, Term) |>
    gt(groupname_col = "Topic") |>
	opt_stylize(style=3) |>
	fmt_markdown(columns=Definition) |>
	tab_style(
       style = cell_text(weight = "bold"
  				  , size="large")
                  , locations = cells_row_groups() ) |>
	print_gt_table() |>
	cat()
```

{{< include common_trailer.qmd >}}