---
title: "System Design Rack Profiles"
date: last-modified
editor: visual
execute: 
  eval: TRUE
  echo: false
  warning: false
  message: false

format:
  html:
    toc: true
  pdf:
    toc: true
  titlepage-pdf:
    toc: true     

always_allow_html: yes  
---

# Introduction

This documents the rack profiles for the Audio, Video and Lighting systems at UAC.

This is a work in progress and is not complete as a lot of mapping work remains.

```{r packages  }
source('commonPackages.R')
source('commonFunctions.R')
source("commonRackProfile.R")
```

```{r  functions}
gt_rack_summary <- function(df, rack) {
tt <- glue("Overview of Rack : {rack}")
asset <- df |> 
	filter( AssetTag == rack) 

dat <- tribble (
	~Name         , ~Value 
   , "Building"   , asset$Building
   , "Floor"      , asset$Floor
   , "Room"       , asset$Room
   , "Location"   , asset$Location
   , "Description", asset$Desc
   , "Usage"      , asset$Usage
   , "Item Count"
   , df |> filter( Rack == rack ) |> nrow() |> as.character()
)
	
tab <- dat |> 
		gt() |>  
		opt_stylize(style = 5) |>
		tab_header( tt )  
	return(tab)
}

gt_rack_detail <- function(df, rack) {
tt <- glue("Rack Contents: {rack}")
asset <- df |> 
	filter( AssetTag == rack) 

st <- glue("Building {asset$Building}, Floor {asset$Floor}, Room {asset$Room}, Location {asset$Location}")
	
tab <- df |> 
	filter( Rack == rack) |>
	arrange( desc( RackU) ) |>
	select(RackU, AssetTag
		   , Manufacturer, Model
		   , Desc, Usage ) |>
		gt() |>  
		opt_stylize(style = 5) |>
		tab_header( tt, subtitle=st )  
	return(tab)
}
```

```{r get_data}
db.inventory <- get.inventory()  
```

```{r racklist}
racks <- db.inventory |> select(Rack) |> 
	distinct() |> pull()
```

# Racks

```{r gt_racks}
db.inventory |> filter( AssetTag %in% racks) |>
	select(AssetTag
		   , Manufacturer, Model
		   , Desc, Usage 
		   , Building, Room, Location) |>
	arrange(Building, Room,AssetTag ) |> 
	gt() |>  
	opt_stylize(style = 5)
```

# Main Floor

## Amp Room ZAHU-0001

```{r ZAHU-0001}
rack <- 'ZAHU-0001'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory
				  , range = c(31, 55))
plot_rack_profile(rack, db.inventory
				  , range = c(16, 30))
plot_rack_profile(rack, db.inventory
				  , range = c(1, 15))
```

F15 is a brush plate F30 PP

```{r gtZAHU-0001}
gt_rack_detail(db.inventory, rack)
```

## Broadcast Room ZAHU-0003

```{r ZAHU-0003}
rack <- 'ZAHU-0003'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory)
```

F10 Blank F09 Patch F08 Gap F06-7 blank F02-03 Blank F01 Startech RKPW161915

R02 PDU

```{r gtZAHU-0003}
gt_rack_detail(db.inventory, rack)
```

## Stage Rack 2509-1703

```{r 2509-1703}
rack <- '2509-1703'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory)
gt_rack_detail(db.inventory, rack)
```

## Server Room

Yet to be documented

# Balcony

## ZVHU-0002

```{r ZVHU-0002}
rack <- 'ZVHU-0002'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory)

gt_rack_detail(db.inventory, rack)
```

## Baclony Rack 2602-1800

```{r balcony_rack}
rack <- '2602-1800'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory
				  , range = c(21, 42))
plot_rack_profile(rack, db.inventory
				  , range = c(1, 21))
gt_rack_detail(db.inventory, rack)
```

## 2410-0900

```{r 2410-0900}
rack <- '2410-0900'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory
				   )
gt_rack_detail(db.inventory, rack)
```

## ZAHU-0004

```{r ZAHU-0004}
rack <- 'ZAHU-0004'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory
				   )
gt_rack_detail(db.inventory, rack)
```

## ZAHU-0005

```{r ZAHU-0005}
rack <- 'ZAHU-0005'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory
				   )
```

F12 Gemini PL-8 - notag179 ? check sn F11 Shure UA844 ZAIU-B003 F10 - F07 ULXDQ F06 Tascam CD F01 Stuart and related gear

R12 PDU

```{r gtZAHU-0005}
gt_rack_detail(db.inventory, rack)
```

## ZVHU-0001

```{r ZVHU-0001}
rack <- 'ZVHU-0001'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory )
```

F08 STARTech RKPW161915 F10 Sehlf with Decklink 3U

F13 Shelf with 6 MC

Group1: G005,g004,G003

Group 2: ZVIU-A009, ZVIU-A006

Group 3: ZVIU-E001

F14 Gap

F15 - Kramer 2U

F17-18 Gap

F19 Blinds

F20 Furhman PL-8

R04 Shelf for Clearcom 2U

R06 ZLIU-0003

R20 PDU

```{r gtZVHU-0001}
gt_rack_detail(db.inventory, rack)
```

## ZVHU-0002

```{r ZVHU-0002b}
rack <- 'ZVHU-0002'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory  )
```

F01-03 Drawer F04-06 Drawer F07-F09 Drawer F10-F12 Gap F14 Gap F16 Gap

```{r gtZVHU-0002b}
gt_rack_detail(db.inventory, rack)
```

## ZVHU-0003

```{r ZVHU-0003}
rack <- 'ZVHU-0003'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory)
```

F10 Furman PL-8 f08 blank F7 gap

```{r gtZVHU-0003}
gt_rack_detail(db.inventory, rack)
```

## ZAHU-0002

```{r ZAHU-0002}
rack <- 'ZAHU-0002'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory )
```

F1-3 HH09-HH12 F4-6 HH5-8 F7-9 HH1-4 F10-11 BP3-6 F12-13 BP1-2 F14-15 blank F16 blank F17 blank F18-20 blank

```{r gtZAHU-0002}
gt_rack_detail(db.inventory, rack)
```

# Fellowship Hall

## 2401-3000

```{r 2401-3000}
rack <- '2401-3000'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory )
```

```{r gt2401-3000}
gt_rack_detail(db.inventory, rack)
```

# Youth Building

## Rear Desk 2308-0900

```{r 2308-0900 }
rack <- '2308-0900'

gt_rack_summary(db.inventory, rack)
plot_rack_profile(rack, db.inventory)  
```

```{r gt2308-0900}
gt_rack_detail(db.inventory, rack)
```

## Stage 2308-0901

```{r 2308-0901}
rack <- '2308-0901'
gt_rack_summary(db.inventory, rack)

plot_rack_profile(rack, db.inventory)
```

```{r gt2308-0901}
gt_rack_detail(db.inventory, rack)
```

# Reference Chart of U Heights

```{r tofrh}

u_inch =1.75
u_mm = 44.45

num_u <- seq(0, 41)

df_u <- tibble(
	U = num_u+1,
	Height_inch = num_u * u_inch,
	Height_mm = num_u * u_mm
)


df <- df_u
library(data.table)  # Or use base R subsetting
n_rows <- nrow(df)
chunk_size <- ceiling(n_rows / 3)

df1 <- df[1:chunk_size, ]
df2 <- df[(chunk_size+1):(2*chunk_size), ]
df3 <- df[(2*chunk_size+1):n_rows, ]

wide_df <- cbind(df1, df2, df3)
names(wide_df) <- c(names(df1), paste0(names(df2), "_2"), paste0(names(df3), "_3"))

# Now format as gt
wide_df |>
  gt() |>
	cols_label(
   U = "U", Height_inch = "Height (in)", Height_mm = "Height (mm)",
   U_2 = "U", Height_inch_2 = "Height (in)", Height_mm_2 = "Height (mm)",
   U_3 = "U", Height_inch_3 = "Height (in)", Height_mm_3 = "Height (mm)"
  )  |>
  tab_header("Table of Rack Heights")
```
