---
title: "System Design - Projection"
 
execute: 
  eval: true
  echo: false
  warning: false
  message: false
format:
  html:
    toc: true 
  pdf:
    toc: true
  titlepage-pdf:
    toc: true
always_allow_html: yes
---

```{r packages}
source("commonPackages.R")

require(formattable)
```

```{r functions}
source("commonFunctions.R")
```

```{r data }
NetworkInventory <- get.network()
assets           <- get.assets()
further          <- get.further() 
```

# Introduction

This document provides key technical documentation for the video subsystems at UAC. @fig-overview provides a simplified overview of the major components in the system. Subsequent sections provide more detail.

```{dot overview}
//| fig-width: 4
//| label: fig-overview
//| fig-cap: "Projection Overview"
//| file: gv/sdv-topology0-overview.gv
```

# ProPresenter {#sec-propresenter}

ProPresenter generates 7 physical video outputs, and those are five of the 8 inputs into the video matrix. It also has one [NDI](https://sites.google.com/view/buzz-sparky-and-flip/articles/video/ndi-overview) output which is a network interface.

* Three outputs are the triple wide video outputs which are normally routed directly to the front of house (FoH) projectors. This is via the Decklink.

* Two outputs are specifically to feed the ATEM video mixer. This pair of feeds are called a *Key* and *Fill.* The *Fill* looks like a normal single wide image. The *Key* is a mask which the ATEM uses to select which parts of the *Fill* are to be displayed. An area on the *Key* which is white is displayed. An area which is black, is transparent. Areas which a grey are semi-transparent, the darker the grey, the more transparent is that portion.

* One output is the stage display via the Decklink.

* An HDMI output which can be used when the decklink outputs are not appropriate (eg: Powerpoint and DVDs).  

* The NDI output is a copy of the stage display that is sent out over the network and provides key status information to the audio engineer running the livestream.  

## Decklink

The Decklink card is connected to the computer via a USBC/Thunderbolt cable. It is configured using a program called *Desktop Video*. It can provide up to 8 video outputs, but we configure it for 6 outputs.
 
The Decklink outputs are special purpose outputs which are not recognized by the Mac Operating system. So you cannot do things like DVD playback or Safari Web Page display on those outputs. You can use the hdmi output for that, with corresponding routing changes on the video matrix.

::: callout-note
See the document *deepdive_displaying_a_web_page_within_pp7.docx* for instructions on how to display a browser webpage via ProPresenter.
:::

::: {#fig-decklink-tw-sd layout-ncol=2}
```{dot pp_and_decklink-tw}
//| fig-cap: (a) Triplewide
//| file: gv/sdv-decklink_ProPresenter-tw.gv
```
```{dot pp_and_decklink-sd}
//| fig-cap: (b) Stage Display
//| file: gv/sdv-decklink_ProPresenter-sd.gv
//| 
```
ProPresenter and Decklink Configurations
:::

::: {#fig-decklink-kf-in layout-ncol=2}
```{dot pp_and_decklink-kf}
//| fig-cap: (a) Key and Fill
//| file: gv/sdv-decklink_ProPresenter-kf.gv
```
```{dot pp_and_decklink-in}
//| fig-cap: (b) Inputs
//| file: gv/sdv-decklink_ProPresenter-in.gv
```
ProPresenter and Decklink Configurations
:::

:::callout-note
When using the video input into ProPresenter from the ATEM, the video is delayed about 20ms. This may be noticeable in some circumstances; lip synchronization on a tight shot vocal or a drummer might be noticeable to the audience.  
:::

# Video Matrix

The main job of a video matrix is to take multiple video sources, such as cameras or computers, and direct their video signals to different destinations, like TVs, projectors, or recording devices.

Our video matrix is a Kramer VS-88DT which is an 8x8 matrix and can handle HDMI inputs and both HDMI and [HDBaseT](https://en.wikipedia.org/wiki/HDBaseT) formats. Any of the 8 inputs can be routed to any of the 8 outputs (or several outputs).

It can be controlled via the buttons on the front panel or from its built in web page.


```{r psi, results='asis'}
#| label: fig-matrix-inputs
#| fig-cap: Matrix Inputs

psi <- tribble(
~Input, ~Usage, ~Comment,
1,
"TW A",
"The left most third of the ProPresenter triple wide display from the decklink (sdi4)",

2, 
"TW B",
"The centre third of the ProPresenter triple wide display from the decklink (sdi6)",

3,
"TW C",
"The right most third of the ProPresenter triple wide display from the decklink (sdi8)",

4,
"Stage Display",
"The stage display from ProPresenter via the decklink (sdi3)",

5,
"CDWU-0009",
"Source is Windows machine which can run Powerpoint and OBS",

6,
"ATEM Program",
"The Program feed from the ATEM, a copy of what is also streamed",

7, 
"ATEM Auxillary",
"Auxillary feed from the ATEM video mixer. Not usually used but could be used to source different video content from the ATEM. For example a static graphic for the centre projector.",

8,
"CDMU-A001 HDMI",
"The HDMI Video from CDMU-A001. This would be used when a system display is required.")

tab <- psi |> 
	gt() |>
	opt_stylize(style = 3) |>
 	tab_header("Video Matrix Inputs" ) |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=Input)
	)
# 	) |>
#   cols_width(
#     Comment ~ pct(70),
#     Usage   ~ pct(15),
#     Input  ~ pct(15)
#   )

print_gt_table(tab) |> cat()
```

```{r pso, results='asis'}
#| label: fig-matrix-outputs
#| fig-cap: Matrix Outputs
 
pso <- tribble(
~Output, ~Type, ~Usage, ~Comment,
"1", "HDBaseT", 
"East Projector",
"Front of House projector - Stage Right / East wall.",

"2",  "HDBaseT",
"Centre Projector",
"Front of House projector - Stage Centre / South wall.",

"3",  "HDBaseT",
"West Projector",
"Front of House projector - Stage Left / West wall.",

"4", "HDBaseT", 
"Rear Projector",
"Projector which projects onto the rear wall in balcony. Lyrics for singers, etc.",

"5", "HDMI" ,
"Feed to ATEM","Secondary feed to Video Mixer. Destination is to the video mixer so projected content can be mixed with camera – Picture-in-Picture, etc.",

"6", NA,
"unused","unused",

"7",  "HDBaseT",
"Lobby","Feed to the Lobby TV.",


"8" ,  "HDBaseT",
"Nursery", "Feed to the Nursery TV."
)

tab <- pso |> 
	gt() |>
	opt_stylize(style = 3) |>
	tab_header("Video Matrix Outputs" ) |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=Output)
	) |>
	tab_footnote("A potential future output would be an audio feed to the Audio mix console, or a decklink input.", 
				 locations=cells_body(
				 	columns=Comment , 
				 	rows= Output==6)) 
# |>
#   cols_width(
#     Comment ~ pct(55),
#     Usage   ~ pct(15),
#     Type    ~ pct(15),
#     Output  ~ pct(15)
#   ) |>
# 	tab_options(table.width=pct(100))
print_gt_table(tab) |> cat()
```

## Video Matrix Configurations

:::{.calloiut-note}
Would this be better located in the Video Operations?
:::

The current matrix routing can be queried and changed using either the webpage or the front panel.

The LCD display on the front of the unit report the current routing topology. The Output row shows the number of the input which is selected for that output. A '0' indicates no source has been selected. Here are a few sample configurations. The detailed settings are in the table @tbl-vmsc that follows.

Full_TW
: Use this when you want triple wide capability. 

Centre_ATEM_AUX
: Use this when you want to use the ATEM Aux output as a source. An common example of this is a static graphic on the centre screen. This could also be done using the Full_TW with a prop on the centre screen which is never cleared.

Centre_ATEM_Prg
: Use this when you want live camera on the centre screen. 

All_three_HDMI
: Use this when you want the conputers HDMI output to be routed to the projectors. For example, playing a DVD. It could also be a fallback if there is a problem with the triple wide system.

```{r samp_cfg}
samp_cfg <- tribble(
~Num,
~Output, ~Full_TW, ~Centre_ATEM_AUX, ~Centre_ATEM_Prg, ~All_three_HDMI,
1, "ProjEast",	1,	1,	1,	8,
2, "ProjCent",	2,	7,	6,	8,
3, "ProjWest",	3,	3,	3,	8,
4, "RearProj",	4,	4,	4,	4,
5, "ATEM In 1", 	8,	8,	8,	8,
6, "not used",	4,	4,	4,	4,
7, "Lobby"  ,	6,	6,	6,	6,
8, "Nursery",	6,	6,	6,	6
)
```

```{r tbl-vmsc}
#| label: tbl-vmsc
#| tbl-cap: Video Matrix Sample Configurations
samp_cfg |> 
	gt() |>
	opt_stylize(style = 3) |>
	tab_header("Video Matrix Sample Configurations" 
			  , subtitle="Settings which are differnt from Full_TW are in Yellow." ) |>
    tab_style(  
      style = list(  cell_fill(color = "yellow")  ),
      locations = cells_body(columns = Centre_ATEM_AUX,
      					     rows = Num == 2   )
	) |>
    tab_style(  
      style = list(  cell_fill(color = "yellow")  ),
      locations = cells_body(columns = Centre_ATEM_Prg,
      					     rows = Num == 2   )
	) |>
    tab_style(  
      style = list(  cell_fill(color = "yellow")  ),
      locations = cells_body(columns = All_three_HDMI,
      					     rows = Num %in% c(1,2,3)   )
	)
```

# Topologies

There are a lot of components to the system. One big diagram is daunting. It has been broken down into smaller portions to be more consumable.

## Computer Topology

There are three computers in the system (@fig-comp-top):

CDMU-A001 MacOS / ProPresenter

: This system runs ProPresenter and has a built in operator display and a number of other outputs, see @sec-propresenter for details. It also has Powerpoint for Mac and Keynote installed.

CUMU-G001 MacOS / ATEM - OBS

: This system runs the ATEM switcher software, and OBS (for distrbution of the ATEM program output over the network) and can also run things like Skype. It has a USBC-HDMI adapter that is *not* currently connected to Input 3 of the video mixer.

CDWU-0009 Windows / PowerPoint

: The windows system runs the windowns version of PowerPoint and has a dual output video card. One is used for the operator display, and the second for presentation.  This can be used if a guest has a PowerPoint that can only be run on Windows.

```{dot dot_top_comp}
//| fig-width: 4
//| label: fig-top-comp
//| fig-cap: "Computer Topology"
//| file: gv/sdv-topology1-computer.gv
```

```{r gt_topComp}
#| fig-cap: Computer Inventory
#| label: fig-comp-top
selected.at <- c(
                "CDWU-0009", "CDMU-A001"
              , "CUMU-G001", "CUMU-E001"
              , "ZVKU-A001",  "ZVKU-A003" 
              , "ZVIU-A004", "ZVIU-E004") 

assets |>
   filter( AssetTag %in% selected.at) |> 
    select(AssetTag, Manufacturer, Model, Desc ) |>
    arrange( AssetTag ) |> 
	gt() |>
	opt_stylize(style = 3) |>
	tab_header("Device Details" ) |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=AssetTag)
	) 
```


## Projection Topology

Long distance signal transmission is achieved using Cat5e or Cat6 cabling. An industry standard solution called HDBaseT is used.  All of our projectors have HDBaseT connections built in.  

```{dot top_proj}
//| fig-width: 4
//| label: fig-top-proj
//| fig-cap: "Projector Topology"
//| file: gv/sdv-topology2-projection.gv
```

```{r}
#| fig-cap: Projection Topology Inventory
#| label: fig-proj-det
selected.at <- c(
              "ZVKU-A001", 
              "ZVVU-0001",
              "ZVVU-A001", "ZVVU-A002", "ZVVU-A003" 
              )

assets |>
   filter( AssetTag %in% selected.at) |> 
    select(AssetTag, Manufacturer, Model, Desc ) |>
    arrange( AssetTag ) |> 
	gt() |>
	opt_stylize(style = 3) |>
	tab_header("Device Details" ) |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=AssetTag)
	) 

```

## Lobby Topology

The TV in the lobby gets its content from the video matrix. For the main service it should get its feed from the video mixer program output. HDBaseT is used for this and also requires a converter at the TV to provide the HDMI format.

```{dot top_lobby}
//| fig-width: 4
//| label: fig-top-lobby
//| fig-cap: "Lobby Topology"
//| file: gv/sdv-topology3-lobby.gv
```

```{r gt-topLobby}
#| fig-cap: Lobby Inventory
#| label: fig-lob-top

selected.at <- c(
              "ZVKU-A001" , "ZVIU-A002"
              , "2310-1700"
              ) 

assets  |>
   filter( AssetTag %in% selected.at) |> 
    select(AssetTag, Manufacturer, Model, Desc ) |>
    arrange( AssetTag ) |> 
	gt() |>
	opt_stylize(style = 3) |>
	tab_header("Device Details" ) |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=AssetTag)
	) 
```

## Nursery/Toddler Topology

The TV in the nursery gets its content from the video matrix. For the main service it should get its feed from the video mixer program output. HDBaseT is used for this and also requires a converter at the TV to provide the HDMI format.

There is an HDMI splitter at the Nursery TV which provides an HDMI feed to the TV in the Toddler room.

Each TV has a remote control.

```{dot top_nursery}
//| fig-width: 4
//| label: fig-top-nursery
//| fig-cap: "Nursery Topology"
//| file: gv/sdv-topology4-nursery.gv
```

```{r top3}
#| fig-cap: Nursery Topology Inventoru
#| label: fig-nursery-det

selected.at <- c(
              "ZVKU-A001",  
              "ZVVU-0002", "2308-2900",
              "ZVIU-A002", "ZVVU-0003"
              )  

assets |>
   filter( AssetTag %in% selected.at) |> 
    select(AssetTag, Manufacturer, Model, Desc ) |>
    arrange( AssetTag ) |> 
	gt() |>
	opt_stylize(style = 3) |>
	tab_header("Device Details" ) |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=AssetTag)
	) 
```

## Recording Topology

The recording topology is quite complex and so it is broken up into pieces.

### Inputs

See @fig-rec-inputs

```{dot top_rec-inputs}
//| fig-width: 4
//| label: fig-rec-inputs
//| fig-cap: "Recording Inputs Topology"
//| file: gv/sdv-topology5-rec-inputs.gv
```

### Outputs

See @fig-rec-outputs

```{dot top_rec-outputs}
//| fig-width: 4
//| label: fig-rec-outputs
//| fig-cap: "Recording Outputs Topology"
//| file: gv/sdv-topology5-rec-outputs.gv
```

### Web Presenter

See @fig-rec-wp and @fig-wp-det

```{dot top_rec-wp}
//| fig-width: 4
//| label: fig-rec-wp
//| fig-cap: "WebPresenter Topology"
//| file: gv/sdv-topology6-rec-wp.gv
```

```{r}
#| fig-cap: WebPresenter Details
#| cap-location: bottom
#| label: fig-wp-det
selected.at <- c(
              "ZVKU-A003", 
              "ZVRU-A001", "ZVRU-A002",
              "ZVIU-A004",
              "CUMU-G001"
              , "ZVIU-D001"
              ) 

assets|>
   filter( AssetTag %in% selected.at) |> 
    select(AssetTag, Manufacturer, Model, Desc ) |>
    arrange( AssetTag ) |> 
	gt() |>
	opt_stylize(style = 3) |>
	tab_header("Device Details" ) |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=AssetTag)
	) 
```

The details of the network configuration are not shown. See the Network design document for technically accurate descriptions.


# Network Details

See @fig-net-det

```{r gt-net-details, results="asis", fig.id=TRUE }
#| fig-cap: Network Details
#| cap-location: bottom
#| label: fig-net-det
NetworkInventory |> 
 left_join(assets) |>
 filter(Category=="Video") |> 
 filter(Building == "Main") |>
 select(AssetTag, Location, Usage, Device, MAC, IP, URL, Notes) |>
 arrange(AssetTag) |>
	gt() |>
	opt_stylize(style = 3) |>
	tab_header("Network Device Details" ) |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=AssetTag)
	)  |>
 print_gt_table() |> cat()	
```

# Video Equipment Inventory

```{r inventory }
#| fig-cap: Asset Details
#| cap-location: bottom
#| label: fig-asset-det
 
cs = c("AssetTag", "Qty"  ,
  "Manufacturer" ,
  "Model"  , 
  "Qty",
  "Location"  ,
  "Type" ,
  "Desc"     )

Video_Inventory <- assets |>  
          filter( Category=="Video" 
          		, InService== "Y"
          		, Building == "Main"
          		, Floor != "Basement") 
nr <- nrow(Video_Inventory)

Video_Inventory |>
   #filter( AssetTag %in% selected.at) |> 
    select(AssetTag, Location, Manufacturer, Model, Desc ) |>
    arrange( AssetTag ) |> 
	gt() |>
	opt_stylize(style = 3) |>
	tab_header(glue("Video Device Details n={nr} ") ) |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=AssetTag)
	) 
```

# Terminology

```{r terminology, results="asis"}
# A hack - gt doesn't provide a means of line-breaking for pdf. So we create a graphic and then include the graphic.

tab <- get.glossary() |>
	filter(  Topic == "Video" 
		   | Topic == "General"
		   | Term == "Category Cable") |>
	select(Term, Definition, Topic) |>
	arrange(Topic, Term) |>
    gt(groupname_col = "Topic") |>
	opt_stylize(style=3) |>
	fmt_markdown(columns=Definition) |>
	tab_style(
       style = cell_text(weight = "bold"
  				  , size="large")
                  , locations = cells_row_groups() ) |>
	print_gt_table() |>
	cat()
```

{{< include common_trailer.qmd >}}