---
title: "System Design - Video"
author: "Terry Doner"
date: "`r format(Sys.time(), '%B %d %Y')`"
output: 
    html_document:
        toc: true
---

```{r options, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
options(knitr.table.format = "html") # latex for pdf 
```

```{r packages }
require(readr)
require(dplyr)
require(readxl)
require(knitr)
require(kableExtra)
```

```{r getdata}
path <-"~/Documents/UACTech/SystemDocumentation"
inventoryfile <- "TechInventory.xlsx"
fname <- paste(path, inventoryfile, sep="/")

ct <- c(  "text", "text",  "numeric", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "date", "text", "text", "numeric", "text", "numeric", "numeric", "numeric"     
)

Tech_Inventory <- read_excel(fname, sheet = "TechInventory", col_types=ct)
NetworkInventory <- read_excel(fname, sheet = "Network")
```

```{r functions}
source("./commonFunctions.R") 
```

## Introduction
This document provides key technical documentation for the video subsystems at UAC. This diagram provides an overview of the major components and leaves out some details.

Frequently throughout this document there will be a diagram or description of some aspect of the installation and following that a listing of the mentioned equipment which provide more detail on the mentioned assets.

```{r}
DiagrammeR::grViz("sdv-topology0-overview.gv")
```

## Presentation Switcher
The unit is a Kramer VS-88DT which is an 8x8 matrix and can handle both HDMI and HDBaseT formats.

It has 8 inputs and 8 outputs. It can be controlled via the buttons on the front panel or from it’s built in web page.

>TODO: review details of the input list

```{r}
psi <- tribble(
  ~Input, ~Usage,       ~Comment,

1, "TW Left",       "Tripple wide input Left (from PP via fx4)" ,
2, "TW Centre",     "Tripple wide input Centre (from PP via fx4)", 
3, "TW Right",      "Tripple wide input Right (from PP via fx4)",
4, "Confidence",    "Stage display from PP. Meant for the rear projector.",
5, "VMIX Program",  "Program output from Video Mixer",
6, "VMIX AUX",      "Aux output from Video Mixer.",
7, "CDWU-0009",     "Video Output from Windows machine. Usually used from OBS.",
8, "Lighting Console", "Could also be used for a guest machine." 
)

pso <- tribble(
    ~Output, ~Usage,       ~Comment,
1,
"FoH Prj Left", 
"Front of House projector - East wall",
2, 
"FoH Prj Centre",
"Front of House projector - South wall",
3, 
"FoH Prj Right",
"Front of House projector - West wall",
4,
"Confidence",
"Rear Balcony Projector (stage display from PP). Lyrics for singers, etc.",
5,
"Video Mix 1",
"Video mixer input 1",
6,
"Video Mix 3",
"Video mixer input 3",
7,
"Lobby",
"Feed to the Lobby TV.",
8,
"Nursery",
"Feed to the Nursery TV."   
)
```

###Inputs

```{r}
psi %>% 
  kable() %>%
    column_spec( 1,  bold = TRUE ) %>%
    kable_styling("striped", full_width = TRUE)
```

###Outputs
```{r}
pso %>% 
  kable() %>%
    column_spec( 1,  bold = TRUE ) %>%
    kable_styling("striped", full_width = TRUE)
```

###Configurations
The LCD display on the front of the unit report the current routing topology. The Output row shows the number of the input which is selected for that output. A '0' indicated no source has been selected. Here are two sample configurations.  

#### Normal Service Switcher Configuration 
The display should look like:

|Input |1|2|3|4|5|6|7|8|
|-|:-:|:-:|:-:|:-:|:-:|:-:|:-:|:-:|
|Output|1|0|0|4|1|1|1|0|

```{r normal}
DiagrammeR::grViz("sdv-PSnormal.gv", height=300)
```

#### Camera Switcher Configuration  
The display should look like:

|Input |1|2|3|4|5|6|7|8|
|-|:-:|:-:|:-:|:-:|:-:|:-:|:-:|:-:|
|Output|6|0|0|4|6|0|6|0|

```{r camera}
DiagrammeR::grViz("sdv-PScamera.gv", height=300)
```

## Topologies
There are a lot of components to the system. One big diagram is daunting. It has been broken down into smaller portions to be more consumable. 

### Computer Topology

There are three computers in the system:

CDWU-0009 Windows / OBS / Mediashout
: The windows system runs OBS or Mediashout and has a dual output video card. One is used for the operator display, and the second for presentation. It also has Powerpoint for Windows installed.

CDMU-A001 MacOS / ProPresenter
: This system runs ProPresenter and has a built in operator display, and a displayport output to the datapath video processor which split the output to three separate video signals for the front projectors, and a separate video output that drives the rear confidence montitor. It also has Powerpoint for Mac and Keynote installed.

CDMU-A002 MacOS / ATEM - OBS
: This system runs the ATEM switcher software, and OBS (for streaming) and can also run things like Skype. It has a USBC-HDMI adapter that is direct connected to Input 2 of the video mixer.
  
```{r top1}
DiagrammeR::grViz("sdv-topology1-computer.gv")
print_inv(c("CDWU-0009","CDMU-A001","CDMU-A002"), Tech_Inventory)
```

### Projection Topology
There are four projectors in the auditorium, three FoH and one at the rear for confidence. Thet are all feed an hdmi signal via HDBaseT (Over Cat6).

```{r top2}
DiagrammeR::grViz("sdv-topology2-projection.gv")
print_inv(c("ZVKU-A001","ZVVU-A001", "ZVVU-A002", "ZVVU-A003", "ZVVU-0001"),                    Tech_Inventory)
```

###Lobby Topology
The TV in the lobby gets its content from the presentation Switcher. For the main service it should get its feed from the video mixer program output.

```{r l132}
DiagrammeR::grViz("sdv-topology3-lobby.gv")

print_inv(c("ZVIU-A002", "ZVKU-A001", "ZVVU-0003"), Tech_Inventory)
```

### Nursery Topology
The TV in the nursery gets its content from the presentation Switcher. For the main service it should get its feed from the video mixer program output.

Alternately it can be switched to the Bluray player.
```{r top3}
DiagrammeR::grViz("sdv-topology4-nursery.gv")
print_inv(c("ZVIU-A001", "ZVKU-A001", "ZVPU-0001", "ZVVU-0002"), Tech_Inventory)
```

The TV and the Bluray player each have a remote control.

### Recording Topology
The recording topology is quite complex and so it is broken up into peices.

####Inputs

```{r top5a}
DiagrammeR::grViz("sdv-topology5-rec-inputs.gv", height=350)
```

####Outputs
```{r top5b}
DiagrammeR::grViz("sdv-topology5-rec-outputs.gv", height=350)
```

####Web Presenter
There are some details on the signal path between the Video Mixer and the Web Presenter that need to be documented.

```{r topwp}
DiagrammeR::grViz("sdv-topology6-rec-wp.gv", height=350)
```

```{r}
print_inv(c("ZVKU-A004", "ZVKU-A001", "CDMU-A002", "ZVCU-A001",
           "ZVCU-A002", "ZVCU-A003", "ZVKU-A003",
           "ZVRU-A001", "ZVRU-A002", "ZVIU-A004"), Tech_Inventory)
```

# Network Details

```{r} 
NetworkInventory %>% 
filter(Category=="Video") %>% 
select(Location, Usage, Device, MAC, IP, URL, Notes) %>%
kable() %>%
    column_spec( 1,  bold = TRUE ) %>%
    kable_styling("striped", full_width = TRUE)
```

# Video Equipment Inventory

```{r inventory, echo=FALSE, asis=TRUE}

cs = c("Qty"  ,
  "Manufacturer" ,
  "Model"  , 
  "Qty",
  "Location"  ,
  "Type" ,
  "Desc"     )

Video_Inventory <- Tech_Inventory %>%  
          filter( Category=="Video" , InService== "Y") %>%  
          dplyr::select(one_of(cs))   

knitr::kable(Video_Inventory  )  %>%
    column_spec( 1,  bold = TRUE ) %>%
    kable_styling("striped", full_width = TRUE)
```

[Back to top](#top)

`r knit_child('FurtherInformation.Rmd', quiet=TRUE)`

[Back to top](#top)

# Document Source
This document is compiled by merging text and data together using rmarkdown. The source is found here `r getwd()` / `r knitr::current_input()`.