---
title: "System Design Youth"
date: last-modified
editor: visual
execute: 
  eval: TRUE
  echo: false
  warning: false
  message: false

format:
  html:
    toc: true
  pdf:
    toc: true
  titlepage-pdf:
    toc: true     

always_allow_html: yes  
---

# Introduction

This is a detailed design report for the Audio and Video systems in the Youth Building. This documents is not complete as a lot of mapping work remains.

Notes for future updates.

-   rear rack tag 0812 - or not
-   front rack tag 0813 - or not
-   I have a note that suggest 2308-0011 is a cable into the audio interface 2308-0008
-   Need to remove dead gear
-   Change EQ from Peavey to AART

```{r packages_functions }
source('commonPackages.R')
source('commonFunctions.R')
source('commonDiagram.R')
```

```{r get_data}
inventory <- get.inventory()  
cables <- get.cables()
```

# Audio Inputs Diagram

::: {#fig-audio-inputs .cell-output-display}
```{r audio_inputs, results="asis"}
label <- "'Audio inputs'"

targets <- c('2308-0906', 'CDWU-A002', '2308-0914', "2308-0008"
			  ,'ZAKU-A001'
			  , "RearGuest"
			 ,"2310-2500", "2309-2503", "2309-2504") 
xd <- c("youthswitch", "2308-0902", "2308-0002", "VMNU-0029", 
		"2308-0006", "2308-0008", "d228", "d229", "d227", "b236"
		,"2308-0908","2308-0911","2308-0903")
dot_code <- get_diagram(targets, inventory, cables
						, label=label , exc_dev=xd )
out_str <- get_diagram_aux(dot_code)
cat(out_str)

```

Audio Inputs
:::

# Audio Outputs Diagram

As of 2023-11-04 Amplifier '2308-0912' and speaker "2311-0206" were noit connected to anything.

::: {#fig-audio-outputs .cell-output-display}
```{r audio_out, results="asis" }
targets <- c(  '2308-0008', '2308-0913', '2308-0911'
			   #, 'ZAKU-A001'
			, '2308-0910', '2308-0909', '2308-0908', '2308-0904', '2308-0903'
			, '2308-0902' , '2308-1000'
			, "2311-0200",  "2311-0201", "2311-0202"
			, "2311-0204",  "2311-0205", "2311-0206", "2311-0207"
			, '2308-0912', "2311-0206" # these two were disconnected asof 2023-11-04
			)

label <- "'Audio Outputs'"
xd <- c('CDWU-A002')

dot_code <- get_diagram(targets, inventory, cables, label=label, exc_dev=xd)
out_str <- get_diagram_aux(dot_code)
#dot_code |> clipr::write_clip()
cat(out_str)
#
```

Audio Outputs
:::

```{r temp}
x <-'2310-2500'
cables |> 
	filter(SrcTag == x | DstTag== x | str_detect(Tag, x)) |> 
	select(-Invoice, -GraphFormula, -`Labelled?`) |>
	arrange(SrcTag, DstTag) |>
	gt() |> 
	opt_stylize(style=3) |>
	tab_header("Snake Connected Cables")
```

```{dot}
//| label: fig-sdy-audio-outputs4
//| fig-cap: "Audio system simplified"
//| file: ./gv/sdy-audio-outputs4.gv
```

# Video System Diagram

::: {#fig-video-system .cell-output-display}
```{r video_digram, results="asis" }
targets <- c(   '2308-0002'
, '2308-0003'  
, "2309-1600", "2309-1601")
 
xd <- c('youthswitch')
dot_code <- get_diagram(targets, inventory, cables
						, label="'Video System'"
						, exc_dev=xd)
out_str <- get_diagram_aux(dot_code)
cat(out_str)
```

Video System
:::

{{< pagebreak >}}

# Network Diagram

::: {#fig-network .cell-output-display}
```{r network_digram, results="asis"}
targets <- c( "youthswitch", 
"NRPU-0001"
,"NAPU-B002")
 
dot_code <- get_diagram(targets, inventory, cables, label="'Network System'")
out_str <- get_diagram_aux(dot_code)
cat(out_str)
```

Network
:::

{{< pagebreak >}}

# Audio Inventory

```{r audio_inventory}
#| label: tbl-audio_inventory
#| tbl-cap: Audio Inventory
#| tbl-cap-location: bottom

asset_items <- inventory |>
	filter(Category == 'Audio'
		   & Building == 'Portable' 
		   & Disposition == 'N') |> 
	filter(!is.na(Building) ) |>
	arrange(AssetTag) |>
	select(AssetTag, SN, Manufacturer, Model, Type, Location, Desc) 

nr <- nrow(asset_items)
mhdr <- glue("Installed Audio Devices in the Youth Building")
shdr <- glue("n={nr}")

asset_items |>
	gt() |>
			opt_stylize(style = 3) |>
	tab_header( glue("Audio Inventory ")
			   
			  )   |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=AssetTag)
	) |>
	tab_header(mhdr, subtitle = shdr) |>
	sub_missing(missing_text="")
```

```{r audio_cables}

cable_items <- cables |>
	filter(SrcTag %in% asset_items$AssetTag | DstTag %in% asset_items$AssetTag) |>
	filter(!is.na(SrcTag) & !is.na(DstTag))

nr <- nrow(cable_items)
mhdr <- glue("Installed Audio Cables in the Youth")
shdr <- glue("n={nr}")

cable_items |>
	arrange(Tag) |>
	select(Tag, SrcTag, SrcPort, DstTag, DstPort, Type, Usage, Notes) |>
	gt() |>
	opt_stylize(style=3) |>
	tab_header(mhdr, subtitle = shdr) |>
	sub_missing(missing_text="")

```

{{< pagebreak >}}

# Video Inventory

```{r video_inventory}
#| label: tbl-video_inventory
#| tbl-cap: Video Inventory
#| tbl-cap-location: bottom

asset_items <- inventory |>
	filter(Category == 'Video'
		   & Building == 'Portable' 
		   & Disposition == 'N') |> 
	filter(!is.na(Building) ) |>
	select(AssetTag, SN, Manufacturer, Model, Type, Desc) 

nr <- nrow(cable_items)
mhdr <- glue("Installed Video Devices in the Youth")
shdr <- glue("n={nr}") 

asset_items |>
	gt() |>
			opt_stylize(style = 3) |>
	tab_header( glue("Video Inventory ")
			   
			  )   |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=AssetTag)
	)
```

```{r video_cables}
cable_items <- cables |>
	filter(SrcTag %in% asset_items$AssetTag | DstTag %in% asset_items$AssetTag) |>
	filter(!is.na(SrcTag) & !is.na(DstTag))

nr <- nrow(cable_items)
mhdr <- glue("Installed Audio Cables in the Youth")
shdr <- glue("n={nr}")

cable_items |>
	arrange(Tag) |>
	select(Tag, SrcTag, SrcPort, DstTag, DstPort, Type, Usage, Notes) |>
	gt() |>
	opt_stylize(style=3) |>
	tab_header(mhdr, subtitle = shdr) |>
	sub_missing(missing_text="")
```

{{< pagebreak >}}

# Network Inventory

```{r net_inventory}
#| label: tbl-net_inventory
#| tbl-cap: Network Inventory

asset_items <- inventory |>
	filter((Category == 'Network'
		   & Building == 'Portable' 
		   & Disposition == 'N' ) 
		   | (AssetTag == "CDWU-A002" | AssetTag == "2308-0003") 
		   ) |> 
	filter(!is.na(Building) ) |>
	arrange(AssetTag) |>
	select(AssetTag, SN, Manufacturer, Model, Type, Location, Desc) 

nr <- nrow(asset_items)
mhdr <- glue("Installed Network Devices in the Youth Building")
shdr <- glue("n={nr}")

asset_items |>
	gt() |>
			opt_stylize(style = 3) |>
	tab_header( mhdr, subtitle=shdr )   |>
	tab_style(
		style=list( cell_text(weight = "bold") ),
		locations=cells_body(columns=AssetTag)
	) |>
	tab_header(mhdr, subtitle = shdr) |>
	sub_missing(missing_text="")
```

```{r net_cables}
cable_items <- cables |>
	filter(SrcTag %in% asset_items$AssetTag | DstTag %in% asset_items$AssetTag) |>
	filter(!is.na(SrcTag) & !is.na(DstTag))

nr <- nrow(cable_items)
mhdr <- glue("Installed Network Cables in the Youth")
shdr <- glue("n={nr}")

cable_items |>
	arrange(Tag) |>
	select(Tag, SrcTag, SrcPort, DstTag, DstPort, Type, Usage, Notes) |>
	gt() |>
	opt_stylize(style=3) |>
	tab_header(mhdr, subtitle = shdr) |>
	sub_missing(missing_text="")

```
