---
title: "System Design - Video"
execute: 
  eval: true
  echo: false
  warning: false
  message: false
format:
  html:
    toc: true
  pdf:
     toc: true
  titlepage-pdf:
    toc: true
    include-in-header: 
      text: |
        \usepackage{graphicx}
   
always_allow_html: yes
---

```{r packages }
source('./commonPackages.R')
```

```{r functions}
source("./commonFunctions.R")
source("./commonDiagram.R")
source("./commonDiagramConnectivity.R")
```

```{r getdata}
db.inventory <- get.inventory()
db.assets    <- get.assets() 
db.cables    <- get.cables()
 
network.data   <- get.network()
further        <- get.further()
```

# Introduction
This document provides key technical documentation for the video recording and broadcasting subsystems at UAC. This diagram (@fig-video-overview) provides an overview of the major components and in doing so leaves out some details.

```{dot   }
//| fig-width: 4
//| label: fig-video-overview
//| fig-cap: "Video system overview."
//| file: gv/sdv-topology0-overview.gv
```

Frequently throughout this document there will be a diagram or description of some aspect of the installation and following that a listing of the mentioned equipment which provide more detail on the mentioned assets.

Every significant inventory item is to have an asset tag - an actual label attached to the device. For the AV gear these tags start with a Z or in the format of yymm-ddxx. For example ZVKU-A001 is the asset tag of the Kramer video matrix. Cables also have a tag in the format yymm-ddxx. yymm-ddxx represents the year, month, and date followed by a sequence number when the item was tagged.

# Video Matrix

The main job of a video matrix is to take multiple video sources, such as cameras or computers, and direct their video signals to different destinations, like TVs, projectors, or recording devices.

We currently have two video matrix devices. The older one ("ZVKU-A001") is based on HDBaseT, and the newer one ("2507-0700") is based on SDI.

```{r vhdiag, results="asis",eval=FALSE}

targets_v <- c( "2507-0700" 
			 ) 

xd <- c(   "CDWU-A001" # FH Computer
		 , "NAHU-B008" #FH WAP
		) 

label <- NA

dot_code <- get_diagram(targets_v
						, db.inventory, db.cables
						, label=label , exc_dev=xd )
out_str <- get_diagram_aux(dot_code)
cat(out_str)
# write_clip(dot_code)
```

```{r,eval=FALSE}
target <- "2507-0700"
```

```{r,eval=FALSE}
tt <- glue("Inbound to {target}")

db.cables |>
	filter(DstTag == target) |>
	select(Tag, SrcTag, SrcPort, Type, Usage) |>
	gt() |>
	tab_header(tt) |>
	cols_label(Tag = "Cable Label"
			   , SrcTag = "Source Device"
			   , SrcPort = "Source Port") |>
	opt_stylize(style = 5)
```

```{r,eval=FALSE}
tt <- glue("Outbound from {target}")

db.cables |>
	filter(SrcTag == target) |>
	select(Tag, DstTag, DstPort, Type, Usage) |>
	gt() |>
	tab_header(tt) |>
	cols_label(Tag = "Cable Label"
			   , DstTag = "Target Device"
			   , DstPort = "Target Port") |>
	opt_stylize(style = 5)
```

## BMD VideoHub Matrix

The Black Magic Design 40x40 Video Hub is a video matrix that has 40 SDI inputs and 40 SDI outputs. An Input can be routed to any number of outputs. 
The routing can be managed via the front panel on the device or via the "VideoHub Control" that is installed on several computers. There are also some presets that have be created for the Stream Deck device located at the video Desk. 

### Inputs VideoHub

All inputs to the matrix are SDI. An input can be routed to a one or more outputs at once. Since there are 40 inputs and outputs, a single diagram to show everything at once is unreadable. A few diagrams show key connections with the full details are in the table.

The Decklink is an 8-port PCIe Card located in the expansion chassis next to the Mac Studio (CUMU-G002). These ports can be configured for either input or output. Seven of them feed into the VideoHub and one (sdi7) is fed from it.

```{r dl2vh, results="asis"}
dot_code <- get_connectivity_diagram ( "2507-0700", "in"
								, db.inventory
					   , db.cables, types = NULL
					   , label = '"Connectivity from Decklink into VideoHub"' 
								, rankdir = "LR",
								partners = c("ZVIU-E004"))
cat(get_diagram_aux(dot_code ))
```

The Constellation is a video switching device that has 12 inputs and 20 outputs, plus two multi-view outputs. All of its inputs and outputs go to the video hub. The diagram is rather messy as a result.

```{r cons2vh, results="asis"}
a <- get_connectivity_diagram ( "2507-0700", "in"
								, db.inventory
					   , db.cables, types = NULL
					   , label = '"Connectivity from Constellation into VideoHub"' 
								, rankdir = "LR",
								partners = c("2601-2800")) 
cat(get_diagram_aux(a))
```

We have four cameras that are connected to the VideoHub which are then normally routed to the Constellation.

```{r cameras2vh, results="asis"}
	ps <- c("ZVCU-A001"
			,"ZVCU-A002"
			,"ZVCU-A003"
			,"ZVVU-C001")
	
	a <- get_connectivity_diagram ( "2507-0700", "in", db.inventory
									, db.cables, types = NULL
									, label = '"Connectivity from Cameras into VideoHub"' 
									, rankdir = "LR",
									partners = ps) 
	cat(get_diagram_aux(a))
```

```{r vh_in_table, results='asis' }
#| tbl-cap: "VideoHub Matrix Inputs"
#| tbl-cap-location: bottom
#| out-width: 50%       # Scales the image to 100% of the text width
#| fig-width: 4          # Sets the figure width in inches (useful for LaTeX)
#| fig-height: 4         # Sets the figure height in inches

dev <- "2507-0700"
tt <- glue("Inputs for {dev}")
st <- db.inventory |> filter(AssetTag == dev) |> mutate(txt = paste(Manufacturer, Model, Usage)) |> pull(txt)

tab <- db.cables |>
	full_join(db.inventory, by=join_by(SrcTag == AssetTag)
			  , na_matches = "never") |>
	filter(DstTag == dev) |>
 	select(Tag , SrcTag
 		   , Manufacturer, Model
 		   , SrcPort,  DstPort,Type.x, Usage.x ) |>
   gt() |>  
		opt_stylize(style = 5) |>
	tab_header(tt, subtitle=st) |>
	cols_merge(
	    columns = c(Manufacturer, Model),
    	pattern = "{1}\n{2}"
  ) |> cols_label( Tag = "Cable"
  				 , Manufacturer ="Src Device"
  				 , Type.x ="Type"
  				 , Usage.x = "Usage")   

print_gt_table(tab ) |> cat()
```

### Outputs VideoHub

All outputs are SDI.

```{r vh2projs, results="asis"}
	ps <- c("2601-1304", "2601-1305" , "2601-1306"
			, "2604-2401", "2604-2402" , "2604-2403"
	)
	
	a <- get_connectivity_diagram ( "2507-0700", "out", db.inventory
									, db.cables, types = NULL
									, label = '"Connectivity from VideoHub into Projectors"' 
									, rankdir = "LR",
									partners = ps) 
	cat(get_diagram_aux(a))
```

```{r vh_out_tab, results='asis',eval=TRUE}
#| tbl-cap: "VideoHub Matrix Outputs"
#| tbl-cap-location: bottom

dev <- "2507-0700"
tt <- glue("Output Ports for {dev}")
st <- db.inventory |> filter(AssetTag == dev) |> mutate(txt = paste(Manufacturer, Model, Usage)) |> pull(txt)

tab <- db.cables |>
	filter(SrcTag == dev) |> 
	full_join(db.inventory, by=join_by(DstTag == AssetTag)
			  , na_matches = "never") |>
	filter( ! is.na(Tag )  ) |>
	arrange(SrcPort) |>
    select(Tag, SrcPort, DstTag
			   , Manufacturer, Model
			   ,DstPort,Type.x,Usage.x ) |>
    gt() |>  
	opt_stylize(style = 5) |>
	tab_header(tt, subtitle=st) |>
	cols_merge(
	    columns = c(Manufacturer, Model),
    	pattern = "{1}\n{2}"
  ) |> cols_label( Tag = "Cable"
  				 , Manufacturer ="Dst Device"
  				 , Type.x ="Type"
  				 , Usage.x = "Usage")   
	 
print_gt_table(tab) |> cat()
```

## VS-88DT Matrix

The Kramer VS-88DT video matrix which is an 8x8 matrix and can handle HDMI inputs and outputs which are either HDMI or [HDBaseT](https://en.wikipedia.org/wiki/HDBaseT) formats. Any of the 8 inputs can be routed to any of the 8 outputs (or several outputs).

It can be controlled via the buttons on the front panel or from its built-in web page.

### Inputs

All inputs to the matrix are HDMI. An input can be routed to a one or more outputs at once.

```{r vs_in_tab, results='asis'}
#| tbl-cap: "Video Matrix Inputs"
#| tbl-cap-location: bottom

dev <- "ZVKU-A001"
tt <- glue("Input Ports for {dev}")
st <- db.inventory |> filter(AssetTag == dev) |> 
	mutate(txt = paste(Manufacturer, Model, Usage)) |> 
	pull(txt)

tab <- db.cables |>
	filter(DstTag == dev) |>
	select(Tag,SrcTag,SrcPort,DstTag,DstPort,Type,Usage ) |>
	arrange(DstPort) |>
	gt() |>  
	opt_stylize(style = 5) |>
	tab_header(tt, subtitle=st)

print_gt_table(tab) |> cat()
```

### Outputs

Each matrix output can be either HDMI or HDBaseT. Several typical configurations are discussed on the Operations document.   


```{r vs882projs, results="asis"}
	ps <- c( 
			 "2604-2401", "2604-2402" , "2604-2403"
	)
	
	a <- get_connectivity_diagram ( "ZVKU-A001", "out", db.inventory
									, db.cables, types = NULL
									, label = '"Connectivity from VS88 into Projectors"' 
									, rankdir = "LR",
									partners = ps) 
	#cat(get_diagram_aux(a))
	grViz(a)
```


```{r vs_out_table, results='asis', eval=TRUE}
#| tbl-cap: "Video Matrix Outputs"
#| tbl-cap-location: bottom
#| out-width: 40%       # Scales the image to 100% of the text width
#| fig-width: 4          # Sets the figure width in inches (useful for LaTeX)
#| fig-height: 4         # Sets the figure height in inches

dev <- "ZVKU-A001"
tt <- glue("Output Ports for {dev}")
st <- db.inventory |> filter(AssetTag == dev) |> mutate(txt = paste(Manufacturer, Model, Usage)) |> pull(txt)

tab <- db.cables |>
	filter(SrcTag == dev) |>
	full_join(db.inventory, by=join_by(DstTag == AssetTag)
			  , na_matches = "never") |>
	filter( ! is.na(Tag )  ) |>
	select(Tag ,SrcPort,DstTag
		   ,Manufacturer, Model
		   , DstPort,Type.x,Usage.x ) |>
	arrange(SrcPort) |>
    gt() |>  
	opt_stylize(style = 5) |>
	tab_header(tt, subtitle=st) |>
	cols_merge(
	    columns = c(Manufacturer, Model),
    	pattern = "{1}\n{2}"
  ) |> cols_label( Tag = "Cable"
  				 , Manufacturer ="Dst Device"
  				 , Type.x ="Type"
  				 , Usage.x = "Usage")  
	 
print_gt_table(tab) |> cat()
   
```

```{r vh-connections, results='asis'}
#| label: tbl-vh-connections
#| tbl-cap: "VideoHub Connected Devices"

dev <- "2507-0700" #videohub

l1 <- db.cables |> 
	filter(SrcTag == dev | DstTag == dev)

cdev <- c(l1$SrcTag, l1$DstTag) |> unique()

items <-cdev
inventory <- db.inventory

print_inv(cdev, db.inventory) |>
	print_gt_table() |>
    cat()
```

# ATEM Constellation 2ME Video Mixer

The ATEM Constellation 2ME is a professional video switcher that allows for seamless switching between multiple video sources during live productions. It offers advanced features such as picture-in-picture, transitions, supersource and keying effects.

## Inputs

```{r atem_in_table, results='asis' }
#| tbl-cap: "ATEM Inputs"
#| tbl-cap-location: bottom
#| out-width: 50%       # Scales the image to 100% of the text width
#| fig-width: 4          # Sets the figure width in inches (useful for LaTeX)
#| fig-height: 4         # Sets the figure height in inches

dev <- "2601-2800"
tt <- glue("Inputs for {dev}")
st <- db.inventory |> filter(AssetTag == dev) |> mutate(txt = paste(Manufacturer, Model, Usage)) |> pull(txt)

tab <- db.cables |>
	full_join(db.inventory, by=join_by(SrcTag == AssetTag)
			  , na_matches = "never") |>
	filter(DstTag == dev) |>
 	select(Tag , SrcTag
 		   , Manufacturer, Model
 		   , SrcPort,  DstPort,Type.x, Usage.x ) |>
   gt() |>  
		opt_stylize(style = 5) |>
	tab_header(tt, subtitle=st) |>
	cols_merge(
	    columns = c(Manufacturer, Model),
    	pattern = "{1}\n{2}"
  ) |> cols_label( Tag = "Cable"
  				 , Manufacturer ="Src Device"
  				 , Type.x ="Type"
  				 , Usage.x = "Usage")   

print_gt_table(tab ) |> cat()
```

## Outputs

```{r atem_out_table, results='asis' }
#| tbl-cap: "ATEM Outputs"
#| tbl-cap-location: bottom
#| out-width: 50%       # Scales the image to 100% of the text width
#| fig-width: 4          # Sets the figure width in inches (useful for LaTeX)
#| fig-height: 4         # Sets the figure height in inches

dev <- "2601-2800"
tt <- glue("Outputs for {dev}")
st <- db.inventory |> filter(AssetTag == dev) |> mutate(txt = paste(Manufacturer, Model, Usage)) |> pull(txt)

tab <- db.cables |>
	full_join(db.inventory, by=join_by(DstTag == AssetTag)
			  , na_matches = "never") |>
	filter(SrcTag == dev) |>
    select(Tag, SrcPort, DstTag
			   , Manufacturer, Model
			   ,DstPort,Type.x,Usage.x ) |>
    gt() |>  
	opt_stylize(style = 5) |>
	tab_header(tt, subtitle=st) |>
	cols_merge(
	    columns = c(Manufacturer, Model),
    	pattern = "{1}\n{2}"
  ) |> cols_label( Tag = "Cable"
  				 , Manufacturer ="Dst Device"
  				 , Type.x ="Type"
  				 , Usage.x = "Usage")    

print_gt_table(tab ) |> cat()
```

# Recording Devices and Broadcasting

There are two main recording devices in the system. The Blackmagic Design HyperDeck Studio Mini and a Resi Encoder.

```{r RDnB, results="asis"}
    targets <- c( "ZVRU-A001", "ZVRU-A002", "ZVIU-G001"
			 ) 
	ps <- c(   "2507-0700"  
	)
	l <- '"Connectivity to Recorders and Resi"'
	
	a <- get_connectivity_diagram ( targets, "both"
									, db.inventory
									, db.cables
									, types = NULL
									, label = l 
									, rankdir = "LR",
									partners = ps) 
	#cat(get_diagram_aux(a))
	grViz(a)
```

```{r RDnB_in_table, results='asis' }
#| tbl-cap: "Recording Devices and Broadcasting"
#| tbl-cap-location: bottom
#| out-width: 50%       # Scales the image to 100% of the text width
#| fig-width: 4          # Sets the figure width in inches (useful for LaTeX)
#| fig-height: 4         # Sets the figure height in inches

dev <- c("ZVRU-A001", "ZVRU-A002")
devlist <- paste(dev, collapse=", ")
tt <- glue("Inputs for {devlist}")
st <- db.inventory |> filter(AssetTag %in% dev) |> mutate(txt = paste(Manufacturer, Model, Usage)) |> pull(txt) |> paste(collapse = " / ")

tab <- db.cables |>
	full_join(db.inventory
			  , by=join_by(SrcTag == AssetTag)
			  , na_matches = "never") |>
	filter(SrcTag %in% dev) |>
    select(Tag, SrcPort, DstTag
			   , Manufacturer, Model
			   ,DstPort,Type.x,Usage.x ) |>
    gt() |>  
	opt_stylize(style = 5) |>
	tab_header(tt, subtitle=st) |>
	cols_merge(
	    columns = c(Manufacturer, Model),
    	pattern = "{1}\n{2}"
  ) |> cols_label( Tag = "Cable"
  				 , Manufacturer ="Dst Device"
  				 , Type.x ="Type"
  				 , Usage.x = "Usage")    

print_gt_table(tab ) |> cat()
```

```{r RDnB_ot_table, results='asis' }
#| tbl-cap: "Recording Devices and Broadcasting"
#| tbl-cap-location: bottom
#| out-width: 50%       # Scales the image to 100% of the text width
#| fig-width: 4          # Sets the figure width in inches (useful for LaTeX)
#| fig-height: 4         # Sets the figure height in inches

dev <- c("ZVRU-A001", "ZVRU-A002")
devlist <- paste(dev, collapse=", ")
tt <- glue("Outputs for {devlist}")
st <- db.inventory |> filter(AssetTag %in% dev) |> mutate(txt = paste(Manufacturer, Model, Usage)) |> pull(txt)

tab <- db.cables |>
	full_join(db.inventory, by=join_by(DstTag == AssetTag)
			  , na_matches = "never") |>
	filter(DstTag %in% dev) |>
    select(Tag, DstPort, SrcTag
			   , Manufacturer, Model
			   ,SrcPort,Type.x,Usage.x ) |>
    gt() |>  
	opt_stylize(style = 5) |>
	tab_header(tt, subtitle=st) |>
	cols_merge(
	    columns = c(Manufacturer, Model),
    	pattern = "{1}\n{2}"
  ) |> cols_label( Tag = "Cable"
  				 , Manufacturer ="Src Device"
  				 , Type.x ="Type"
  				 , Usage.x = "Usage")    

print_gt_table(tab ) |> cat()
```


# Topologies

There are a lot of components to the system. One big diagram is daunting. The system description has been broken down into smaller portions to be more consumable. 

## Computer Topology

There are three computers in the system. The paths from the ProPresenter outputs through the VideoHub are generated from the cable database below.

CUMU-G002 / MacOS / ProPresenter / DVD Player
: This system runs ProPresenter and has multiple outputs:

* An HDMI port on the main system used as the operator display
* An HDMI output via dongle that is used for programs that need to show their output on a OS managed display. For example the DVD Player or Powerpoint. This is converted to SDI and fed into the video hub.
* Seven outputs from the Decklink card that are used for various purposes.  
    +  Three SDI outputs to the front projectors via the Decklink interface
    + Two SDI outputs of Fill and Key for the ATEM
    + One SDI output for stage display which is fed into the video hub and then to the rear projector, broadcast room and the monitor beside FoH audio desk. 
    + One output is spare and could be used for the announcement layer.
 

CDWU-0009 Windows  
: This windows 10 system has a dual output video card. One is used for the operator display, and the second for presentation. It has Powerpoint for Windows installed.

CUMU-G001 MacOS / ATEM Control 
: This system runs the ATEM switcher software and can also run things like Zoom. Although it has an unused HDMI output via a dongle, it is not currently connected.

```{r topology1-computer-diag, results='asis'}
dot_code <- videohub_path_diagram(db.cables, db.inventory
					, src_tags = c("ZVIU-E004", "ZVIU-A006", "ZVIU-C001")
					, label = "ProPresenter outputs through the VideoHub")
cat(get_diagram_aux(dot_code))
```

```{r topology1-computer, results='asis'}
#| label: tbl-topology1-computer
#| tbl-cap: "Computer Topology"

print_inv(c("CUMU-G002", "ZVIU-E004", "ZVIU-E005", "ZVIU-A006", "ZVIU-C001"
			, "CDWU-0009", "CUMU-G001"), db.inventory) |>
	print_gt_table() |>
    cat()
```

## Projection Topology
There are four projectors in the auditorium, three FoH and one at the rear for confidence. They are all fed a HDBaseT signal (via Cat6) and a SDI signal.

```{r projtopo , results="asis"}
    targets <- c( "ZVKU-A001"
			 ) 
	ps <- c(   "2507-0700"   
			   ,"ZVVU-0001"
			   ,"2604-2401", "2604-2402", "2604-2403"
		, "2601-1304", "2601-1305" , "2601-1306"
			   )
	
	l <- '"Projection Topology"'
	
	a <- get_connectivity_diagram ( targets, "both"
									, db.inventory
									, db.cables
									, types = NULL
									, label = l 
									, rankdir = "LR",
									partners = ps) 
	cat(get_diagram_aux(a))
```


```{r top2}
print_inv(c("ZVKU-A001","2604-2401", "2604-2402", "2604-2403"
			, "ZVVU-0001", "2310-1700"),
          db.inventory)
```

## Lobby Topology
The TV in the lobby gets its content from the video matrix. For the main service it should get its feed from the video mixer program output .

There is a network cable that also runs to the lobby TV, and is for future use.

```{dot}
//| fig-width: 4
//| fig-height: 2
//| label: fig-topology-lobby
//| fig-cap: "Topology for lobby TV"
//| file: gv/sdv-topology3-lobby.gv
```

```{r l132}
print_inv(c("ZVIU-A001", "ZVKU-A001" 
			, "2310-1700"
			), db.inventory)
```

## Nursery Topology
The TV in the nursery gets its content from the video matrix. For the main service it should get its feed from the video mixer program output.

```{dot}
//| fig-width: 4
//| fig-height: 2
//| label: fig-topology-nursery
//| fig-cap: "Topology for nursery TV"
//| file: gv/sdv-topology4-nursery.gv
```

```{r top3_inv}
print_inv(c("ZVIU-A002", "ZVKU-A001","ZVVU-0002", "ZVVU-0003"), db.inventory)
```

The TV has a remote control which is found on top of the coatrack near the TV, power on/off can be controlled directly using the button on the bottom centre of the screen.

## Library Topology

The TV in the library gets its content from the VideoHub, typical source is the VideoMixer output. 
 
```{r libtop, results="asis"}

targets_v <- c(    "2507-0700" 
				 , "2512-1001" 
				 , "2601-0600"
			 ) 

xd <- c(   "ZVCU-A001" , "ZVCU-A002", "ZVCU-A003"
		   , "ZVRU-A001", "ZVRU-A002" #  "recorder"
		   , "ZVIU-C001"
		   , "ZVVU-C001"
		   , "ZVIU-E002"
		   , "ZVIU-E004"
		  
		 , "2601-2800"  
		 , "2601-0803"
		 , "2603-1203"
		 , "2601-1304", "2601-1305" , "2601-1306"
		 , "2510-0502", "2510-0503"
		 , "ZVIU-A004"
		 , "ZVIU-G001" 
		 , "2602-1800-F38"
		 , "c59", "c60"
		) 

label <- '"Library Topology"'

dot_code <- get_diagram(targets_v
						, db.inventory, db.cables
						, label=label , exc_dev=xd )
out_str <- get_diagram_aux(dot_code)
cat(out_str)
grViz(dot_code)
```

```{r toplib_inv}
print_inv( targets_v, db.inventory)
```

## Recording / Livestream Topology
The recording topology is quite complex and so it is broken up into pieces.

### Inputs

A key constraint for the ATEM video mixer is that all inputs must have the same input resolution settings. We have chosen 1080p59.94. 

All ATEM inputs come from the VideoHub. The diagram below shows each source, the VideoHub input it lands on, the default crosspoint, and the ATEM input it reaches. The crosspoints are the defaults recorded in the cable database; the Stream Deck presets can change them.

```{r recin-diag, results='asis'}
dot_code <- videohub_path_diagram(db.cables, db.inventory
					, dest_tags = "2601-2800"
					, label = "Sources routed into the ATEM")
cat(get_diagram_aux(dot_code))
```

### Outputs

All ATEM outputs go back into the VideoHub, which distributes them to the recorders, the Resi encoder, the Web Presenter, the NDI converter and the monitors.

```{r recout-diag, results='asis'}
dot_code <- videohub_path_diagram(db.cables, db.inventory
					, src_tags = "2601-2800"
					, label = "ATEM outputs routed to destinations")
cat(get_diagram_aux(dot_code))
```

### Web Presenter

The WebPresenter converts its SDI input to a USB webcam format which is used by the video computer (CUMU-G001) for Zoom or OBS. It is fed from VideoHub output 28.

```{r wp-diag, results='asis'}
dot_code <- videohub_path_diagram(db.cables, db.inventory
					, dest_tags = "ZVIU-A004"
					, label = "Web Presenter feed")
cat(get_diagram_aux(dot_code))
```

```{r wp-inv, results='asis'}
#| label: tbl-wp-inv
#| tbl-cap: "Web Presenter"
print_inv(c("ZVIU-A004", "CUMU-G001"), db.inventory) |>
	print_gt_table() |>
	cat()
```

# Network Details

```{r net-details, results='asis'} 
network.data |>
	inner_join(db.assets, by=join_by(AssetTag == AssetTag)) |>
filter(Category=="Video") |>
select(AssetTag, Usage.x,   MAC, IP, URL, Notes) %>%
    gt( ) |>
			opt_stylize(style = 3) |>
    		tab_style(
			style = cell_text(
				weight = "bold", 
				),
			locations = cells_body(
				columns = "AssetTag")
		) |>
		tab_options(table.font.size="50%") |>
	print_gt_table() |>
	cat()
```

# Video Equipment Inventory

```{r inventory, results='asis'}
#| label: tbl-video-inventory
#| tbl-cap: "Video Equipment Inventory"

items <- db.inventory |> 
          filter( Category=="Video" ,
                  InService== "Y", !is.na(AssetTag)) |>
          filter(!Type %in% c("Cable")) |>
          select(AssetTag) %>%
          pull()
  
print_inv(items, db.inventory) |>
	print_gt_table() |>
	cat()
```

{{< include common_trailer.qmd >}}
