---
title: "System Administration Guide"
author: "UAC Media Arts"
execute: 
  eval: true
  echo: false
  warning: false
  message: false
format:
  html:
    toc: true
  pdf:
    toc: true
  titlepage-pdf:
    toc: true
always_allow_html: yes
---

```{r packages, include=FALSE}
source("commonPackages.r")
```

```{r functions}
source("commonFunctions.r")
```

```{r getdata}
credentials <- get.credentials()
software    <- get.software()
db.assets   <- get.assets()
db.cables   <- get.cables()
db.network  <- get.network()
```

# Introduction

This document provides key administrative documentation for the AV technical systems at UAC. This material is meant to be disclosed to a few people who may need this information to take over the responsibilities of the Technical Manager.  

# Credentials
One can't manage the systems if you cannot get past userids and passwords, so they need to be protected and shared discretly.

Passwords are not revealed in this document, instead the following tables discloses which passwords exist (PasswordKnown). Terry knows these passwords and a copy will be filed with the Office Manager.

## Internal Systems
```{r}
credentials %>% 
  mutate(PasswordKnown = !is.na(Password)) %>%
  filter(AssetOrService=="Asset") %>%
  select(ID,	Userid, PasswordKnown, 	Comment) %>%
  rename(AssetTag = ID) %>%
  gt(  ) |>
  opt_stylize(style=5) 
```

## External Services
  
```{r}  
credentials %>% 
  mutate(PasswordKnown = !is.na(Password)) %>%
  filter(AssetOrService=="Service") %>%
  select(ID, URL,	Userid, PasswordKnown, 	Comment) %>%
  rename(Name = ID) %>%
  gt(  ) |>
  opt_stylize(style=5)  
```

# Software

The details of which software is to be installed on every system. A manufacturer value of 'oss' means open source software.
License keys are not exposed in this report.

```{r software}
software %>%
  arrange(InstalledOn, Manufacturer, Title) %>%
  select(InstalledOn, Title, Version, Manufacturer, Comments) %>%
  gt(  ) |>
  opt_stylize(style=5) 
```

## Summary by Title

```{r}
 software |>
	mutate(installed = "X") |>
	select(Title,InstalledOn, installed ) |>
	pivot_wider(names_from = "InstalledOn", values_from = "installed" ) |>
    gt(  ) |>
    opt_stylize(style=5) 
```

# Server Applications

Four server applications run on the video computer **CUMU-G001** under the `avuser` account. The three custom ones are managed with a `run.sh` script in their respective directories under `/Users/avuser/`; the fourth, Companion, is a packaged application.

## AVL Tech Assistant (`avltechassistant`) {#sec-avltechassistant}

### Purpose

A web-based documentation and asset management tool for the AV/Lighting technical systems. Provides asset search, connectivity diagrams, signal path finding, rack location views, a knowledge base, and an operational dashboard.

### Architecture

| Component | Technology | Port |
|-----------|-----------|------|
| Frontend | Python `http.server` serving static HTML/CSS/JS | 8080 |
| Backend | FastAPI + uvicorn | 9000 |
| Data | Excel spreadsheets (`/data/*.xlsx`) | — |
| Diagrams | Graphviz (`dot`) | — |

The frontend is a single-page application (`index.html`) that calls the backend REST API. The backend reads asset, cable, network, and knowledge base data from `.xlsx` files at startup (reloadable via the UI). Connectivity diagrams are rendered server-side using Graphviz and returned as SVG.

The backend also proxies manual lookups to the `media_arts_home` server (see below), rewriting relative file URLs to absolute before returning them to the browser.

### Source Code

GitHub: `https://github.com/avmaint/avltechassistant` (private, owned by `avmaint` account; `donert` is a collaborator)

### Directory Layout

```
avltechassistant/
  backend/
    main.py           # FastAPI application
    requirements.txt
  frontend/
    index.html
    script.js
    style.css
    full.render.js
  tests/
    run_tests.py
  data/               # symlink → ../data  (xlsx data files live outside the repo)
  run.sh
```

### Dependencies

- Python 3 with virtual environment (`.venv/`)
- Graphviz — installed via MacPorts at `/opt/local/bin/dot`; must be on PATH

### Installation (first time on a new machine)

```bash
cd /Users/avuser/avltechassistant
./run.sh install        # creates .venv and installs Python packages
ln -s ../data data      # point to shared data directory if not already present
```

Ensure `/opt/local/bin` is on the PATH used by the shell that launches the app (add to `~/.zshrc`):

```bash
export PATH="/opt/local/bin:$PATH"
```

### Deployment (updating to latest code)

```bash
cd /Users/avuser/avltechassistant
./run.sh deploy         # git pull + pip install
./run.sh restart        # stop and start both services
```

### Start / Stop

```bash
./run.sh start          # starts frontend (8080) and backend (9000) as background daemons
./run.sh stop           # stops both
./run.sh restart        # stop then start
```

Logs: `frontend.log` and `backend.log` in the repo root directory.

---

## Media Arts Home (`media_arts_home`) {#sec-media-arts-home}

### Purpose

An internal web server providing:

- **Documentation browser** — rendered HTML versions of the Quarto system design documents
- **Manuals browser** — PDF equipment manuals indexed by asset tag
- **Messages board** — operational notes visible to the tech team

### Architecture

| Component | Technology | Port |
|-----------|-----------|------|
| Web server | Flask (Python) | 80 |
| Docs | Static HTML files in `docs/` directory | — |
| Manuals | PDF files in `manuals/` directory | — |
| Manual index | `manuals/assets_manuals_index.json` | — |

### Source Code

GitHub: `https://github.com/avmaint/media_arts_home` (private)

### Key API Endpoints

| Endpoint | Description |
|----------|-------------|
| `GET /` | Home page |
| `GET /docs/` | Documentation index |
| `GET /docs/<filename>` | Serve a documentation file |
| `GET /manuals/` | Manuals index |
| `GET /manuals/files/<path>` | Serve a PDF manual |
| `GET /api/manuals/<asset_tag>` | JSON list of manuals for an asset |
| `GET /api/messages` | Retrieve operational messages |
| `POST /api/messages` | Post a new message |

### Installation (first time)

```bash
cd /Users/avuser/media_arts_home
./run.sh install        # creates .venv and installs Flask
```

Publish content after first install:

```bash
./scripts/publish_docs.sh       # copies rendered HTML docs into docs/
./scripts/publish_manuals.sh    # copies PDFs and builds manuals index
```

### Deployment (updating)

```bash
cd /Users/avuser/media_arts_home
./run.sh deploy         # git pull + pip install
./run.sh stop
./run.sh start
```

### Start / Stop

```bash
./run.sh start          # starts Flask on port 80 as a background daemon
./run.sh stop
```

Log: `server.log` in the repo root directory.

---

## Stream Decks and Companion {#sec-streamdeck}

### Purpose

The Elgato Stream Decks are the primary operator control surfaces for the video switcher, VideoHub routing, camera PTZ, projector and TV power, ProPresenter slide control, lighting presets, audio helpers and the nursery parental call. The buttons themselves are dumb; every action is executed by [Companion](https://bitfocus.io/companion) (Bitfocus) running on CUMU-G001, which talks to the ATEM, VideoHub, projectors, grandMA3, Shure receivers, Reaper and ProPresenter over the network.

::: callout-important
Nothing on any Stream Deck works unless **`avuser` is logged in on CUMU-G001 and Companion is running**. This is the first thing to check when a Stream Deck goes blank.
:::

### Hardware

```{r sd-hardware}
#| label: tbl-sd-hardware
#| tbl-cap: Stream Deck Hardware
db.assets |>
	filter(grepl("stream deck|network dock", paste(Model, Desc), ignore.case = TRUE)) |>
	select(AssetTag, Model, Desc, Location, InService) |>
	arrange(AssetTag) |>
	gt() |>
	opt_stylize(style = 5)
```

Video desk (2603-1301)

:   Stream Deck XL connected directly to CUMU-G001 by USB-C. Runs the Video, Audio and Lighting menus. Its main job is switching the ATEM.

ProPresenter desk (2605-2504)

:   Stream Deck XL connected to a Stream Deck Network Dock (2605-2500), which puts it on the network so that Companion on CUMU-G001 can drive it. Its main job is projector and TV power control, projector freeze/thaw and ProPresenter slide control.

Nursery (2605-1502)

:   Stream Deck MK2 with its own network dock (2605-1503), not yet installed. Restricted to the parental call page: a parent number is punched in and the message appears on the projectors for a set time, managed by ProPresenter.

```{r sd-connections}
#| label: tbl-sd-connections
#| tbl-cap: Stream Deck Connections
sd <- db.assets |> filter(grepl("stream deck|network dock", paste(Model, Desc), ignore.case = TRUE)) |> pull(AssetTag)
db.cables |>
	filter(SrcTag %in% sd | DstTag %in% sd) |>
	select(Tag, SrcTag, SrcPort, DstTag, DstPort, Type, Usage) |>
	arrange(DstTag) |>
	gt() |>
	opt_stylize(style = 5) |>
	sub_missing(missing_text = "-")
```

```{r sd-network}
#| label: tbl-sd-network
#| tbl-cap: Stream Deck Dock Network Addresses
db.network |>
	filter(AssetTag %in% sd) |>
	select(AssetTag, Usage, IP, Notes) |>
	gt() |>
	opt_stylize(style = 5) |>
	sub_missing(missing_text = "-")
```

### Menu Structure

Both the video and ProPresenter units share one button layout. The three buttons in the lower right corner of every page are for navigation: the very corner button is **Main Menu**, the one to its left is the sub-menu, and the one to the left of that shows the current page name and does nothing when pressed.

```{r sd-menu}
#| label: tbl-sd-menu
#| tbl-cap: Stream Deck Menu Structure
tribble(
	~Menu, ~Page, ~Description,
	"Video", "ATEM ME1", "The most important controls for mix effects engine 1 on the video mixer: program/preview rows, T-bar steps, CUT/AUTO, Lyrics and PiP toggles",
	"Video", "ATEM ME2", "Program/preview for mix effects engine 2, mostly used to pick the SuperSource camera",
	"Video", "VideoHub", "Routing presets: Normal Projectors, Baptism, Pgm to B, Pgm to A & C, ProP HDMI to ABC",
	"Video", "Camera 1 / 2 / 3", "PTZ, focus, colour and brightness for each camera",
	"Video", "ATEM Macros", "Pre Service, Start Service, Start Message, Stop Service, Stop Message, Kaleo Bug (logo for 120 s)",
	"Video", "Record Control", "Rec, Stop, Play, Prev/Next Clip, Format Prepare/Confirm for the HyperDeck recorders",
	"ProPresenter", "Power Control", "Projector A/B/C and TV on/off (red = off, green = on), Freeze/Thaw A/B/C",
	"ProPresenter", "ProP Controls", "Focus previous/next presentation, trigger first slide, previous/next slide",
	"Audio", "Shure", "Signal and battery levels for the wireless microphones",
	"Audio", "Reaper", "Layer keys that snap fader 1 of the FaderPort 16 to the first channel of a group (Drums, Guitars, Talk, Choir, Spare, Vocals, Keys, Busses)",
	"Lighting", "Presets", "Lighting moments: Walk in, Talk Thrust, Talk Vox, Video, Message, Walk out; Scheme Series NoG, Scheme Missions",
	"Utility (hidden)", "Jado", "Podcast / Normal: switches the Dante routing for a podcast session and back",
	"Utility (hidden)", "Nursery", "Parental call: digits 0-9, Clear, Call #"
) |>
	gt(groupname_col = "Menu") |>
	opt_stylize(style = 5) |>
	tab_style(style = cell_text(weight = "bold"), locations = cells_row_groups())
```

The operator-facing descriptions of each page are in the Operations documents: the ATEM, VideoHub, macro and recorder pages in *System Operations - Video*, the power control page in *System Operations - Projection*.

### Power Control Notes

-   **Proj A / B / C**: pressing when red turns the projector on; the button turns green after some seconds. Pressing when green turns it off.
-   **TV Lobby**: red when off, green when on; pressing also forces the TV input to HDMI 1.
-   **StgDsp TV** and **Nursery TV**: not currently working.
-   **Freeze x / Thaw x**: holds the image on that projector until thawed. Companion cannot show freeze status on the button.

### Architecture

| Component | Technology | Location |
|-----------|-----------|----------|
| Companion | Bitfocus Companion (packaged macOS app) | CUMU-G001, `avuser` |
| Configuration | Companion config (pages, buttons, connections) | Companion's application data on CUMU-G001 |
| Devices | Stream Deck XL over USB; Stream Deck XL / MK2 over Network Dock | see @tbl-sd-connections |
| Emulator | Companion's built-in web emulator | Companion web interface on CUMU-G001 |

Companion also offers a web page emulator that presents the same button pages in a browser, which is the fallback if a physical unit fails.

Companion connects to the controlled devices through its device modules: Blackmagic ATEM (2601-2800), Blackmagic VideoHub (2507-0700), Blackmagic HyperDeck (ZVRU-A001, ZVRU-A002), Sony PTZ cameras (ZVCU-A001..A003), Sony projectors (2604-2401..2403), the lobby TV (2310-1700), grandMA3 (2607-2500), the Shure wireless receivers, Reaper (CUMU-E001) and ProPresenter (CUMU-G002).

### Startup

Companion must be running whenever the Stream Decks are needed. If a Stream Deck is blank:

1.  Log in to CUMU-G001 as `avuser`.
2.  Check that Companion is running (menu bar icon). Start it from Applications if not.
3.  Open the Companion web interface and check the *Connections* tab: every connection should show a green status. A red one usually means the device is off or unreachable on the network.
4.  Check the *Surfaces* tab: the USB Stream Deck and the network docks should be listed. A network dock that is missing usually needs its power or network cable reseated.

::: callout-note
TODO: confirm how Companion is launched at login (login item vs. Automator), the web interface URL/port, and add Companion to the software inventory sheet.
:::

### Backup and Changes

-   Before changing anything, export the configuration from the Companion web interface (*Import / Export* > *Export*) and keep the file with the other system backups.
-   Button changes are made in the web interface. Test on the emulator before relying on the physical unit.
-   A Companion upgrade can change module behaviour; export first and keep the previous installer.

---

## CueCommander {#sec-cuecommander-admin}

{{< include common_CueCommander.qmd >}}

### Installation & Startup

CueCommander runs on the Node-RED platform. Node-RED is installed as a global npm package and starts automatically when `avuser` logs in via an Apple Automator script.

To start or restart manually:

```bash
node-red start
```

The web interface is available at `http://192.168.0.206:1880/ui`.

Source code: `https://github.com/donert/CueCommander-NR` (public)

---

## Quick Reference — All Services

| Application | URL | Port | Run script location |
|-------------|-----|------|-------------------|
| AVL Tech Assistant | `http://192.168.0.206:8080` | 8080 / 9000 | `/Users/avuser/avltechassistant/run.sh` |
| Media Arts Home | `http://192.168.0.206` | 80 | `/Users/avuser/media_arts_home/run.sh` |
| CueCommander | `http://192.168.0.206:1880/ui` | 1880 | Automator / `node-red` |
| Companion (Stream Decks) | TODO | TODO | Companion application, see @sec-streamdeck |

{{< include common_trailer.qmd >}}
