---
title: "System Operations - Audio"
author: "Terry Doner"
date: "`r format(Sys.time(), '%B %d %Y')`"
output: 
    html_document:
        toc: true
---

```{r setup, include=FALSE}
require(readr)
require(dplyr)
require(readxl)
require(knitr)
require(jpeg)
require(grid)
require(ggplot2)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.table.format = "html") # latex for pdf 
```

```{r data}
path <-"~/Documents/UACTech/SystemDocumentation"
inventoryfile <- "TechInventory.xlsx"
fname <- paste(path, inventoryfile, sep="/")
```

```{r functions}
source("commonFunctions.R")
```


# Introduction
This document provides basic operating information for each of the Audio systems at UAC.

[Back to top](#top)

## Power On
 
There are three numbered swtiches located in the balcony required to turn the system on

#. is located at the far west end of the front desk. This energizes the front desk gear.
#. is located behind the mix position at the top of the rack. This energizies the rear desk audio gear.
#. is just below #2. This energizes the audio amplifiers.

Allow a 10 second pause between flipping each swtich.

After the console has fully started, you would typically want to recall the default scene so all settings are in a known good state.
 
[Back to top](#top) 

## Power Off 

Power off is the opposite sequence from power on.  Provide a 30 second pause between switch 3 and 2. This gives the power amps time to cycle off before proceeding.

[Back to top](#top) 
 
# Basic Operations

## The Two Consoles

>To Be written. 

## Scene Recall 

>To Be written. 

## Operating a Channel

>To Be written. 
 
[Back to top](#top) 

## Audio Recording - Audio CD

To record the sermon or teaching for publication on the web site.
Also serves as a backup for the CD recording.

Key Points:

#. Place a blank CD into the recorder and close the tray. It will take a few moments to recognize the disc type.
#. Press the Auto/Manual (or is it tracking) button on the left hand side to select whether you want new tracks created automatically or not.
#. Press the record button to begin recording
#. Press the record button again to start a new track when desired.
#. Press stop when done. The display will flash a PMA message for a few moments
#. To Finalize. 
    * Press the "Finalize" button, it will think for a moment or three and the display will show a time. (usually 2:01). 
    * Push Play and it will begin finalizing. The time will count down.
    * Eject disc, remove disc
    * Close tray.
#. If for some reason the audio CD was not finalized, put it back into the recorder and pick up the instructions at step #6.

[Back to top](#top)

#Audio Terminology
   
None.  

[Back to top](#top)

`r knit_child('FurtherInformation.Rmd', quiet=TRUE)`

[Back to top](#top)

# Document Source
This document is compiled by merging text and data together using rmarkdown. THe source is found here `r paste0(getwd(),  "/", knitr::current_input())`.

#Change History

`r commit.log.html( knitr::current_input() )`