---
title: "UAC System Operations Guide"
author: "Terry Doner, Technical Director"
date: "`r format(Sys.time(), '%B %d %Y')`"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
classoption: landscape
---

```{r setup, include=FALSE}
require(readr)
require(readxl)
require(knitr)
require(formattable)
require(tidyr)
require(dplyr)
require(kableExtra)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
options(knitr.table.format = "html") # latex for pdf 

base <-  "~/Documents/UACTech/SystemDocumentation"
path <-"~/Documents/UACTech/SystemDocumentation"
inventoryfile <- "TechInventory.xlsx"
fname <- paste(path, inventoryfile, sep="/")
further <- read_excel(fname, sheet = "Further")

```

# Introduction

This document provides an overall view of what needs to happen during Sunday morning with a focus on the corrdination of activities. It is structured around a typical service; any particular service may have variations that need to be accomodated. 

The activities described are structured according to these milestone events. The times are approximate.  

```{r getdata, echo=FALSE, asis=TRUE}
 
f <- paste0(base, "/", "SystemOperationsGuide.xlsx")

ct <- c("numeric" ,"numeric", "text", "numeric","text", "text","text", "text", "text", "text"  )
#"blank", "numeric", "date" or "text"

df <- read_excel(f, 
                 sheet = "linear",
                 col_types=ct) 
 
num2time  <- function(s) {
  hr <- floor(24 * s)
  mi <- round((24*s - hr ) * 60)

  if (nchar(hr) == 1) {
     hr <-paste0("0",hr)
   }
  
  if (nchar(mi) == 1) {
    mi <- paste0("0", mi)
  }
  
  return( paste0( hr, ":", mi ) )
}

df <- df %>% rowwise() %>%
  mutate(Time = num2time(Time1)         )

Events <- df %>%
              select(Time1, Time, Event ) %>%
              unique()

Events %>% 
  select(Time, Event ) %>% 
  kable() %>%
  column_spec(1  , width = "10em") %>%
  kable_styling("striped", full_width = FALSE)
```

[Back to top](#top)

#Summary

```{r summary}
df %>%  
  group_by(  Time, Event, Who) %>%
  summarise(Detail = paste(What, collapse="; ") ) %>% 
  select(Time, Event, Who, Detail ) %>%  
  spread( Who, Detail, fill="") %>%
  ungroup() %>%
  select(Time, Event, Presenter, Video, Audio, Lights,  TD	 ) %>%
  kable( ) %>%
    column_spec(1  , width = "5em") %>%  
    column_spec(2  , width = "5em") %>% 
    column_spec(3:7 , width = "10em") %>%
    kable_styling("striped", full_width = FALSE)
```

#Details

```{r details, results="asis"}
#Rundown by Position and Time

positions <- df %>% select(Who) %>% unique() %>% as.list()
times     <- df %>% select(Time1) %>% unique()%>% as.list()
out <- ""

for (i in  positions$Who  ) {
  p <- i 
  out <- paste(out, "<h2>", p, "</h2>")
  
  for (t in times$Time1) {
    
    s <- num2time(t)
    n <- Events[Events$Time==s,]$Event 
    
    hdr <- paste0("<h3>", s, " - ", n,"</h3>") 
      
    this <- df %>%
       filter(Who == p) %>%
       filter(Time1 == t) %>%
        select(  Where, Where2, What, How, Fallback) %>%
        kable() %>%
        kable_styling("striped", full_width = FALSE)

     out <- paste(out, hdr, this)
  }
}
```

`r out`

[Back to top](#top)

`r knit_child('FurtherInformation.Rmd', quiet=TRUE)`

[Back to top](#top)
