---
title: "System Administration Guide"
author: "Terry Doner"
date: "`r format(Sys.time(), '%B %d %Y')`"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
require(readr)
require(dplyr)
require(readxl)
require(knitr)
require(formattable)
require(kableExtra)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
options(knitr.table.format = "html") 
```

```{r getdata}
path <-"~/Documents/UACTech/SystemDocumentation"
inventoryfile <- "TechInventory.xlsx"
fname <- paste(path, inventoryfile, sep="/")

Creds <- read_excel(fname, sheet = "Credentials")
software <- read_excel(fname, sheet = "Software")
further <- read_excel(fname, sheet = "Further")
```

# Introduction

This document provides key administrative documentation for the AV technical systems at UAC. This material is meant to be disclosed to a few people who may need this information to take over the responsibilities of the technical director.  

# Credentials
One can't manage the systems if you cannot get past userids and passwords, so they need to be protected and shared discretly.

Passwords are not revealed in this document, instead the following tables discloses which passwords exist (PasswordKnown). Terry knows these passwords and a copy will be filed with the Office Administrator.

## Internal Systems
```{r}
Creds %>% 
  mutate(PasswordKnown = !is.na(Password)) %>%
  filter(AssetOrService=="Asset") %>%
  select(ID,	Userid, PasswordKnown, 	Comment) %>%
  rename(AssetTag = ID) %>%
  kable(  ) %>%
  kable_styling("striped", full_width = FALSE) %>%
  column_spec(1, background=rgb(.98,.98,.98) )  
```
## External Services
  
```{r}  
Creds %>% 
  mutate(PasswordKnown = !is.na(Password)) %>%
  filter(AssetOrService=="Service") %>%
  select(ID, URL,	Userid, PasswordKnown, 	Comment) %>%
  rename(Name = ID) %>%
  kable(  ) %>%
  kable_styling("striped", full_width = FALSE) %>%
  column_spec(1, background=rgb(.98,.98,.98) )    
```

# Software
The details of which software is to be installed on every system. A manufacturer value of 'oss' means open source software.
License keys are not exposed in this report.

```{r software}
software %>%
  arrange(InstalledOn, Manufacturer, Title) %>%
  select(InstalledOn, Title, Version, Manufacturer, Comments) %>%
  kable( ) %>%
  kable_styling()  %>%
  collapse_rows(columns = 1 ) %>%
  kable_styling("striped", full_width = FALSE)
```
##Summary by Title
```{r}
with(software, table(Title , InstalledOn)) %>%
  kable()%>%
  kable_styling("striped", full_width = FALSE)
```

[Back to top](#top)

`r knit_child('FurtherInformation.Rmd', quiet=TRUE)`

[Back to top](#top)

# Document Source
This document is compiled by merging text and data together using rmarkdown. The source is found here `r file.path(getwd(), knitr::current_input())`.