---
title: "System Operations - Audio"
author: "Terry Doner"
date: "`r format(Sys.time(), '%B %d %Y')`"
output:
  html_document:
    toc: yes
    number_sections: true
    theme: cosmo
---

```{r options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.table.format = "html") # latex for pdf 
```

```{r setup, include=FALSE}
require(readr)
require(dplyr)
require(readxl)
require(knitr)
require(jpeg)
require(grid)
require(ggplot2)
require(kableExtra)
require(tidyr)
```

```{r functions}
source("commonFunctions.R")
```

```{r data}
inventoryfile <- get.inventory()
activities <- get.activities()
```

# Introduction
This document provides basic operating information for each of the Audio systems at UAC.

Purpose of our Sound System:

* Necessary to help the hearing impaired ( roughly 10% of the population) 
* Supports video recording
* Helps draw attention to the central item – conversely makes it easier to ignore other noise 
* Helps audience to focus and concentrate
* Reinforces the message (spoken or sung)

[Back to top](#top)

# Sunday Morning Rundown
    
These are the steps to follow for a normal Sunday morning.

```{r rundown}
p <- "Audio"
activities %>%
       filter(Who == p) %>%
        mutate(Time = num2time(Time1)) %>%
        replace_na(list(Details="", How="", 
                               Fallback="", Where="", Where2="")) %>%
        select(Time, Event, Where, Where2, What, Details) %>%
        kable(caption=paste("Rundown for Postion:", p)) %>%
        kable_styling("striped", full_width = FALSE) %>%
        collapse_rows(columns = 1:2  )
```    

[Back to top](#top)

# Power On and Off
## Power On
 
There are three numbered swtiches located in the balcony required to turn the system on

#. is located at the far west end of the front desk. This energizes the front desk gear.
#. is located behind the mix position at the top of the rack. This energizies the rear desk audio gear.
#. is just below #2. This energizes the audio amplifiers.

Allow a 10 second pause between flipping each swtich.

After the console has fully started, you would typically want to recall the default scene so all settings are in a known good state.

> Although not part of the audio system it is the audio engineer who turns on portions of lighting and video system as well
 
[Back to top](#top) 

## Power Off 

Power off is the opposite sequence from power on.  Provide a 30 second pause between switch 3 and 2. This gives the power amps time to cycle off before proceeding.

[Back to top](#top) 
 
# Basic Operations

## The Two Consoles

We have two audio consoles in the auditorium. The main console and a sub console to provide expanded input capacity.

Most vocal and stage instruments are wired into the main console (M7CL). Addtional inputs for wireless beltpacks, computers, and palyback machines come in via the sub console. The outputs of the sub console are routed into the corresponding busses of the main console.

The monitor mix busses on both consoles are numbered the same. 

Scene recall on the main console will cause the same numbered scene to be recalled on the sub console as well. 

## Scene Recall 

>TODO: write content

Scenes are a collection of settings that can be stored and recalled together. This is a very effective way of getting to a good known state. We have defined scene #1 and our base scene to use for most things. It is locked so it can not be easily overwritten. If you would like to make a change to this base scene, please discuss with Terry and Mark.

To recall the base scene ... 

>TODO: Need to write instructions and add pictures.

## Operating a Channel

>TODO: write content
 
[Back to top](#top) 

## Audio Recording - Audio CD

To record the sermon or teaching for publication on the web site.
Also serves as a backup for the CD recording.

Key Steps:

#. Place a blank CD into the recorder and close the tray. It will take a few moments to recognize the disc type.
#. Press the Auto/Manual (or is it tracking) button on the left hand side to select whether you want new tracks created automatically or not.
#. Press the record button to begin recording
#. Press the record button again to start a new track when desired.
#. Press stop when done. The display will flash a PMA message for a few moments
#. To Finalize. 
    * Press the "Finalize" button, it will think for a moment or three and the display will show a time. (usually 2:01). 
    * Push Play and it will begin finalizing. The time will count down.
    * Eject disc, remove disc
    * Close tray.
#. If for some reason the audio CD was not finalized, put it back into the recorder and pick up the instructions at step #6.

[Back to top](#top)

# Monitors

>TODO: write content

[Back to top](#top)

# Operating the Wireless Microphones

>TODO: write content

[Back to top](#top)

# Audio Terminology

Amplifier
: An audio component that take low-level inputs, from a console, and amplifies them to the power level required to drive a speaker. 

Bus
: Refers to a logical structure within the console where multiple channels (sources) can contribute an audio signal.

Channel aka Strip
: refers to an input in the console. Typically this is a microphone input or an instrument.

Direct Box
: A device, usually a box, which can interface an instrument, like a electronic keyboard, to an audio console.

Scene
: A collection of setting which can be saved and recalled as a group.

[Back to top](#top)

`r knit_child('FurtherInformation.Rmd', quiet=TRUE)`

[Back to top](#top)

# Document Source
This document is compiled by merging text and data together using rmarkdown. THe source is found here `r file.path(getwd(), knitr::current_input())`.

# Change History

`r commit.log.html( knitr::current_input() )`