---
title: "System Design - Projection"
author: "Terry Doner"
date: "`r format(Sys.time(), '%B %d %Y')`"
output:
  html_document:
    toc: yes
    number_sections: true
    theme: cosmo
---

```{r options, include=FALSE}
options(knitr.table.format = "html") 
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
```

```{r packages}
require(readr)
require(dplyr)
require(readxl)
require(knitr)
require(formattable)
require(kableExtra)
```

```{r functions}
source("commonFunctions.R")
```

```{r data, include=FALSE}
NetworkInventory <- get.network()
Tech_Inventory   <- get.inventory()
further          <- get.further() 
```

## Introduction

This document provides key technical documentation for the video subsystems at UAC. This diagram provides an overview of the major components and leaves out some details. 

```{r}
DiagrammeR::grViz("sdv-topology0-overview.gv")
```


## Video Matrix
The unit is a Kramer VS-88DT which is an 8x8 matrix and can handle both HDMI and HDBaseT formats.

It has 8 inputs and 8 outputs. It can be controlled via the buttons on the front panel or from it's built in web page.

[Back to top](#top)

### Presentation Switcher Inputs 

```{r psi}
psi <- tribble(
~Input, ~Usage, ~Comment,
"1",
"FoH Left",
"Primary computer for video content (including audio).",

2, 
"FoH Centre",
"FUTURE. Alternate which can be used for backup. Advanced presentations and building video while Balcony 1 is in use. |",

3,
"FoH Right",
"Video input for guest computer. Can handle hdmi or VGA.",

4,
"Confidence",
"Video input for Confidence display (rear projector)",

5,
"Backup Presentation",
"Source is Windows running Mediashout and Powerpoint",

6,
"Guest",
"Input for a guest presenter to use.",

7, 
"Video Mix Auxillary",
"Auxillary feed from the ATEM video recording mixer",

8,
"Video Mix",
"Program output is from the ATEM Video Mixer. Use for FOH projection or building distribution.")

psi %>% kable(align="l")   %>%
    kable_styling(bootstrap_options = c("striped", "hover"))


```

[Back to top](#top)

### Video Matrix Outputs

```{r pso}
pso <- tribble(
~Output, ~Usage, ~Comment,
"1", "FoH Projector",
"Front of House projector - Stage Right / East wall.",

"2",
"FoH Projector",
"Front of House projector - Stage Centre / South wall.",

"3",
"FoH Projector",
"Front of House projector - Stage Left / West wall.",

"4", 
"Confidence",
"Projector which covers rear wall in balcony. Lyrics for singers, etc.",

"5", "VMix 4","Secondary feed to Video Mixer",

"6" , "Nursery", "Feed to the Nursery TV.",

"7","Lobby","Feed to the Lobby TV.",

"8","VMix 1","Destination is to the video mixer so projected content can be mixed with camera – Picture-in-Picture, etc."
)

pso %>% kable(align="l")   %>%
    kable_styling(bootstrap_options = c("striped", "hover"))

```

> A potential future output would be an audio feed to the Audio mix console.

[Back to top](#top)

### Video Matrix Configurations
The LCD display on the front of the unit report the current routing topology. The Output row shows the number of the input which is selected for that output. A '0' indicated no source has been selected. Here are two sample configurations.  

#### Normal Service Switcher Configuration 
The display should look like:

|Input |1|2|3|4|5|6|7|8|
|-|:-:|:-:|:-:|:-:|:-:|:-:|:-:|:-:|
|Output|1|2|3|4|1|8|8|2|

```{r normal}
DiagrammeR::grViz("sdv-PSnormal.gv", height=300)
```

[Back to top](#top)

## Topologies
There are a lot of components to the system. One big diagram is daunting. It has been broken down into smaller portions to be more consumable. 

[Back to top](#top)

### Computer Topology
There are three computers in the system:

CDWU-0009 Windows / Mediashout
: The windows system runs Mediashout and has a dual output video card. One is used for the operator display, and the second for presentation. It also has Powerpoint for Windows installed.

CDMU-A001 MacOS / ProPresenter
: This system runs ProPresenter and has a built in operator display, and a displayport output to the datapath video processor which split the output to three separate video signals for the front projectors, and a separate video output that drives the rear confidence montitor. It also has Powerpoint for Mac and Keynote installed.

CDMU-A002 MacOS / QLC - ATEM - OBS
: This system runs lighting (QLC+), ATEM switcher software, and OBS (for streaming) and can also run things like Skype. It has a USBC-HDMI adapter that is direct connected to Input 2 of the video mixer.

```{r topComp}
DiagrammeR::grViz("sdv-topology1-computer.gv")

selected.at <- c(
              "CDWU-0009", "CDMU-A001", "CDMU-A002",
              "ZVKU-A001", "ZVKU-A002" , "ZVKU-A003" ,
              "ZVIU-A004") 

Tech_Inventory %>%
   filter( AssetTag %in% selected.at) %>% 
    select(AssetTag, Manufacturer, Model, Desc ) %>%
    arrange( AssetTag ) %>%
    kable(align="l")   %>%
    kable_styling(bootstrap_options = c("striped", "hover"))

```

[Back to top](#top)

### Projection Topology
Long distance signal transmission is achieved using Cat5 or Cat6 cabling. This used to require discrete transmitters and receviers, and those are in use for the front of house (FoH) projectors. But there is now a industry standard solution called HDBaseT which is now appearing on professional grade equipment; this is used for the read confidence projector and is why that portion of the diagram is so much simpler.
 
```{r topProj}
DiagrammeR::grViz("sdv-topology2-projection.gv")
```

The old projection system is still installed but not in active service. Nor does it have a video source connected.
```{r}
DiagrammeR::grViz("sdv-topology2-projection-old.gv")
```

```{r}
selected.at <- c(
              "ZVKU-A001", 
              "ZVVU-0001",
              "ZVVU-A001", "ZVVU-A002", "ZVVU-A003", 
              "ZVVU-0004",  "ZVVU-0005"
              )

Tech_Inventory %>%
    filter(AssetTag %in% selected.at) %>% 
    select(AssetTag, Manufacturer, Model, Desc ) %>%
    arrange( AssetTag ) %>%
    kable(align="l")  %>%
    kable_styling(bootstrap_options = c("striped", "hover"))

```

[Back to top](#top)

### Lobby Topology
The TV in the lobby gets its content from the video matrix. For the main service it should get its feed from the video mixer program output. 

```{r topLobby}
DiagrammeR::grViz("sdv-topology3-lobby.gv")

selected.at <- c(
              "ZVKU-A001" , "ZVIU-A002", "ZVVU-0003"
              ) %>%
      data.frame(AssetTag=.)

merge( Tech_Inventory, selected.at) %>% 
    select(AssetTag, Manufacturer, Model, Desc ) %>%
    arrange( AssetTag ) %>%
    kable(align="l") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))

```

[Back to top](#top)

### Nursery Topology
The TV in the nursery gets its content from the video matrix. For the main service it should get its feed from the video mixer program output.

Alternately it can be switched to the Bluray player.

```{r top3}
DiagrammeR::grViz("sdv-topology4-nursery.gv")

selected.at <- c(
              "ZVKU-A001", "ZVIU-A001", 
              "ZVPU-0001", "ZVVU-0002"
              ) %>%
      data.frame(AssetTag=.)

merge( Tech_Inventory, selected.at) %>% 
    select(AssetTag, Manufacturer, Model, Desc ) %>%
    arrange( AssetTag ) %>%
    kable(align="l") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))

```
The TV and the Bluray player each have a remote control.

[Back to top](#top)

### Recording Topology
The recording topology is quite complex and so it is broken up into peices.

#### Inputs
```{r}
DiagrammeR::grViz("sdv-topology5-rec-inputs.gv", height=350)
```

#### Outputs
```{r top4}
DiagrammeR::grViz("sdv-topology5-rec-outputs.gv", height=350)
```

#### Web Presenter
There are some details on the signal path between the Video Mixer and the Web Presenter that need to be documented.
```{r wp}
DiagrammeR::grViz("sdv-topology6-rec-wp.gv", height=350)
``` 

```{r}
selected.at <- c(
              "ZVKU-A001" , 
              "ZVCU-A001", "ZVCU-A002", "ZVCU-A003",
              "ZVKU-A003", "ZVKU-A004", 
              "ZVRU-A001", "ZVRU-A002",
              "ZVIU-A004",
              "CDMU-A002"
              ) 

Tech_Inventory %>%
    filter( AssetTag %in% selected.at) %>% 
    select(AssetTag, Manufacturer, Model, Desc ) %>%
    arrange( AssetTag ) %>%
    kable(align="l") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))

```

The details of the network configuration are not shown. See the Network design document for technically accurate descriptions.

[Back to top](#top)

# Network Details

```{r} 
NetworkInventory %>% 
filter(Category=="Video") %>% 
select(AssetTag, Location, Usage, Device, MAC, IP, URL, Notes) %>%
  arrange(AssetTag) %>%
  kable()   %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

[Back to top](#top)

# Video Equipment Inventory

```{r inventory, echo=FALSE, asis=TRUE}
 
cs = c("AssetTag", "Qty"  ,
  "Manufacturer" ,
  "Model"  , 
  "Qty",
  "Location"  ,
  "Type" ,
  "Desc"     )

Video_Inventory <- Tech_Inventory %>%  
          filter( Category=="Video" , InService== "Y") %>%  
          dplyr::select(one_of(cs))   

knitr::kable(Video_Inventory  )   %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
```

[Back to top](#top)

`r knit_child('FurtherInformation.Rmd', quiet=TRUE)`

[Back to top](#top)

# Document Source
This document is compiled by merging text and data together using rmarkdown. The source is found here `r file.path(getwd(), knitr::current_input())`.

#Change History

`r commit.log.html( knitr::current_input() )`