---
title: "UAC System Operations Guide"
author: "Terry Doner, Technical Director"
date: "`r format(Sys.time(), '%B %d %Y')`"
output:
  html_document:
    toc: yes
    number_sections: true
    theme: cosmo
classoption: landscape
---

```{r options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
options(knitr.table.format = "html") # latex for pdf 
```

```{r packages}
require(readr)
require(readxl)
require(knitr)
require(formattable)
require(tidyr)
require(dplyr)
require(kableExtra)
```

```{r functions}
source("commonFunctions.R")
```


```{r getdata}
Activities <- get.activities()
Events <- get.events() 
further <- get.further()
```

# Introduction

This document provides an overall view of what needs to happen during Sunday morning with a focus on the corrdination of activities. It is structured around a typical service; any particular service may have variations that need to be accomodated. 

The activities described are structured according to these milestone events. The times are approximate.  

```{r events, echo=FALSE, asis=TRUE}
Events %>% 
  select(Time, Event ) %>% 
  kable() %>%
  column_spec(1  , width = "10em") %>%
  kable_styling("striped", full_width = FALSE, position="center")
```

[Back to top](#top)

#Summary

```{r summary}
Activities %>%  
  group_by(  Time, Event, Who) %>%
  summarise(Detail = paste(What, collapse="; ") ) %>% 
  select(Time, Event, Who, Detail ) %>%  
  spread( Who, Detail, fill="") %>%
  ungroup() %>%
  select(Time, Event, Presenter, Video, Audio, Lights,  TD	 ) %>%
  kable( ) %>%
    column_spec(1  , width = "5em") %>%  
    column_spec(2  , width = "5em") %>% 
    column_spec(3:7 , width = "10em") %>%
    kable_styling("striped", full_width = FALSE)
```

#Rundown by Time

```{r}
times     <- Activities %>% select(Time1) %>% unique()%>% as.list()
out <- ""

for (t in times$Time1) {
    
    s <- num2time(t)
    n <- Events[Events$Time==s,]$Event 
    
    hdr <- paste0("<h3>", s, " - ", n,"</h3>") 
      
    this <- Activities %>%
       filter(Time1 == t) %>%
       arrange(Item) %>%
        select(Who,  Where, Where2, What, How, Details, Fallback) %>%
        kable( ) %>%
        kable_styling("striped", full_width = TRUE)

     out <- paste(out, hdr, this)
}
```
`r out`

#Rundown by Position and Time

```{r details, results="asis"}
#Rundown by Position and Time

positions <- Activities %>% select(Who) %>% unique() %>% as.list()
times     <- Activities %>% select(Time1) %>% unique()%>% as.list()
out <- ""

for (i in  positions$Who  ) {
  p <- i 
  out <- paste(out, "<h2>", p, "</h2>")
  
  for (t in times$Time1) {
    
    s <- num2time(t)
    n <- Events[Events$Time==s,]$Event 
    
    hdr <- paste0("<h3>", s, " - ", n,"</h3>") 
      
    this <- Activities %>%
       filter(Who == p) %>%
       filter(Time1 == t) %>%
        select(  Where, Where2, What, How, Fallback) %>%
        kable(caption=paste("Postion:", p, "@", s)) %>%
        kable_styling("striped", full_width = FALSE)

     out <- paste(out, hdr, this)
  }
}
```

`r out`

[Back to top](#top)

`r knit_child('FurtherInformation.Rmd', quiet=TRUE)`

[Back to top](#top)

#Change History

`r commit.log.html( knitr::current_input() )`
