---
title: "System Design - Audio"
author: "UAC Media Arts"
execute: 
  eval: true
  echo: false
  warning: false
  message: false
format:
  html:
    toc: true
  pdf:
    toc: true
  titlepage-pdf:
    toc: true
always_allow_html: yes
---

```{r packages, include=FALSE}
source("commonPackages.r")
```

```{r functions}
source("commonFunctions.r")
```

```{r getdata}
credentials <- get.credentials()
software    <- get.software()
```

# Introduction

This document provides key administrative documentation for the AV technical systems at UAC. This material is meant to be disclosed to a few people who may need this information to take over the responsibilities of the Technical Manager.  

# Credentials
One can't manage the systems if you cannot get past userids and passwords, so they need to be protected and shared discretly.

Passwords are not revealed in this document, instead the following tables discloses which passwords exist (PasswordKnown). Terry knows these passwords and a copy will be filed with the Office Manager.

## Internal Systems
```{r}
credentials %>% 
  mutate(PasswordKnown = !is.na(Password)) %>%
  filter(AssetOrService=="Asset") %>%
  select(ID,	Userid, PasswordKnown, 	Comment) %>%
  rename(AssetTag = ID) %>%
  gt(  ) |>
  opt_stylize(style=5) 
```

## External Services
  
```{r}  
credentials %>% 
  mutate(PasswordKnown = !is.na(Password)) %>%
  filter(AssetOrService=="Service") %>%
  select(ID, URL,	Userid, PasswordKnown, 	Comment) %>%
  rename(Name = ID) %>%
  gt(  ) |>
  opt_stylize(style=5)  
```

# Software

The details of which software is to be installed on every system. A manufacturer value of 'oss' means open source software.
License keys are not exposed in this report.

```{r software}
software %>%
  arrange(InstalledOn, Manufacturer, Title) %>%
  select(InstalledOn, Title, Version, Manufacturer, Comments) %>%
  gt(  ) |>
  opt_stylize(style=5) 
```

## Summary by Title

```{r}
 software |>
	mutate(installed = "X") |>
	select(Title,InstalledOn, installed ) |>
	pivot_wider(names_from = "InstalledOn", values_from = "installed" ) |>
    gt(  ) |>
    opt_stylize(style=5) 
```

# Server Applications

Three custom server applications run on the video computer **CUMU-G001** under the `avuser` account. All are managed with a `run.sh` script in their respective directories under `/Users/avuser/`.

## AVL Tech Assistant (`avltechassistant`) {#sec-avltechassistant}

### Purpose

A web-based documentation and asset management tool for the AV/Lighting technical systems. Provides asset search, connectivity diagrams, signal path finding, rack location views, a knowledge base, and an operational dashboard.

### Architecture

| Component | Technology | Port |
|-----------|-----------|------|
| Frontend | Python `http.server` serving static HTML/CSS/JS | 8080 |
| Backend | FastAPI + uvicorn | 9000 |
| Data | Excel spreadsheets (`/data/*.xlsx`) | — |
| Diagrams | Graphviz (`dot`) | — |

The frontend is a single-page application (`index.html`) that calls the backend REST API. The backend reads asset, cable, network, and knowledge base data from `.xlsx` files at startup (reloadable via the UI). Connectivity diagrams are rendered server-side using Graphviz and returned as SVG.

The backend also proxies manual lookups to the `media_arts_home` server (see below), rewriting relative file URLs to absolute before returning them to the browser.

### Source Code

GitHub: `https://github.com/avmaint/avltechassistant` (private, owned by `avmaint` account; `donert` is a collaborator)

### Directory Layout

```
avltechassistant/
  backend/
    main.py           # FastAPI application
    requirements.txt
  frontend/
    index.html
    script.js
    style.css
    full.render.js
  tests/
    run_tests.py
  data/               # symlink → ../data  (xlsx data files live outside the repo)
  run.sh
```

### Dependencies

- Python 3 with virtual environment (`.venv/`)
- Graphviz — installed via MacPorts at `/opt/local/bin/dot`; must be on PATH

### Installation (first time on a new machine)

```bash
cd /Users/avuser/avltechassistant
./run.sh install        # creates .venv and installs Python packages
ln -s ../data data      # point to shared data directory if not already present
```

Ensure `/opt/local/bin` is on the PATH used by the shell that launches the app (add to `~/.zshrc`):

```bash
export PATH="/opt/local/bin:$PATH"
```

### Deployment (updating to latest code)

```bash
cd /Users/avuser/avltechassistant
./run.sh deploy         # git pull + pip install
./run.sh restart        # stop and start both services
```

### Start / Stop

```bash
./run.sh start          # starts frontend (8080) and backend (9000) as background daemons
./run.sh stop           # stops both
./run.sh restart        # stop then start
```

Logs: `frontend.log` and `backend.log` in the repo root directory.

---

## Media Arts Home (`media_arts_home`) {#sec-media-arts-home}

### Purpose

An internal web server providing:

- **Documentation browser** — rendered HTML versions of the Quarto system design documents
- **Manuals browser** — PDF equipment manuals indexed by asset tag
- **Messages board** — operational notes visible to the tech team

### Architecture

| Component | Technology | Port |
|-----------|-----------|------|
| Web server | Flask (Python) | 80 |
| Docs | Static HTML files in `docs/` directory | — |
| Manuals | PDF files in `manuals/` directory | — |
| Manual index | `manuals/assets_manuals_index.json` | — |

### Source Code

GitHub: `https://github.com/avmaint/media_arts_home` (private)

### Key API Endpoints

| Endpoint | Description |
|----------|-------------|
| `GET /` | Home page |
| `GET /docs/` | Documentation index |
| `GET /docs/<filename>` | Serve a documentation file |
| `GET /manuals/` | Manuals index |
| `GET /manuals/files/<path>` | Serve a PDF manual |
| `GET /api/manuals/<asset_tag>` | JSON list of manuals for an asset |
| `GET /api/messages` | Retrieve operational messages |
| `POST /api/messages` | Post a new message |

### Installation (first time)

```bash
cd /Users/avuser/media_arts_home
./run.sh install        # creates .venv and installs Flask
```

Publish content after first install:

```bash
./scripts/publish_docs.sh       # copies rendered HTML docs into docs/
./scripts/publish_manuals.sh    # copies PDFs and builds manuals index
```

### Deployment (updating)

```bash
cd /Users/avuser/media_arts_home
./run.sh deploy         # git pull + pip install
./run.sh stop
./run.sh start
```

### Start / Stop

```bash
./run.sh start          # starts Flask on port 80 as a background daemon
./run.sh stop
```

Log: `server.log` in the repo root directory.

---

## CueCommander {#sec-cuecommander-admin}

{{< include common_CueCommander.qmd >}}

### Installation & Startup

CueCommander runs on the Node-RED platform. Node-RED is installed as a global npm package and starts automatically when `avuser` logs in via an Apple Automator script.

To start or restart manually:

```bash
node-red start
```

The web interface is available at `http://192.168.0.206:1880/ui`.

Source code: `https://github.com/donert/CueCommander-NR` (public)

---

## Quick Reference — All Services

| Application | URL | Port | Run script location |
|-------------|-----|------|-------------------|
| AVL Tech Assistant | `http://192.168.0.206:8080` | 8080 / 9000 | `/Users/avuser/avltechassistant/run.sh` |
| Media Arts Home | `http://192.168.0.206` | 80 | `/Users/avuser/media_arts_home/run.sh` |
| CueCommander | `http://192.168.0.206:1880/ui` | 1880 | Automator / `node-red` |

{{< include common_trailer.qmd >}}
