---
title: "Team Design"
author: "Terry Doner"
date: "`r format(Sys.time(),  '%B %d %Y')`" 
output:
  html_document:
    toc: yes
    toc_depth: 2
---
<a id="top"></a>
```{r options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE )
options(knitr.table.format = "html") 
```

```{r packages}
require(kableExtra)
require(readxl)
require(dplyr)

require(xtable)
require(formattable)
require(DiagrammeR)

require(knitr)
require(kableExtra)
```

```{r functions}
source("commonFunctions.R")

positionString2 <- function(tid) {
skid <- subset(teamskill, TeamID == tid & IsLead == "Y")$Skill

pid <- subset(peopleskill,  Skill == skid )$PersonID

p.name <- people %>% filter(PersonID == pid) %>%
        mutate(Name = paste(FirstName, LastName)) %>%
        select(Name) %>% 
        pull()

parent.tid <- subset(teamstructure, TeamID==tid)$ParentTeamID

parent.tn  <- subset(teamstructure, TeamID==parent.tid)$TeamName

parent.skill <- subset(teamskill, TeamID==parent.tid & IsLead == "Y")$Skill 

parent.lead <- subset(peopleskill, Skill==parent.skill)$PersonID
parent.lead.row <- subset(people, PersonID == parent.lead)
parent.lead.name <- paste(parent.lead.row$FirstName, parent.lead.row$LastName)

s <- paste0("The ",  skid, " (" , p.name,  ") reports to the ",
           parent.tn, ". The leader of that team is ",
            parent.lead.name, ".")
s}

team.members <- function(tid) {
  skills.on.team <- subset(teamskill, TeamID == tid)
  
  merge(skills.on.team, peopleskill) %>%
  merge(people) %>%
  filter(IsLead == "N") %>%
  arrange(FirstName, LastName) %>%
  select(FirstName, LastName, Skill) %>%
  kable(caption = "Team Members") %>%
  kable_styling(bootstrap_options = c("striped", "hover"),
  full_width = FALSE)
}

team.matrix <- function(tid) {
  
    skills.on.team <- subset(teamskill, TeamID == tid)

    merge(skills.on.team, peopleskill) %>%
    merge(people) %>%
    mutate(Name = paste(FirstName, LastName)) %>%  
    select(Name, Skill) %>%
    table() %>%
    kable(caption="Skills Matrix") %>%
    kable_styling(bootstrap_options = c("striped", "hover"),
                   full_width = FALSE)
}
```

```{r data ,results='asis', echo=FALSE}
teamstructure <- get.teamstructure()  

teamskill <- get.teamskill()  

people <- get.people(  )

peopleskill <- get.peopleskill()

positionString <- function(s) {
  
  thisname <- org.df %>% 
    dplyr::filter( position == s) %>% 
    dplyr::select(who)
  thisname <- thisname$who %>% as.character()
  
  bossTitle <- org.df %>% dplyr::filter( position == s) %>% dplyr::select(reportsTo)
  bossTitle <- bossTitle$reportsTo  %>% as.character()
  bossName <- org.df %>% dplyr::filter(position == bossTitle) %>% dplyr::select(who)
  bossName <- bossName$who
  
  t <- paste0("The ",  s, " (" , thisname,  ") reports to the ", bossTitle, " (", bossName, ")." )
  
  return(t)
}
```

#Introduction

A clear understanding of the roles and responsibilities within a team is always important. Even more so within a church volunteer environment where are relationships are much more complex than what they might be in a secular workplace. This document outlines the many roles within the Technical Arts organization. 

Let's start with the overall team structure. This represents the structure we have planned, and overtime each of the Lead positions should be replaced by a different name. 

```{r overallorg  }
nodes <- merge(teamstructure, teamskill) %>%
         filter(IsLead == "Y") %>%
         merge(peopleskill) %>% 
         merge(people) %>% #now do the formatting
         mutate(nodename = TeamID) %>%
         mutate(line1 = paste(FirstName, LastName)) %>%
         mutate(line2 = Skill) %>%
         mutate(colour = '#D7F2D5') %>%
         select(nodename, line1, line2, colour)
      
edges <- teamstructure %>%
         mutate(to   = TeamID) %>%
         mutate(from = ParentTeamID) %>%
         filter(from != "boe") %>%
         filter(to   != "boe") %>%
         select(from, to)

org.header  <- "
digraph org { 
graph [overlap = true, fontsize = 30, rankdir=LR 
      label='Organizational Chart',
      fontname = Helvetica]

node [shape=Mrecord, tooltip='',  fontsize = 16, style=filled  
       ]
" 

org.nodes <- nodes %>%
           mutate(node = paste( nodename, "[label='", line1, "|", line2, "'" ,   ",fillcolor='", colour , "'  ]\n"  ) ) %>%
           select(node) %>%
           unlist() %>% paste( collapse=" ")


org.edges <- edges %>%    
         mutate(edge = paste0( from, "->", to )) %>% 
         select(edge) %>%
         unlist() %>% paste( collapse=" ")

org.footer <- "}"

org <- paste(org.header, org.nodes, org.edges, org.footer)

DiagrammeR::grViz(org)

```

#Team Descriptions

```{r}
 
```


##Technical Arts Team
```{r}
tid <- "tech"
```
`r positionString2(tid)`

[Back to top](#top)

##Audio Team
```{r}
tid <- "audio"
```
This team manages the audio console and the sound that we hear.
`r positionString2(tid)`
`r team.matrix(tid)`

[Back to top](#top)

##Presentation Team
```{r}
tid <- "presentation"
```
This team manages ProPresenter and the things we see on the projection screens.
`r positionString2(tid)`
`r team.matrix(tid)`

[Back to top](#top)

##Video Team
```{r}
tid <- "video"
```
This team manages the video recording for distribution within the building, recording, projection (as needed) and livestreaming.
`r positionString2(tid)`
`r team.matrix(tid)`

[Back to top](#top)

##Lighting Team
```{r}
tid <- "lighting"
```
This team manages our lighting design and operation. 
`r positionString2(tid)`
`r team.matrix(tid)`

[Back to top](#top)

##Stagecraft Team
```{r}
tid <- "stage"
```
The stagecraft team manages the physical design elements we place on the stage. The purpose is to add visual interest to the stage. These physical elements are often illuminated by the lights and can either be abstract or tied into the theme of the season or series.  
`r positionString2(tid)`
`r team.matrix(tid)`

# Job Descriptions

All of these positions share some requirements in common:

1. A spiritual call to this ministry.
2. A servant spirit -- we all need to serve one another and technical support serves the production technology needs of all participants.
3. Eagerness to learn.

The description for each position below expands on these with role specifics needs.

[Back to top](#top)

## Worship Leader

###Responsibilities
The full job description of this position is not in the scope of this document.

>todo add commentary about the relationship between this job and the rest of these jobs.
 

## Technical Manager

###Responsibilities
1.	Oversee the operation and maintenance of the sanctuary sound system, theatre lighting, video and computer projection systems and all other AV equipment on campus. This task includes:
    + Regular checks of the equipment for malfunctions and making repairs or getting repairs performed as required.
    +	Ensuring that a good supply of consumables are on hand: spare lamps for the theatre lights,  video projectors, batteries, CD blanks, and gaffe/duct tape.
    +	Maintenance of a formal equipment inventory.
    +	Ensuring that the technical spaces are clean and tidy.
2.	Recruit and train technical staff.
    +	This is a difficult part of the job. Not everyone who wants to twist knobs is suited to the job. Commitmentt, punctuality, attention to detail, a willingness to learn from the present staff as well as do independent learning is vital. 
3.	Schedule Crews for all services.
    + This task includes:
        + Maintain the schedule and coordinate last minute changes. Scheduling is managed via Planning Center Online.
        + Be the point of contact for events outside the regular service schedule, such as weddings, funerals and outside groups wanting to use the facilities.
4.	Liase between the church and outside suppliers for rentals, purchases, etc.
    + This task includes:
        + Advise the Facilities Committee on projected equipment needs.
        +	Know who the suppliers of equipment and services are and be able to negotiate the best rates.
        + Establish relationships with key suppliers
5. Be the primary contact for facility users who require technical support.
    +	This task includes:
        +	Be available to all users of the church facility to advise them of the capabilities of the installed systems and how to enhance them as required. Eg. renting extra lighting equipment.
6.	Budgeting.
    + Prepare planned expenditures for the coming fiscal year and manage within that plan.
    + Forecast large expenditures for at least three years beyond the next year to minimize surprises and allow for good long term financial management.
7. Manage online service used by the eminstry
    + Example, Dropbox, Vimeo

[Back to top](#top)

## Audio Lead
 
###Responsibilities

1. An appropriate technical knowledge of sound reinforcement.  
2. Ability and willingness to train and supervise others.
3. Collaboration with the Worship Leader on the goals and design of the worship set.
5. Assist with the maintenance  audio equipment inventory.
6. Manage the audio equipment, overseeing the repair or replacement of failed equipment, planning preventive maintenance, 
7. Contributing to budget planning.
8. Planning and executing on the long term strategy for the audio systems
9. The ability to reconfigure the system as needed. 

[Back to top](#top)

## Audio Crew
 
###Responsibilities

1. Availability during the week for rehearsal. 
2. Working with the worship leader for each event to ensure all details are understood.
3. Critical listening of our productions to detect problems and make improvements.
4. Ensuring audio cues are executed without fault.
 
[Back to top](#top)

## Lighting Lead
 

###Responsibilities

1. An appropriate technical knowledge of lighting design.  
2. Ability and willingness to train and supervise others.
3. Collaboration with the Worship Leader on the goals and design of the service.
5. Assist with the maintenance  lighting equipment inventory.
6. Manage the lighting equipment, overseeing the repair or replacement of failed equipment, planning preventive maintenance, 
7. Contributing to budget planning.
8. Planning and executing on the long term strategy for the lighting systems
9. Understanding of the safety principles and practices for working at height.
10. An understanding of how lighting control systems work and in particular how the system as installed at UAC works. The ability to reconfigure the system as needed. 

[Back to top](#top)

## Lighting Crew
 
###Responsibilities

1. Availability during the week for rehearsal. 
2. Working with the worship leader for each event to ensure all details are understood.
3. Critical observation of our productions to detect problems and make improvements.
4. Ensuring lighting cues are executed without fault.
5. An working understand of colour theory as applied to lighting design. 
6. An understanding of how lighting control systems work and in particular how the system as installed at UAC works.

[Back to top](#top)
 
## Presentation Lead

###Responsibilities

1. An appropriate technical knowledge of presentation system design.  
2. Ability and willingness to train and supervise others.
3. Collaboration with the Worship Leader on the goals and design of the service.
5. Assist with the maintenance  presentation equipment inventory; computers, video switches, and projectors.
6. Manage the presentation equipment, overseeing the repair or replacement of failed equipment, planning preventive maintenance, 
7. Contributing to budget planning.
8. Planning and executing on the long term strategy for the presentation systems
10. An understanding of how the presentation control systems work as installed at UAC works. The ability to reconfigure the system as needed. 

[Back to top](#top)

## Presentation Crew

###Responsibilities

1. Availability during the week for rehearsal. 
2. Working with the worship leader for each event to ensure all details are understood.
3. Critical observation of our productions to detect problems and make improvements.
4. Ensuring computer cues are executed without fault.
5. An understanding of how the advanced features of ProPresenter work
6. Ability to operate the video matrix switch to get the right content on the right display.

[Back to top](#top)

## Video Lead

###Responsibilities

1. An appropriate technical knowledge of video system design and operation.  
2. Ability and willingness to train and supervise others.
3. Collaboration with the Worship Leader on the goals and design of the service.
5. Assist with the maintenance  video equipment inventory; computers, video switches, and cameras.
6. Manage the video equipment, overseeing the repair or replacement of failed equipment, planning preventive maintenance, 
7. Contributing to budget planning.
8. Planning and executing on the long term strategy for the presentation systems
10. An understanding of how the video control systems work as installed at UAC works. The ability to reconfigure the system as needed.
11. An understanding and working ability of video production practises. Specifically camera angle selection, cutting, fading, keying.

[Back to top](#top)

## Video Crew 
 
###Responsibilities

1. Availability during the week for rehearsal. 
2. Working with the worship leader for each event to ensure all details are understood.
3. Critical observation of our productions to detect problems and make improvements.
4. Ensuring video cues are executed without fault.
5. An understanding and working ability of video production practises. Specifically camera angle selection, cutting, fading, keying.
6. Ensuring that all video media needed for recording or live streaming has been prepared and available for use during the service, such as titles and bumpers. 

[Back to top](#top)

## Stagecraft Lead

###Responsibilities

1. An appropriate knowledge of set design and construction.  
2. Ability and willingness to train and supervise others.
3. Collaborate with the Ministry team on their long range plans to assess the themes in the upcoming series 
4. Contributing to budget planning.
5. A working understanding of safe set design, including physical and fire safety.
6. Collaborate with the stagecraft team members and the other department leads to determine the elements to be constructed.
7. Manage budget
8. Acquire and manage materials
9. Schedule team activities
10. Install and deinstall elements as per plan.

[Back to top](#top)

## Stagecraft Crew
 
The stagecraft team constructs things like this. http://pin.it/hD_vg0k

### Skills needed by the team:

* Carpentry
* Light mechanical (nuts, bolts and brackets)
* Painting
* Rigging (making sure stuff can't fall over)
* Painters
* Electrical (plug things in & low voltage wiring)
* Creatives 
 
I would expect we would do a project for every series. Sometimes we may just remix what we already had. Also expect a project for special events.

###Responsibilities
 
[Back to top](#top)
 
# WL Assistant 

###Responsibilities

####Series / Seasonal Planning
#. Identify production elements (video, staging, music)
#. Commmunicate details of the execution to other teams 
#. Plan and execute preparation
#. Checkpoint with ministry staff 

####Weekly planning
#. Review service plan, ensuring all elements are understood
#. Ensure all production elements are in place
#. If communion Service, understand the distribution plan (come forward, served)
#. Checkpoint with ministry staff
#. Ensure needed supplies are in place (coffee, cream, milk, other)

####Service Execution

#. Unlock front doors
#. Turn on lobby and bathroom lights
#. Turn on the ceiling fans
#. Make coffee for worship team
#. Ensure order of service is correct and printed
#. Print/Distribute and last minute sheet music
#. Ensure all elements in place
#. Communicate last minute changes to interested parties. 
#. Ensure lobby is in order
#. Before countdown, ensure sanctuary is ready: doors closed, walk-in lighting set, stage clean. 
#. Ensure fans are turned off before the message

[Back to top](#top)

`r knit_child('FurtherInformation.Rmd', quiet=TRUE)`

[Back to top](#top)

# Document Source
This document is compiled by merging text and data together using rmarkdown. The source is found here `r file.path(getwd(), knitr::current_input())`.

#Change History
 
`r commit.log.html( knitr::current_input() )`

```{r eval=FALSE, echo=FALSE}
Refactored data model.

1. Team Structure  
~TeamID, ~TeamName, ~ParentTeamID

2. Team Skill
~TeamID, ~Skill

3. People
~PersonID, ~FirstName, ~lastName

4. Person-Skill
~PersonID, ~Skill
```