---
title: "Tech Team Intro"
author: "Terry Doner"
date: "`r format(Sys.time(), '%B %d %Y %H:%M')`"
output:
  html_document:
    toc: yes
    number_sections: true
    theme: cosmo
---

```{r options, message=FALSE, warning=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE)
knitr::opts_chunk$set(warning = FALSE, warnings=FALSE)
options(knitr.table.format = "html") 
```

```{r packages}
require(knitr )
require(dplyr)
require(kableExtra)
require(readxl)
require(here)
```

```{r functions}
source("commonFunctions.R")
```

# Team Overview
 
What we do as a team ties back to what we are to be doing as the local body of Christ. 

UAC Mission
: To Lead people to know Jesus Christ and to follow Him passionately.

UAC Vision
:   Touching our World through Jesus one life at a time!
 
As a tech team we very much lead from the rear - of the sanctuary. But what we do with sound and light is very much upfront. We use those elements on Sunday morning to lead the congregation on a journey. 
 
There are five sub-teams to the tech team.

Audio
: This team manages the audio console and the sound that we hear both in the house and on-line. 

Lighting
: This team manages our lighting design and operation. 

Presentation
: This team manages ProPresenter and the things we see on the projection screens

Video
: This team manages the video recording for distribution within the building, recording, projection (as needed) and livestreaming.

Stagecraft
: [Future] The stagecraft team manages the physical design elements we place on the stage. 
 
There is a much more detailed description of each role in [Team Design](./TeamDesign.html) document.

There is a operations booklet for each role. You should read the booklet for your role. 
 
# General Logistics
 
The anchor of our Sunday morning activities is the service order (aka cue sheet). It is our guide for what will happen and in what order. The Worhship Leader tries to get a solid draft of the service order by mid-week (Tuesday or Wednesday) so we can assemble the ProPresenter Playlist details and give it to Worship Leader to review on Thursday (via dropbox). 

There will also be adjustments to make Sunday morning and we try to put enough effort in during the week to ensure we have the capacity to comfortably deal with things that are truly last minute on Sunday morning. "Planning Center Online” is our main tool for building and communicating the service order.
 
It is ideal for a volunteer to take a shift at their job every 3 or 4 weeks. More frequent is a lot to ask of somebody and can burn them out. Less frequent and they can become out of practice between rotations. Once again, "Planning Center Online” is our tool for managing everybody’s schedule.
 
Also, we have rehearsal on Sunday morning at 8:15am. Audio and presentation must be ready to roll by the start of rehearsal. Lighting and Video can start later most Sundays.The worhsip team has a short devotional prior to 8:15 and we are encouraged to join that. 
 
# Our Tools

## Planning Centre Online
 
["Planning Centre Online”](https://www.planningcenteronline.com) (PCO) is pretty important. As a new team members you will receive an invite to the web site. Once you have setup an account and password you will be able to do several key things:
Manage your contact information
Configure things like how often you would like to serve
Block out dates on the calendar for dates when you are not available to serve
Accept and decline requests to take shift
View the service order for the services for which you are serving.
 
You can also use your cell phone for these things. There is an app you can load on your phone. And you can accept or decline requests to serve using txt messaging.
 
## Slack
 
[Slack](https://unionvillealliance.slack.com) is a tool that we use to discuss the details of Sunday morning. These conversations help us all work together; a forum where we can toss around ideas about an upcoming service (or series) or share tips on various topics. Each of these would have a channel. 
 
Slack is not a replacement for PCO. Slack is where we can talk about ideas and intention. PCO is the actual plan. 
 
Whenyou see an invite in your in-box you will know what it is about. 

## Dropbox

We use Dropbox a lot to share graphics and other content between staff and the balcony computers. You won't need to have a dropbox account yourself. And in day-to-day usage it is just a folder on each of the computers where files magically appear. 
 
## txt
 
During a service we often use txt messaging to communicate between people who are serving during the service. So it can be a help to have your cell phone with you (on vibrate!) and share your number with the others, particularly Kesha and Colin. It is most usually her who needs to inform us of a change or ask us to do something.

## RightNowMedia for Training

We have built a series of training videos which are published via [RightNowMedia](https://www.rightnowmedia.org/trainingv2/mytraining). The full list of training material for each role can be found in the operations guide for each role.   If you don't have an account with RIghtNow, you can sign up for free here: [UAC's RightNow resources](https://uachome.org/rightnow)
 
# Thanks
Thanks to everybody for the role you play on the team. 

Terry Doner<br/>
Technical Director<br/>
Unionville Alliance Church<br/>

[Back to top](#top)

`r knit_child('FurtherInformation.Rmd', quiet=TRUE)`

[Back to top](#top)

<div style="page-break-after: always;"/> 

# Document Source
This document is compiled by merging text and data together using rmarkdown. The source is found here `r file.path(getwd(), knitr::current_input())`.

# Change History

`r commit.log.html( knitr::current_input() )`