---
title: "Tech Home Page"
output: html_document
---
Here are all the links to web pages you might need today. 
[Detailed documentation](./index.html) is available.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
options(knitr.table.format = "html") # latex for pdf 

require(readr)
require(dplyr)
require(readxl)
require(knitr)
require(kableExtra)
```

```{r data, include=FALSE}
path <-"~/Documents/UACTech/SystemDocumentation"
inventoryfile <- "TechInventory.xlsx"
fname <- paste(path, inventoryfile, sep="/")
NetworkInventory <- read_excel(fname, sheet = "Network")
```

#Projectors
To turn on/off the front projectors, use the Control tab on each projector's page. There is a On/Off button in the upper left corner. It takes about 30 seconds before you will see any image and a minute before it is ready. Use the remote for the rear projector.

```{r} 
NetworkInventory %>% 
  filter(AssetTag %in% c("ZVVU-A001", "ZVVU-A002", 
                         "ZVVU-A003", "ZVVU-0001")) %>% 
  select(Usage, URL, Device, AssetTag,  Notes) %>%
  kable() %>%
  column_spec( 1,  bold = TRUE ) %>%
  kable_styling("striped", full_width = TRUE)
```

# Video Matrix Switch
Use this page to change our video routing configuration. The left hand side is the outputs, and the right hand the inputs. There is a number in the lower right corner of the output boxes which tells you which input it is currently linked to. To Change it, click on the output and then the desired input.

```{r} 
NetworkInventory %>% 
  filter(AssetTag=="ZVKU-A001") %>% 
  select(Usage, URL, Device, AssetTag,  Notes) %>%
  kable() %>%
  column_spec( 1,  bold = TRUE ) %>%
  kable_styling("striped", full_width = TRUE)
```

#Lighting Control
QLC has to be running on the video iMac for this link to work. The formatting on that web page can sometimes be funky.

```{r} 
NetworkInventory %>% 
  filter(AssetTag %in% c("CDMU-A002")) %>% 
  select(Usage, URL, Device, AssetTag,  Notes) %>%
  kable() %>%
  column_spec( 1,  bold = TRUE ) %>%
  kable_styling("striped", full_width = TRUE)
```

#Web Sites
```{r}
sites <- tribble(
  ~Name, ~URL, ~Notes,
  "UAC Web Page", "http://www.uachome.org", "",
  "Planning Center", "https://www.planningcenteronline.com", "",
  "Vimeo", "https://vimeo.com/unionvillealliance", "",
  "Slack", "https://unionvillealliance.slack.com/", "",
  "Remote Login", "https://remoteassist.neysh.ca/Host", "",
  "Tech Documents", "Dropbox/UAC_Tech_Docs/", "Location of core documents",
  "This Page", "Dropbox/UAC_Tech_Docs/TechHomePage.html/TechHomePage.html", ""
)

sites %>%
  kable() %>%
  column_spec( 1,  bold = TRUE ) %>%
  kable_styling("striped", full_width = TRUE)
```

#Other Devices
You likely will never need to use these pages.

```{r} 
NetworkInventory %>% 
  filter(AssetTag %in% c("NSCU-A004", "ZVKU-A002", 
                         "ZVCU-A001", "ZVCU-A002", "ZVCU-A003")) %>% 
  select(Usage, URL, Device, AssetTag,  Notes) %>%
  kable() %>%
  column_spec( 1,  bold = TRUE ) %>%
  kable_styling("striped", full_width = TRUE)
```

[Back to top](#top)