---
title: "Troubleshooting"
author: "UAC Media Arts"
execute:
  eval: true
  echo: false
  warning: false
  message: false
format:
  html:
    toc: true
    toc-depth: 2
  pdf:
    toc: true
    toc-depth: 2
  titlepage-pdf:
    toc: true
    toc-depth: 2
    
format-links: false  # This hides links to pdf/ipynb

always_allow_html: yes
editor:
  markdown:
    wrap: sentence
---

# Troubleshooting Guide

This document provides troubleshooting information for AVL systems, organized by category and indexed by both tags and asset tags.


```{=html}
<style>
.issue-page {
  border: 1px solid #d7d7d7;
  border-radius: 10px;
  padding: 1.25rem 1.5rem;
  margin: 1.25rem 0 2rem 0;
  background: #fcfcfc;
  box-shadow: 0 1px 3px rgba(0, 0, 0, 0.06);
}

.issue-page h3 {
  margin-top: 0;
}

.issue-meta {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(220px, 1fr));
  gap: 0.75rem 1rem;
  margin: 1rem 0 1.25rem 0;
}

.issue-meta-item {
  background: #f2f5f7;
  border-radius: 8px;
  padding: 0.75rem 0.9rem;
}

.issue-meta-label {
  font-size: 0.8rem;
  font-weight: 700;
  text-transform: uppercase;
  letter-spacing: 0.03em;
  color: #4d5963;
  margin-bottom: 0.2rem;
}

.issue-section {
  margin-top: 1rem;
}

.issue-tags {
  margin-top: 1.25rem;
  font-size: 0.95rem;
}

.issue-tags a,
.tag-index a {
  text-decoration: none;
}

.tag-index ul {
  margin-bottom: 1rem;
}

@media print {
  .issue-page {
    break-inside: avoid;
    page-break-inside: avoid;
  }
}
</style>
```

```{r packages}
source("./commonPackages.R")
library(markdown)
```

```{r functions}
source("./commonFunctions.R")
source("./commonDiagram.R")
```

```{r data}
db.network <- get.network()
further <- get.further()
db.cables <- get.cables()
db.assets <- get.assets()

db.issues <- read_excel("./data/knowledgebase.xlsx", sheet = "Issues") 


# Strip whitespace from column names
colnames(db.issues) <- str_trim(colnames(db.issues))

db.issues <- db.issues |>
  filter(!is.na(IssueID)) |>
  filter(is.na(Active) | Active == "Yes") |>
  mutate(
    SortOrder = replace_na(SortOrder, Inf),
    Category = replace_na(Category, "Uncategorized"),
    Subcategory = replace_na(Subcategory, "General"),
    Tags = replace_na(Tags, ""),
    AppliesToAssetTag = replace_na(AppliesToAssetTag, "")
  ) |>
  arrange(Category, Subcategory, SortOrder, Title)
```

```{r helpers}
slugify <- function(x) {
  x |>
    str_to_lower() |>
    str_replace_all("[^a-z0-9]+", "-") |>
    str_replace_all("(^-+|-+$)", "")
}

escape_html <- function(x) {
  htmltools::htmlEscape(x %||% "")
}

normalize_text <- function(x) {
  x <- x %||% ""
  x <- str_replace_all(x, "\r\n?", "\n")
  x <- str_trim(x)
  if (identical(x, "")) NA_character_ else x
}

render_markdown <- function(text) {
  if (is.na(text) || identical(text, "")) {
    return("")
  }

  # Render markdown to HTML
  html_output <- markdown::markdownToHTML(
    text = text,
    fragment.only = TRUE,
    options = c("fragment_only", "autolink", "tables", "fenced_code")
  )

  # Clean up extra whitespace
  html_output <- str_trim(html_output)

  return(html_output)
}

render_issue_section <- function(label, value) {
  value <- normalize_text(value)
  if (is.na(value)) {
    return("")
  }

  # Render markdown content
  content <- render_markdown(value)

  glue(
    "<div class=\"issue-section\">
       <h4>{escape_html(label)}</h4>
       <div>{content}</div>
     </div>"
  )
}

render_issue_page <- function(issue_row) {
  issue <- as.list(issue_row)
  issue_anchor <- paste0("issue-", slugify(issue$IssueID))
  issue_title <- issue$Title %||% issue$IssueID

  tags_raw <- issue$Tags %||% ""
  if (is.na(tags_raw)) tags_raw <- ""

  tags <- tags_raw |>
    str_split(",", simplify = FALSE) |>
    pluck(1) |>
    str_trim() |>
    discard(~ is.na(.x) || identical(.x, ""))

  tag_links <- if (length(tags) == 0) {
    "None"
  } else {
    paste0(
      "<a href=\"#tag-", slugify(tags), "\">", escape_html(tags), "</a>",
      collapse = ", "
    )
  }

  # Process AppliesToAssetTag
  asset_tags_raw <- issue$AppliesToAssetTag %||% ""
  if (is.na(asset_tags_raw)) asset_tags_raw <- ""

  asset_tags <- asset_tags_raw |>
    str_split(",", simplify = FALSE) |>
    pluck(1) |>
    str_trim() |>
    discard(~ is.na(.x) || identical(.x, ""))

  asset_tag_links <- if (length(asset_tags) == 0) {
    "None"
  } else {
    paste0(
      "<a href=\"#asset-", slugify(asset_tags), "\">", escape_html(asset_tags), "</a>",
      collapse = ", "
    )
  }

  sections <- compact(list(
    render_issue_section("Symptom", issue$Symptom),
    render_issue_section("Trigger Conditions", issue$TriggerConditions),
    render_issue_section("Likely Cause", issue$LikelyCause),
    render_issue_section("Recovery Steps", issue$RecoverySteps),
    render_issue_section("Notes", issue$Notes)
  )) |>
    discard(~ is.na(.x) || identical(.x, "")) |>
    paste(collapse = "\n")

  glue(
    "<div id=\"{issue_anchor}\" class=\"issue-page\">
       <h3>{escape_html(issue_title)}</h3>
       <div class=\"issue-meta\">
         <div class=\"issue-meta-item\">
           <div class=\"issue-meta-label\">Issue ID</div>
           <div>{escape_html(issue$IssueID)}</div>
         </div>
         <div class=\"issue-meta-item\">
           <div class=\"issue-meta-label\">Applies To</div>
           <div>{escape_html(issue$AppliesToAssetType)}</div>
         </div>
       </div>
       {sections}
       <div class=\"issue-tags\">
         <strong>Tags:</strong> {tag_links}
       </div>
       <div class=\"issue-tags\">
         <strong>Applies to Asset Tags:</strong> {asset_tag_links}
       </div>
     </div>"
  )
}

render_tag_index <- function(issue_data) {
  tag_map <- issue_data |>
    transmute(
      IssueID,
      Title,
      issue_anchor = paste0("issue-", slugify(IssueID)),
      tag_list = str_split(Tags, ",")
    ) |>
    unnest(tag_list) |>
    mutate(tag = str_trim(tag_list)) |>
    filter(!is.na(tag) & tag != "") |>
    distinct(tag, IssueID, Title, issue_anchor) |>
    arrange(tag, IssueID)

  if (nrow(tag_map) == 0) {
    return(
      "<section id=\"tag-index\" class=\"tag-index\">
         <h1>Tag Index</h1>
         <p>No tags were found.</p>
       </section>"
    )
  }

  tags <- unique(tag_map$tag)
  pieces <- c(
    "<section id=\"tag-index\" class=\"tag-index\">",
    "<h1>Tag Index</h1>"
  )

  for (tag in tags) {
    tag_anchor <- paste0("tag-", slugify(tag))
    pieces <- c(
      pieces,
      glue("<h2 id=\"{tag_anchor}\">{escape_html(tag)}</h2>"),
      "<ul>"
    )

    tag_rows <- tag_map |>
      filter(tag == !!tag)

    for (i in seq_len(nrow(tag_rows))) {
      pieces <- c(
        pieces,
        glue(
          "<li><a href=\"#{tag_rows$issue_anchor[i]}\">{escape_html(tag_rows$IssueID[i])}: {escape_html(tag_rows$Title[i])}</a></li>"
        )
      )
    }

    pieces <- c(pieces, "</ul>")
  }

  pieces <- c(pieces, "</section>")
  paste0(pieces, collapse = "\n")
}

render_asset_tag_index <- function(issue_data, asset_data) {
  # Parse asset tags from all issues
  asset_tag_map <- issue_data |>
    transmute(
      IssueID,
      Title,
      issue_anchor = paste0("issue-", slugify(IssueID)),
      asset_tag_list = str_split(AppliesToAssetTag, ",")
    ) |>
    unnest(asset_tag_list) |>
    mutate(AssetTag = str_trim(asset_tag_list)) |>
    filter(AssetTag != "" & !is.na(AssetTag)) |>
    distinct(AssetTag, IssueID, Title, issue_anchor)

  if (nrow(asset_tag_map) == 0) {
    return(
      "<section id=\"asset-tag-index\" class=\"tag-index\">
         <h1>Asset Tag Index</h1>
         <p>No asset tags were found.</p>
       </section>"
    )
  }

  # Join with asset data to get Manufacturer, Model, Usage
  asset_tag_map <- asset_tag_map |>
    left_join(
      asset_data |> select(AssetTag, Manufacturer, Model, Usage),
      by = "AssetTag"
    ) |>
    arrange(AssetTag, IssueID)

  asset_tags <- unique(asset_tag_map$AssetTag)
  pieces <- c(
    "<section id=\"asset-tag-index\" class=\"tag-index\">",
    "<h1>Asset Tag Index</h1>"
  )

  for (asset_tag in asset_tags) {
    asset_anchor <- paste0("asset-", slugify(asset_tag))

    # Get asset info for this tag (should be same for all rows with this tag)
    asset_info <- asset_tag_map |>
      filter(AssetTag == !!asset_tag) |>
      slice(1)

    # Build the heading with asset details
    heading_parts <- c(escape_html(asset_tag))
    if (!is.na(asset_info$Manufacturer) && asset_info$Manufacturer != "") {
      heading_parts <- c(heading_parts, escape_html(asset_info$Manufacturer))
    }
    if (!is.na(asset_info$Model) && asset_info$Model != "") {
      heading_parts <- c(heading_parts, escape_html(asset_info$Model))
    }
    if (!is.na(asset_info$Usage) && asset_info$Usage != "") {
      heading_parts <- c(heading_parts, paste0("(", escape_html(asset_info$Usage), ")"))
    }

    heading_text <- paste(heading_parts, collapse = " - ")

    pieces <- c(
      pieces,
      glue("<h2 id=\"{asset_anchor}\">{heading_text}</h2>"),
      "<ul>"
    )

    asset_rows <- asset_tag_map |>
      filter(AssetTag == !!asset_tag)

    for (i in seq_len(nrow(asset_rows))) {
      pieces <- c(
        pieces,
        glue(
          "<li><a href=\"#{asset_rows$issue_anchor[i]}\">{escape_html(asset_rows$IssueID[i])}: {escape_html(asset_rows$Title[i])}</a></li>"
        )
      )
    }

    pieces <- c(pieces, "</ul>")
  }

  pieces <- c(pieces, "</section>")
  paste0(pieces, collapse = "\n")
}
```

# Introduction
This page is intended to be a troubleshooting guide for common issues that may arise when working with the AVL systems at UAC. It provides step-by-step instructions and solutions for various problems that users may encounter.

# Troubleshooting Issues

```{r issue-pages, results='asis'}
issue_groups <- db.issues |>
  group_by(Category, Subcategory) |>
  group_split()

current_category <- NULL
output <- character()

for (group in issue_groups) {
  category <- group$Category[[1]]
  subcategory <- group$Subcategory[[1]]

  if (!identical(category, current_category)) {
    output <- c(output, glue("\n# {category}\n"))
    current_category <- category
  }

  output <- c(output, glue("\n## {subcategory}\n"))

  for (i in seq_len(nrow(group))) {
    output <- c(
      output,
      "```{=html}",
      render_issue_page(group[i, ]),
      "```",
      ""
    )
  }
}
```

```{r tag-index, results='asis' }
output <- c(
  output,
  "```{=html}",
  render_tag_index(db.issues),
  "```",
  "",
  "```{=html}",
  render_asset_tag_index(db.issues, db.assets),
  "```"
)
```

```{r render-output, results='asis'}
knitr::asis_output(paste(output, collapse = "\n"))
```

{{< include common_trailer.qmd >}}